---
title: "Examination of classifiers with binned intensities"
author: "Peter Kjer Hansen"
date: "2025-09-18"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---
# Introduction

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "svg")

#packages
library(tidyverse)
library(caret)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(broom)
library(readxl)
library(ggpmisc) #For easy plots of coefficients on plots
library(lsr) #Contains cohensD() function
library(nnet) #Feedforward neural network
library(UpSetR) #Package for doing upset plots
library(ggrepel) #Pacakge for making repel text
library(boot) # For bootstrapping confidence intervals
library(pheatmap) # Heatmaps

#Working directory
#Exon description dataset
Path_to_exon_description_sheet <- 'INSERT PATH TO SHEET WITH EXON DESCRIPTIONS'
File_with_exon_description_sheet <- 'INSERT FILE NAME OF .XLSX WITH EXON DESCRIPTIONS'
Event_sheet <- 'INSERT SHEET NAME'
LUMIER_sheet <- 'INSERT SHEET NAME'

# Model folders
# Super folder
classifier_superfolder <- 'INSERT PATH TO SUPER DIRECTORY CONTAINING THE CLASSIFIERS TRAINED USING VARIOUS TYPES OF BINNING'

#Postrans
Postransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON TRANSFECTED CELLS'
#Negtrans 10 percentile with rep aware sampling, No Golgin
Negtransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON NON-TRANSFECTED CELLS'

# Cell datasets and summaries
Cell_data_folder <- 'INSERT PATH TO FOLDER WITH .CSVS CONTAINING THE SINGLE CELL MEASUREMENTS'

# Bootstrap confidence threshold
bootstrap_confidence_threshold <- 0.99
```

```{r Load results from classifiers trained on cells across entire intensity range, echo = FALSE}
#
load(paste0(classifier_superfolder,'/variable_importance_full_data'))

#
load(paste0(classifier_superfolder,'/model_performance_full_data'))

```


```{r Isoform pair descriptions, echo = FALSE}
# Replications of sampling + classifier training + assessment
#Pairs to be test for the various sets
#Smaller sets of pairs for set 1 and A, separately. These are used for the positive classifiers
#PAIRS_1 <- c('PAIR_01','PAIR_03','PAIR_04','PAIR_08','PAIR_09')
#PAIRS_A <- c('PAIR_01','PAIR_03','PAIR_04','PAIR_08','PAIR_09')
#These are the actual isoform tests
PAIRS_1A <- c('PAIR_01','PAIR_02','PAIR_03','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10', 'PAIR_RAB5A', 'PAIR_PosControl')
PAIRS_1A_alternative_comps <- c('PAIR_03DExVSPanEx','PAIR_03bothEx','PAIR_03ExVsEx','PAIR_03Ex1VsBoth')
PAIRS_B <- c('PAIR_01','PAIR_02','PAIR_03','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10')
PAIRS_C <- c('PAIR_02','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10')
PAIRS_D_wo_01 <- c('PAIR_02','PAIR_05','PAIR_08','PAIR_09')#,'PAIR_RAB5A', 'PAIR_PosControl') # PAIR_03 (EVI5) and PAIR_04 (OCRL) removed. Note, OCRL is the only one that shows difference.
PAIRS_D_alternative_comps <- c('PAIR_01wtVS57','PAIR_01wtVS168','PAIR_01dex57VS168','PAIR_08DExVSaltEx','PAIR_08bothEx','PAIR_08ExVsEx','PAIR_08Ex1VsBoth')

```



```{r Function to load in the classifier performance and importance, echo=FALSE}
#
Replicate_performance_and_importance <- function(MODEL_SUPER_FOLDER,
                                                 BINNING_APPROACH,
                                                 WHICH_BIN,
                                                 TRANSFECTION_STATUS,
                                                 SET,
                                                 PAIR,
                                                 PERCENTILE_CUTOFF = 0){
  if(TRANSFECTION_STATUS == 'POSITIVE'){
    load(paste0(MODEL_SUPER_FOLDER,'/',BINNING_APPROACH,'_postrans_',WHICH_BIN,'/',SET,'_',PAIR))
  }
  if(TRANSFECTION_STATUS == 'NEGATIVE'){
    load(paste0(MODEL_SUPER_FOLDER,'/',BINNING_APPROACH,'_negtrans_',WHICH_BIN,'/NegTransModel_',SET,'_',PAIR))
  }
  #
  modeL_fit_and_tune <- function(variable){
    a <- variable$results %>%
      dplyr::filter(!is.na(ROC)) %>% 
      dplyr::arrange(desc(ROC)) %>% 
      dplyr::slice_head(n = 1) %>% 
      dplyr::mutate(size_decay_tune = paste0('size:',size,'_decay:',decay))
    return(a)
  }
  #
  variable_importance_ranking <- function(variable){
    variable_importance <- variable$variable_importance %>% 
      arrange(desc(Overall)) %>%
      rownames_to_column(var = 'Feature') %>% 
      as_tibble()
    
    rank <- seq(1, dim(variable_importance)[1])
    
    variable_importance <- bind_cols(variable_importance, 'Rank' = rank)
    return(variable_importance)
  }
  #
  n_cells <- function(variable){
    cell_count <- variable$training_data_intensity %>% 
    count()
    return(cell_count)
  }
  median_intensity <- function(variable){
    median_intensity <- variable$training_data_intensity %>%
      ungroup() %>% 
      group_by(.outcome) %>% 
      summarize(median_intensity = median(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
      pivot_wider(names_from = .outcome,
                  values_from = median_intensity,
                  names_prefix = 'MedianIntensity_')
    return(median_intensity)
  }
    
  #
  if(class(replicate_nnet)[1] == 'matrix'){
    ISOFORM_MODELS <- as.list(replicate_nnet["ISOFORM_MODEL",]) #Converts matrix rows into lists
    #NEGATIVE_MODELS <- as.list(replicate_nnet[2,])
    #POSITIVE_MODELS <- as.list(replicate_nnet[3,])
  }
  if(class(replicate_nnet)[1] == 'list'){
    ISOFORM_MODELS <- replicate_nnet
  }
  #
  isoform_model_fit_and_tune <- lapply(ISOFORM_MODELS, FUN = modeL_fit_and_tune)
  isoform_variable_importance <- lapply(ISOFORM_MODELS, FUN = variable_importance_ranking)
  isoform_n_cells <- lapply(ISOFORM_MODELS, FUN = n_cells)
  isoform_median_intensity <- lapply(ISOFORM_MODELS, FUN = median_intensity)
  
  #
  iso_performance <- bind_rows(isoform_model_fit_and_tune, .id = 'Replicate') %>%
      dplyr::mutate(Replicate = row_number()) %>% 
                     dplyr::mutate(Group = 'Isoform')
  
  #
  isoform_intensity <- bind_rows(isoform_median_intensity, .id = 'Replicate') %>%
      dplyr::mutate(Replicate = row_number()) %>% 
                     dplyr::mutate(Group = 'Isoform')
  #
  
  iso_n <- bind_rows(isoform_n_cells, .id = 'Replicate') %>% 
      dplyr::mutate(Replicate = row_number()) %>% 
                     dplyr::mutate(Group = 'Isoform') %>% 
    left_join(x = ., y = isoform_intensity, by = join_by('Replicate', 'Group'))
   
  ###
  number_of_classifier_iterations <- length(isoform_variable_importance)
  number_of_features <- length(unique(isoform_variable_importance[[1]]$Feature))
  #
  iso_importance <- bind_rows(isoform_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  
  
  results_list <- list('performance' = iso_performance, 'SET' = SET, 'PAIR' = PAIR, 'TRANSFECTION_STATUS' = TRANSFECTION_STATUS, 'PERCENTILE_CUTOFF' = PERCENTILE_CUTOFF, 'BINNING_APPROACH' = BINNING_APPROACH, 'WHICH_BIN' = WHICH_BIN,
                       'var_importance_iso' = iso_importance, 'n_cells' = iso_n, median_intensity = 'median_intensity')
  return(results_list)
}
```



```{r Loading in performance and variable importance scores for all binned classiifers and compiling into tibbles for each set, echo = FALSE}
### Vectors for iteration
Binning_approach_vector <- c('Approach1','Approach2','Approach3', 'Full')
Which_bin_vector <- c('lowerbin','upperbin')
Transfection_status_vector <- c('POSITIVE','NEGATIVE')

#Set 1A
for(i in PAIRS_1A){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_1A',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
      
        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}

#Set 1A ALT comps
for(i in PAIRS_1A_alternative_comps){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_1A',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
      
        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set 1A + 1A alt comps
combined_model_performance_SET_1A <- bind_rows(mget(ls(pattern = 'model_performance_SET_1A_PAIR')))
#
rm(list = ls(pattern = 'model_performance_SET_1A_PAIR'))
## Variable importance
combined_variable_importance_SET_1A <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR')))
#
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR'))


#Set B
for(i in PAIRS_B){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_B',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
      
        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set B
combined_model_performance_SET_B <- bind_rows(mget(ls(pattern = 'model_performance_SET_B_PAIR')))
#
rm(list = ls(pattern = 'model_performance_SET_B_PAIR'))
## Variable importance
combined_variable_importance_SET_B <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_B_PAIR')))
#
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_B_PAIR'))
  

#Set C
for(i in PAIRS_C){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_C',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
      
        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set C
combined_model_performance_SET_C <- bind_rows(mget(ls(pattern = 'model_performance_SET_C_PAIR')))
#
rm(list = ls(pattern = 'model_performance_SET_C_PAIR'))
## Variable importance
combined_variable_importance_SET_C <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_C_PAIR')))
#
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_C_PAIR'))


#Set D
for(i in PAIRS_D_wo_01){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_D',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
      
        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}
#Set D Alt comps
for(i in PAIRS_D_alternative_comps){
  for(j in Binning_approach_vector){
    for(k in Which_bin_vector){
      for(l in Transfection_status_vector){
        test <- Replicate_performance_and_importance(MODEL_SUPER_FOLDER = classifier_superfolder,
                                                     BINNING_APPROACH = j,
                                                     WHICH_BIN = k,
                                                     TRANSFECTION_STATUS = l,
                                                     SET = 'SET_D',
                                                     PAIR = i,
                                                     PERCENTILE_CUTOFF = 0)
        #
        
        #Creates absolute performance metrics (single metrics)
        assign(paste0(test$TRANSFECTION_STATUS,'trans_model_performance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$performance %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN) %>% 
                 left_join(., y = test$n_cells, by = c('Replicate','Group')))
#      
#        #Creates variable importance object
                assign(paste0(test$TRANSFECTION_STATUS,'trans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR,'_',test$BINNING_APPROACH,'_',test$WHICH_BIN),
               test$var_importance_iso %>% 
                 dplyr::mutate('SET' = test$SET,
                               'ISOFORM_PAIR' = test$PAIR,
                               'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                               'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF,
                               'BINNING_APPROACH' = test$BINNING_APPROACH,
                               'WHICH_BIN' = test$WHICH_BIN))

}}}}


#Combining individual isoforms into proper dataset
## Absolute performance
#Set D
combined_model_performance_SET_D <- bind_rows(mget(ls(pattern = 'model_performance_SET_D_PAIR')))
#
rm(list = ls(pattern = 'model_performance_SET_D_PAIR'))
## Variable importance
combined_variable_importance_SET_D <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_D_PAIR')))
#
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_D_PAIR'))
```


```{r Loading exon descriptions, echo = FALSE}
#Exon description
Exon_descriptions <- readxl::read_xlsx(path = paste0(Path_to_exon_description_sheet, File_with_exon_description_sheet),
                                       sheet = Event_sheet) %>% 
  dplyr::mutate('microexon' = Exon_length_NT <= 30) %>% 
  dplyr::mutate(Gene_name_Rclassifier = case_when( #Note, currently because names in SET D are marked w. asteriks, they have to be so in this exon description file. But excel didn't like starting the name w. an asteriks.
    Gene_name_Rclassifier == 'ATXN2' ~ '*ATXN2', #Only done for the isoform pairs that are not recurring
    Gene_name_Rclassifier == 'EVI5' ~ '*EVI5',
    Gene_name_Rclassifier == 'PPFIA1' ~ '*PPFIA1',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExA' ~ 'CLASP1_ExA_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExB' ~ 'CLASP1_noEx_vs_ExB',
    .default = Gene_name_Rclassifier))

Exon_descriptions_reduced <- Exon_descriptions %>% 
  dplyr::select(microexon, Splice_event_enriched_in_neural_tissue, Splice_event_enriched_in_pancreatic_islet_cells, Enrichment_comment, Exon_length_NT, Gene_name_Rclassifier, Exon_name_Rclassifier, EVENT_ID_vastDB, Location_in_protein) %>% 
  dplyr::filter(!c(Gene_name_Rclassifier %in% c('VAV2'))) #Current_naming_doesn't_work_well_with_genes_with_multiple_exons

### ISOFORM_PAIRS_EXCLUDE
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_DOUBLES <- c('VAV2','*SH3KBP1_D/E','*OCRL_D/E','*SH3GLB1_D/E')
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_INTENSITY <- c('VAV2','PACSIN2') ##THIS DEFINES WHICH ISOFORM PAIRS ARE EXCLUDED.

```


```{r combining absolute classifier outputs into proper datasets, echo = FALSE}
#Combining individual isoforms into proper dataset

#All
combined_model_performance_all <- bind_rows(mget(ls(pattern = 'combined_model_performance_SET_'))) %>%  #WRITE CASE_WHEN TO GIVE ALL SET + PAIR COMBINATIONS THEIR GENE NAME (COULD POTENTIALLY BE GENE + EXON ID -> ALTHOUGH COMBINATIONS GET TRICKY STILL)
  dplyr::mutate('Gene_name' = case_when(
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    #
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    #
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_02' ~ 'Apbb1',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA', #
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03bothEx' ~ 'CLASP1_noEx_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03DExVSPanEx' ~ 'CLASP1_noEx_vs_ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03Ex1VsBoth' ~ 'CLASP1_ExA_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03ExVsEx' ~ 'CLASP1_ExA_vs_ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_05' ~ 'DCTN1',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_06' ~ 'VAV2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_07' ~ 'FBXW11',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_10' ~ 'SPAG9',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_RAB5A' ~ 'NegControl',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_PosControl' ~ 'PosControl',
    #
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_01' ~ 'AP1G1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_02' ~ 'DAAM1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_03' ~ 'DNM1L',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_04' ~ 'DYNC1LI2',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_05' ~ 'EEA1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_06' ~ 'KIF3A',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_07' ~ 'ROBO1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_08' ~ 'SCYL2',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_09' ~ 'SRC',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_10' ~ 'TNK2',
    #
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_02' ~ 'CLTA',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_04' ~ 'DNM2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_05' ~ 'Dnm2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_06' ~ 'Dnm3',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_07' ~ 'OCRL',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_08' ~ 'PACSIN2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_09' ~ 'SH3GLB1',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_10' ~ 'SH3KBP1',
    #
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01dex57VS168' ~ 'APP_noEx_vs_ExA*', #Ex168nt is ExA, Ex57nt is ExB
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01wtVS168' ~ 'APP_noEx_vs_ExA+ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01wtVS57' ~ 'APP_ExA_vs_ExA+ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_02' ~ 'ATXN2*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_03' ~ 'EVI5*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_04' ~ 'OCRL_D/E*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_05' ~ 'PPFIA1*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_06' ~ 'SH3GLB1_D/E*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_07' ~ 'SH3KBP1_D/E*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08' ~ 'VAV2_noEx_vs_ExA*', #ExA (is likely the downstream micro-exon), ExB is upstream micro-exon (I think)
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_RAB5A' ~ 'NegControl_BatchE',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_PosControl' ~ 'PosControl_BatchE',
    #
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08bothEx' ~ 'VAV2_noEx_vs_ExA+ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08DExVSaltEx' ~ 'VAV2_noEx_vs_ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08Ex1VsBoth' ~ 'VAV2_ExA_vs_ExA+ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08ExVsEx' ~ 'VAV2_ExA_vs_ExB*',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_09' ~ 'VAV2_ExB_vs_ExA+ExB*',
    #
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_01dex57VS168' ~ 'APP_noEx_vs_ExA', #Ex168nt is ExA, Ex57nt is ExB
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_01wtVS168' ~ 'APP_noEx_vs_ExA+ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_01wtVS57' ~ 'APP_ExA_vs_ExA+ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_02' ~ '*ATXN2',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_03' ~ '*EVI5',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_04' ~ '*OCRL_D/E',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_05' ~ '*PPFIA1',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_06' ~ '*SH3GLB1_D/E',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_07' ~ '*SH3KBP1_D/E',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_08' ~ '*VAV2_noEx_vs_ExA', #ExA (is likely the downstream micro-exon), ExB is upstream micro-exon (I think)
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_08bothEx' ~ '*VAV2_noEx_vs_ExA+ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_08DExVSaltEx' ~ '*VAV2_noEx_vs_ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_08Ex1VsBoth' ~ '*VAV2_ExA_vs_ExA+ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_08ExVsEx' ~ '*VAV2_ExA_vs_ExB',
    SET == 'SET_E' & ISOFORM_PAIR == 'PAIR_09' ~ '*VAV2_ExB_vs_ExA+ExB'
  )) %>% 
  #left_join(., y = SUMMARY_of_all_sample_ratios, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) %>% 
  left_join(., y = Exon_descriptions_reduced, by = join_by('Gene_name' == 'Gene_name_Rclassifier')) %>% 
  #The fusion doesn't work perfectly for genes with multiple events - the line below removes an unwanted duplication of the VAV2 data (NOTE, THIS IS WHAT GIVES RISE TO THE MANY-TO-MANY RELATIONSHIP)
  dplyr::filter(!c(SET == 'SET_1A' & Gene_name == 'VAV2' & Exon_name_Rclassifier == 'ExB')) %>% 
  #
  dplyr::mutate(microexon = case_when( #Hacky way of making all events have microexon, yes/no label
    word(Gene_name, 1, 1, sep = fixed('_')) == '*APP' ~ FALSE,
    word(Gene_name, 1, 1, sep = fixed('_')) == '*VAV2' ~ TRUE,
    word(Gene_name, 1, 1, sep = fixed('_')) == 'CLASP1' ~ TRUE,
    .default = microexon)) %>% 
  # Renaming binning approach for non-binned dataset and removing duplicates
  dplyr::mutate(BINNING_APPROACH = if_else(BINNING_APPROACH == 'Full', 'None', BINNING_APPROACH)) %>% 
  dplyr::filter(!c(BINNING_APPROACH == 'None' & WHICH_BIN == 'upperbin')) %>% 
  dplyr::mutate(WHICH_BIN = if_else(BINNING_APPROACH == 'None','all', WHICH_BIN))


#Dataframe w. the gene name SET + PAIR combination
gene_ids_match <- combined_model_performance_all %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB) %>%
  unique()

#Dataframe w. n used for classifier and the gene names
n_used_for_classifier <- combined_model_performance_all %>% 
  dplyr::select(n, Gene_name) %>% 
  unique() %>% 
  dplyr::group_by(Gene_name) %>% 
  summarize(n = mean(n))

```


```{r Standardizing the isoform intensity naming, echo = FALSE}
# Fixing that some isoforms have other labels than WT and DEX - this basically makes it uniform so we can plot intensities for all u
combined_model_performance_all <- combined_model_performance_all %>% 
  dplyr::mutate(MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_Both, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_PanEx, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_Ex1, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_DEx168nt, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_DEx57nt, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_AltEx, MedianIntensity_DEx),
                MedianIntensity_DEx = if_else(is.na(MedianIntensity_DEx) == TRUE, MedianIntensity_Ex2, MedianIntensity_DEx)) %>% 
  dplyr::mutate(MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_Ex2, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_AltEx, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_DEx57nt, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_DEx168nt, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_Ex1, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_PanEx, MedianIntensity_WT),
                MedianIntensity_WT = if_else(is.na(MedianIntensity_WT) == TRUE, MedianIntensity_Both, MedianIntensity_WT)) #%>% 
  # Remove intensity cols with special exon names
  #dplyr::select(-all_of(MedianIntensity_Both, MedianIntensity_PanEx, MedianIntensity_Ex1))
```


```{r creating relative ROC that compares negative transfectant and positive transfectant ROCs, echo = FALSE}
#Splitting the combined ROC dataset according to transfection status
#Positive transfectants
combined_model_performance_all_postrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE')
#Negative transfectants
combined_model_performance_all_negtrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE')

#Joining positive and negative transfectants in a wide-format
combined_model_performance_all_posneg_relative <- full_join(x = combined_model_performance_all_postrans, y = combined_model_performance_all_negtrans,
                                                            by = join_by(SET, ISOFORM_PAIR, Group, Replicate, BINNING_APPROACH, WHICH_BIN),
                                                            suffix = c('_postrans', '_negtrans')) %>%
  # Creating ROC relative column (pos - neg). Can be negative.
  dplyr::mutate(ROC_posneg_relative = ROC_postrans - ROC_negtrans,
                tmp_norm_ROC = (ROC_postrans - ROC_negtrans)/(1 - ROC_negtrans),
                Ceiling_normalised_ROC = if_else(tmp_norm_ROC >= 0, tmp_norm_ROC, (ROC_postrans - ROC_negtrans)/(1 - ROC_postrans))) %>% 
  #
  dplyr::filter(!BINNING_APPROACH == 'Approach2') %>% 
  dplyr::mutate(BINNING_APPROACH = if_else(BINNING_APPROACH == 'Approach3','Approach2',BINNING_APPROACH))

```


### Two separate ways of plotting the collective classifier performance

```{r Creating order of gene names based on the median relative difference between pos and negtarns classifiers a single pos and neg contorl included, echo=FALSE}
# Creating order of gene names so we can genes with best isoform performance on top
gene_name_order <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(SET %in% c('SET_1A', 'SET_B', 'SET_C', 'SET_D')) %>% 
  dplyr::filter(PERCENTILE_CUTOFF_negtrans == 0) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::filter(BINNING_APPROACH == 'None') %>% 
  ungroup() %>% 
  group_by(Gene_name_postrans) %>% 
  summarize(mean_ROC_posneg_relative = mean(ROC_posneg_relative),
            median_ROC_posneg_relative = median(ROC_posneg_relative),
            mean_ceiling_normalised_ROC = mean(Ceiling_normalised_ROC),
            median_ceiling_normalised_ROC = median(Ceiling_normalised_ROC)) %>% 
  ungroup() %>% 
  # Ordered according to median ceiling ROC
  arrange(median_ceiling_normalised_ROC) %>% 
  dplyr::pull(Gene_name_postrans)
# Use factor with levels to set the order of the genes
#combined_model_performance_all$Gene_name <- factor(combined_model_performance_all$Gene_name, levels = gene_name_order)

```


### Testing ceiling normalised ROC-AUC distributions for isoform classifiers using boot strap confidence intervals

```{r Function to perform bootstrap confidence interval caluclations, echo = FALSE}
#' Bootstrap Test for Pre-Normalized ROC Scores with Group Support
#'
#' This function calculates bootstrap confidence intervals for normalized ROC scores
#' that have already been calculated. It supports grouping by a variable (e.g., gene name).
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param group_value Value to filter by in the group column (e.g., specific gene name)
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#'
#' @return A list containing bootstrap statistics and test results
#'
#' @examples
#' # Example with pre-calculated normalized values
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2))
#' )
#' result <- bootstrap_norm_roc_grouped(data, "norm_roc", "Gene_name", "Gene1")
#' print(result)
#'
bootstrap_norm_roc_grouped <- function(data, 
                                       norm_col = "norm_roc", 
                                       group_col = NULL,
                                       group_value = NULL,
                                       conf_level = 0.95,
                                       n_bootstrap = 2000,
                                       one_sided = TRUE) {
  
  # Require boot package
  if (!requireNamespace("boot", quietly = TRUE)) {
    stop("Please install the 'boot' package: install.packages('boot')")
  }
  
  # Filter data by group if specified
  if (!is.null(group_col) && !is.null(group_value)) {
    if (!(group_col %in% colnames(data))) {
      stop(paste("Group column", group_col, "not found in data"))
    }
    data <- data[data[[group_col]] == group_value, ]
    if (nrow(data) == 0) {
      stop(paste("No data found for", group_col, "=", group_value))
    }
  }
  
  # Check if norm_col exists
  if (!(norm_col %in% colnames(data))) {
    stop(paste("Normalized score column", norm_col, "not found in data"))
  }
  
  # Extract normalized scores
  norm_scores <- data[[norm_col]]
  
  # Function for bootstrapping
  boot_func <- function(data, indices) {
    return(mean(data[indices]))
  }
  
  # Perform bootstrap
  boot_result <- boot::boot(norm_scores, boot_func, R = n_bootstrap)
  
  # Calculate confidence interval
  if (one_sided) {
    # One-sided interval (lower bound only)
    alpha <- 1 - conf_level
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound of percentile interval
    upper_bound <- Inf
  } else {
    # Two-sided interval
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound
    upper_bound <- ci$percent[5]  # Upper bound
  }
  
  # Determine if zero is in the confidence interval
  zero_in_ci <- (lower_bound <= 0 && upper_bound >= 0)
  
  # Create summary results
  result <- list(
    mean = mean(norm_scores),
    median = median(norm_scores),
    sd = sd(norm_scores),
    ci_lower = lower_bound,
    ci_upper = ifelse(one_sided, Inf, upper_bound),
    one_sided = one_sided,
    conf_level = conf_level,
    zero_in_ci = zero_in_ci,
    significant = !zero_in_ci,
    n_iterations = length(norm_scores),
    n_bootstrap = n_bootstrap,
    group_col = group_col,
    group_value = group_value,
    raw_scores = norm_scores,
    boot_result = boot_result
  )
  
  return(result)
}

#' Run Bootstrap Tests for Multiple Groups
#'
#' This function runs bootstrap tests for multiple groups and returns results in a data frame
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#' @param adjust_method Method for multiple testing correction (default "BH"). Options include 
#'                     "holm", "hochberg", "hommel", "bonferroni", "BH", "BY", "fdr", "none"
#'
#' @return A data frame with bootstrap test results for each group, including adjusted p-values
#'
#' @examples
#' # Example with pre-calculated normalized values for multiple genes
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2", "Gene3"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2), rnorm(50, 0.15, 0.15))
#' )
#' results <- bootstrap_multiple_groups(data, "norm_roc", "Gene_name")
#' print(results)
#'
bootstrap_multiple_groups <- function(data, 
                                      norm_col = "norm_roc", 
                                      group_col,
                                      conf_level = 0.95,
                                      n_bootstrap = 2000,
                                      one_sided = TRUE,
                                      adjust_method = "BH") {
  
  # Get unique groups
  groups <- unique(data[[group_col]])
  
  # Create empty results data frame
  results <- data.frame(
    group = character(),
    mean = numeric(),
    median = numeric(),
    sd = numeric(),
    ci_lower = numeric(),
    ci_upper = numeric(),
    p_value = numeric(),
    significant = logical(),
    adj_p_value = numeric(),
    adj_significant = logical(),
    n_iterations = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Loop through groups
  group_results <- list()
  p_values <- numeric(length(groups))
  
  for (i in seq_along(groups)) {
    group <- groups[i]
    # Run bootstrap test
    boot_result <- bootstrap_norm_roc_grouped(
      data = data,
      norm_col = norm_col,
      group_col = group_col,
      group_value = group,
      conf_level = conf_level,
      n_bootstrap = n_bootstrap,
      one_sided = one_sided
    )
    
    # Calculate p-value from bootstrap distribution
    if (one_sided) {
      # For one-sided test, calculate p-value as proportion of bootstrap values <= 0
      p_value <- mean(boot_result$boot_result$t <= 0)
    } else {
      # For two-sided test, calculate p-value based on whether 0 is in the CI
      # This is approximate but aligns with the confidence interval approach
      z_stat <- boot_result$mean / (boot_result$sd / sqrt(boot_result$n_iterations))
      p_value <- if (boot_result$mean >= 0) 2 * pnorm(-abs(z_stat)) else 2 * pnorm(-abs(z_stat))
    }
    
    p_values[i] <- p_value
    
    # Store result
    group_results[[i]] <- data.frame(
      group = group,
      mean = boot_result$mean,
      median = boot_result$median,
      sd = boot_result$sd,
      ci_lower = boot_result$ci_lower,
      ci_upper = ifelse(one_sided, Inf, boot_result$ci_upper),
      p_value = p_value,
      significant = boot_result$significant,
      n_iterations = boot_result$n_iterations
    )
  }
  
  # Adjust p-values for multiple testing
  adj_p_values <- p.adjust(p_values, method = adjust_method)
  
  # Combine results
  results <- do.call(rbind, group_results)
  results$adj_p_value <- adj_p_values
  results$adj_significant <- results$adj_p_value < (1 - conf_level)
  
  # Return results
  return(results)
}

#' Visualize Bootstrap Distribution
#'
#' Creates a histogram of bootstrap means with confidence interval
#'
#' @param boot_result Result from bootstrap_norm_roc_grouped function
#' @param bins Number of histogram bins (default 30)
#'
#' @return A ggplot2 object
#'
plot_bootstrap_dist <- function(boot_result, bins = 30) {
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Extract bootstrap samples
  t_values <- boot_result$boot_result$t
  
  # Create dataframe for plotting
  df <- data.frame(value = t_values)
  
  # Determine title suffix based on grouping
  group_suffix <- ""
  if (!is.null(boot_result$group_col) && !is.null(boot_result$group_value)) {
    group_suffix <- paste(" for", boot_result$group_col, "=", boot_result$group_value)
  }
  
  # Create plot
  p <- ggplot2::ggplot(df, ggplot2::aes(x = value)) +
    ggplot2::geom_histogram(bins = bins, fill = "steelblue", color = "white", alpha = 0.7) +
    ggplot2::geom_vline(xintercept = boot_result$ci_lower, color = "red", linetype = "dashed") +
    ggplot2::geom_vline(xintercept = 0, color = "black", linetype = "solid") +
    ggplot2::labs(
      title = paste0("Bootstrap Distribution of Normalised ROC-AUC Score", group_suffix),
      subtitle = paste0(
        ifelse(boot_result$one_sided, "One-sided ", "Two-sided "), 
        boot_result$conf_level * 100, "% CI: [", 
        round(boot_result$ci_lower, 4), ", ", 
        ifelse(boot_result$one_sided, "∞", round(boot_result$ci_upper, 4)), "]"
      ),
      x = "Normalised ROC-AUC Score",
      y = "Frequency",
      caption = paste("Mean:", round(boot_result$mean, 4), 
                      "| Significant:", boot_result$significant)
    ) +
    ggplot2::theme_minimal()
  
  return(p)
}

#' Create Forest Plot of Bootstrap Results
#'
#' Creates a forest plot of bootstrap results for multiple groups
#'
#' @param results Data frame from bootstrap_multiple_groups function
#' @param sort_by Column to sort by (default "mean")
#' @param decreasing Logical; if TRUE, sorts in decreasing order (default TRUE)
#' @param color_by_significance Logical; if TRUE, colors points by significance (default TRUE)
#'
#' @return A ggplot2 object
#'
plot_forest <- function(results, 
                        sort_by = "mean", 
                        decreasing = TRUE,
                        color_by_significance = TRUE,
                        use_adjusted_significance = TRUE) {
  
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Sort results
  results <- results[order(results[[sort_by]], decreasing = decreasing), ]
  
  # Make sure group is a factor in the right order for plotting
  results$group <- factor(results$group, levels = results$group)
  
  # Determine which significance column to use
  sig_col <- if(use_adjusted_significance && "adj_significant" %in% colnames(results)) {
    "adj_significant"
  } else {
    "significant"
  }
  
  # Create plot
  p <- ggplot2::ggplot(results, ggplot2::aes(x = mean, y = group)) +
    ggplot2::geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_lower, xmax = ci_upper), height = 0.2) +
    ggplot2::geom_point(ggplot2::aes(color = if(color_by_significance) .data[[sig_col]] else NULL), 
                        size = 3) +
    scale_y_discrete(limits = rev(levels(results$group)))+
    coord_cartesian(xlim = c(-1, 1))+
    ggplot2::labs(
      title = paste0("Normalised ROC-AUC Scores with Bootstrap Confidence Intervals",
                     ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                            "\n(adjusted for multiple testing)", "")),
      x = "Normalised ROC-AUC",
      y = NULL,
      subtitle = ifelse("adj_p_value" %in% colnames(results), 
                        paste0("Multiple testing correction: ", 
                               ifelse(any(results$adj_p_value != results$p_value), "Applied", "None")),
                        "")
    ) +
    ggplot2::theme_bw(base_size = 16) +
    ggplot2::theme(
      axis.text.y = ggplot2::element_text(size = 10),
      legend.position = "bottom"
    )
  
  # Add color scale if coloring by significance
  if (color_by_significance) {
    p <- p + ggplot2::scale_color_manual(
      values = c("FALSE" = "gray50", "TRUE" = "steelblue"),
      name = ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                    "Significant (Adjusted)", "Significant"),
      labels = c("FALSE" = "No", "TRUE" = "Yes")
    )
  }
  
  return(p)
}

```

This code runs the bootstrap confidence interval testing and
```{r Calculating bootstrap confidence intervals and creates confidence interval plot, echo =FALSE}
bootstrap_scores <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform') %>% dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')), 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = bootstrap_confidence_threshold,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH") 


bootstrap_scores_no_D <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform') %>% 
                                    dplyr::filter(SET %in% c('SET_1A','SET_B','SET_C'))
                                    , 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = bootstrap_confidence_threshold,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH") 

bootstrap_scores_ONLY_D <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform') %>% 
                                    dplyr::filter(SET %in% c('SET_D'))
                                    , 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = bootstrap_confidence_threshold,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH")

#Note, p-values are zero or 1 in most cases - anyhow, we can just indicate significance, I guess.

#Could include this plot as supplementary (?)
```

## Plots of results from binning
### Note, approach 2 has been removed, and approach 3 has been renamed approach 2

### Performance across intensity bins
```{r Creates heatmap to compare the median norm performance across all binning approaches and bins, echo=FALSE}
#
bin_classifier_df_temp <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  group_by(Gene_name_postrans, Approach_and_bin_id) %>%
  summarize(median_norm_roc = median(Ceiling_normalised_ROC)) %>% 
  ungroup() %>% 
  pivot_wider(id_cols = Approach_and_bin_id,
              values_from = median_norm_roc,
              names_from = Gene_name_postrans) %>% 
  as.data.frame() %>% 
  # Ordering columns to have proper gene order
  dplyr::select(Approach_and_bin_id, all_of(rev(gene_name_order))) %>% ### CHANGE TO gene_name_order_full_data when all classifiers have finished
  # Ordering rows to have original classifiers at top
  dplyr::slice(match(c('None_all', 'Approach1_lowerbin', 'Approach1_upperbin',
                       'Approach2_lowerbin', 'Approach2_upperbin',
                       'Approach3_lowerbin', 'Approach3_upperbin') , Approach_and_bin_id))

#
row_names <- bin_classifier_df_temp[,1]
bin_classifier_df <- bin_classifier_df_temp[,-1]
rownames(bin_classifier_df) <- row_names

#
bin_classifier_matrix <- as.matrix(bin_classifier_df)
  
#
pheatmap(bin_classifier_matrix,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         display_numbers = TRUE,
         number_format = '%.2f',
         na_col = 'grey',
         main = NA,
         fontsize = 8)
```
### Heatmaps of expression intensities
#### isoforms in pair collapsed into one
```{r Creates heatmap to compare log2 transformed median intensities across all bins with isoforms collapsed, echo=FALSE}
# Transfection threshold Intensity_MeanIntensity_MCHERRY_BACKCORR
shared_threshold <- 0.0005
unique_threshold <- bind_cols('SET' = c())

#
bin_classifier_df_temp <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  dplyr::mutate(Mean_intensity_across_isoforms = (MedianIntensity_DEx_postrans + MedianIntensity_WT_postrans)/2) %>% 
  #dplyr::select(Approach_and_bin_id, Gene_name_postrans, Replicate, MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans) %>% 
  #pivot_longer(cols = c(MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans),
  #             names_to = 'Isoform',
  #             values_to = 'MedianIntensity') %>% 
  #dplyr::mutate(Isoform = case_when(
  #  Isoform == 'MedianIntensity_DEx_postrans' ~ 'A',
  #  Isoform == 'MedianIntensity_WT_postrans' ~ 'B'
  #)) %>% 
  #dplyr::mutate(Approach_and_bin_id_and_isoform = paste0(Approach_and_bin_id,'_Iso',Isoform)) %>% 
#
  group_by(Gene_name_postrans, Approach_and_bin_id) %>%
  summarize(median_intensity_iso = median(Mean_intensity_across_isoforms)/shared_threshold) %>% 
  ungroup() %>% 
  dplyr::mutate(intensity_relative_to_detection_threshold = log2(median_intensity_iso)) %>% 
  pivot_wider(id_cols = Approach_and_bin_id,
              values_from = intensity_relative_to_detection_threshold,
              names_from = Gene_name_postrans) %>% 
  as.data.frame() %>% 
  # Ordering columns to have proper gene order
  dplyr::select(Approach_and_bin_id, all_of(rev(gene_name_order))) %>% ### CHANGE TO gene_name_order_full_data when all classifiers have finished
  # Ordering rows to have original classifiers at top
  dplyr::slice(match(c('None_all',
                       'Approach1_lowerbin','Approach1_upperbin',
                       'Approach2_lowerbin','Approach2_upperbin',
                       'Approach3_lowerbin','Approach3_upperbin') , Approach_and_bin_id))

#
row_names <- bin_classifier_df_temp[,1]
bin_classifier_df <- bin_classifier_df_temp[,-1]
rownames(bin_classifier_df) <- row_names

#
bin_classifier_matrix <- as.matrix(bin_classifier_df)

#
pheatmap(bin_classifier_matrix,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         display_numbers = TRUE,
         #legend_breaks = c(2^(0:ceiling(log2(max(bin_classifier_matrix)))),
        #                   round(max(bin_classifier_matrix),3)),
         number_format = '%.1f',
         na_col = 'grey',
         main = NA,
         fontsize = 9)
```
#### Isoforms kept separate
```{r Creates heatmap to compare log2 transformed median intensities across all bins, echo=FALSE}
# Transfection threshold Intensity_MeanIntensity_MCHERRY_BACKCORR
shared_threshold <- 0.0005
unique_threshold <- bind_cols('SET' = c())


#
bin_classifier_df_temp <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  dplyr::select(Approach_and_bin_id, Gene_name_postrans, Replicate, MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans) %>% 
  pivot_longer(cols = c(MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans),
               names_to = 'Isoform',
               values_to = 'MedianIntensity') %>% 
  dplyr::mutate(Isoform = case_when(
    Isoform == 'MedianIntensity_DEx_postrans' ~ 'A',
    Isoform == 'MedianIntensity_WT_postrans' ~ 'B'
  )) %>% 
  dplyr::mutate(Approach_and_bin_id_and_isoform = paste0(Approach_and_bin_id,'_Iso',Isoform)) %>% 
#
  group_by(Gene_name_postrans, Approach_and_bin_id_and_isoform) %>%
  summarize(median_intensity_iso = median(MedianIntensity)/shared_threshold) %>% 
  ungroup() %>% 
  dplyr::mutate(intensity_relative_to_detection_threshold = log2(median_intensity_iso)) %>% 
  pivot_wider(id_cols = Approach_and_bin_id_and_isoform,
              values_from = intensity_relative_to_detection_threshold,
              names_from = Gene_name_postrans) %>% 
  as.data.frame() %>% 
  # Ordering columns to have proper gene order
  dplyr::select(Approach_and_bin_id_and_isoform, all_of(rev(gene_name_order))) %>% ### CHANGE TO gene_name_order_full_data when all classifiers have finished
  # Ordering rows to have original classifiers at top
  dplyr::slice(match(c('None_all_IsoA','None_all_IsoB',
                       'Approach1_lowerbin_IsoA', 'Approach1_lowerbin_IsoB', 'Approach1_upperbin_IsoA', 'Approach1_upperbin_IsoB',
                       'Approach2_lowerbin_IsoA','Approach2_lowerbin_IsoB', 'Approach2_upperbin_IsoA','Approach2_upperbin_IsoB',
                       'Approach3_lowerbin_IsoA','Approach3_lowerbin_IsoB', 'Approach3_upperbin_IsoA','Approach3_upperbin_IsoB') , Approach_and_bin_id_and_isoform))

#
row_names <- bin_classifier_df_temp[,1]
bin_classifier_df <- bin_classifier_df_temp[,-1]
rownames(bin_classifier_df) <- row_names

#
bin_classifier_matrix <- as.matrix(bin_classifier_df)

#
pheatmap(bin_classifier_matrix,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         display_numbers = TRUE,
         #legend_breaks = c(2^(0:ceiling(log2(max(bin_classifier_matrix)))),
        #                   round(max(bin_classifier_matrix),3)),
         number_format = '%.1f',
         na_col = 'grey',
         main = NA,
         fontsize = 9)
```
#### Intensity difference expressed as absolute log2FC of the median intensity ratio between wt over dex. Calculated on training set for each replication of classifier, then used median as single score here
```{r Creates heatmap to absolute log2 foldchange in median intensity of isoforms wt above dex, echo=FALSE}
#
bin_classifier_df_temp <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  dplyr::mutate(abs_log2fc_median_intensity_difference = abs(log2(MedianIntensity_WT_postrans/MedianIntensity_DEx_postrans))) %>% 
  #dplyr::select(Approach_and_bin_id, Gene_name_postrans, Replicate, MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans) %>% 
  #pivot_longer(cols = c(MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans),
  #             names_to = 'Isoform',
  #             values_to = 'MedianIntensity') %>% 
  #dplyr::mutate(Isoform = case_when(
  #  Isoform == 'MedianIntensity_DEx_postrans' ~ 'A',
  #  Isoform == 'MedianIntensity_WT_postrans' ~ 'B'
  #)) %>% 
  #dplyr::mutate(Approach_and_bin_id_and_isoform = paste0(Approach_and_bin_id,'_Iso',Isoform)) %>% 
#
  group_by(Gene_name_postrans, Approach_and_bin_id) %>%
  summarize(median_intensity_iso = median(abs_log2fc_median_intensity_difference)) %>% 
  ungroup() %>% 
  dplyr::mutate(intensity_relative_to_detection_threshold = median_intensity_iso) %>% 
  pivot_wider(id_cols = Approach_and_bin_id,
              values_from = intensity_relative_to_detection_threshold,
              names_from = Gene_name_postrans) %>% 
  as.data.frame() %>% 
  # Ordering columns to have proper gene order
  dplyr::select(Approach_and_bin_id, all_of(rev(gene_name_order))) %>% ### CHANGE TO gene_name_order_full_data when all classifiers have finished
  # Ordering rows to have original classifiers at top
  dplyr::slice(match(c('None_all',
                       'Approach1_lowerbin','Approach1_upperbin',
                       'Approach2_lowerbin','Approach2_upperbin',
                       'Approach3_lowerbin','Approach3_upperbin') , Approach_and_bin_id))

#
row_names <- bin_classifier_df_temp[,1]
bin_classifier_df <- bin_classifier_df_temp[,-1]
rownames(bin_classifier_df) <- row_names

#
bin_classifier_matrix <- as.matrix(bin_classifier_df)

#
pheatmap(bin_classifier_matrix,
         cluster_rows = FALSE,
         cluster_cols = FALSE,
         display_numbers = TRUE,
         #legend_breaks = c(2^(0:ceiling(log2(max(bin_classifier_matrix)))),
        #                   round(max(bin_classifier_matrix),3)),
         number_format = '%.1f',
         na_col = 'grey',
         main = NA,
         fontsize = 9)
```
## Linear regression of intensity imbalance versus classifier performance using entire dataset as input no binning
#### The cells used for calculation were the once in the training set for each classifier iteration. Calculated as above but not replicate scaling.
```{r}
# CAN PROBABLY JUST RE-WRITE STUFF BELOW, TO FILTER TO ONLY HAVE NONE BINNING, AND THEN USE MEDIAN OF NORM ROC AUC
#colnames(combined_model_performance_all_posneg_relative)
control_labels <- combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::filter(BINNING_APPROACH == 'None') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  dplyr::mutate(abs_log2fc_median_intensity_difference = abs(log2(MedianIntensity_WT_postrans/MedianIntensity_DEx_postrans))) %>% 
  #dplyr::select(Approach_and_bin_id, Gene_name_postrans, Replicate, MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans) %>% 
  #pivot_longer(cols = c(MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans),
  #             names_to = 'Isoform',
  #             values_to = 'MedianIntensity') %>% 
  #dplyr::mutate(Isoform = case_when(
  #  Isoform == 'MedianIntensity_DEx_postrans' ~ 'A',
  #  Isoform == 'MedianIntensity_WT_postrans' ~ 'B'
  #)) %>% 
  #dplyr::mutate(Approach_and_bin_id_and_isoform = paste0(Approach_and_bin_id,'_Iso',Isoform)) %>% 
#
  group_by(Gene_name_postrans, Approach_and_bin_id) %>%
  summarize(median_intensity_iso = median(abs_log2fc_median_intensity_difference),
            median_norm_roc = median(Ceiling_normalised_ROC)) %>% 
  #
  left_join(x = ., y = bootstrap_scores, by = join_by('Gene_name_postrans' == 'group')) %>% 
  dplyr::mutate(control = if_else(Gene_name_postrans == 'PosControl' | Gene_name_postrans == 'NegControl', TRUE, FALSE)) %>% 
  dplyr::filter(control == TRUE)


combined_model_performance_all_posneg_relative %>% 
  dplyr::filter(!Gene_name_postrans %in% c('PosControl_BatchE','NegControl_BatchE')) %>% 
  dplyr::filter(Group == 'Isoform') %>% 
  dplyr::filter(BINNING_APPROACH == 'None') %>% 
  dplyr::mutate(Approach_and_bin_id = paste0(BINNING_APPROACH,'_',WHICH_BIN)) %>% 
  ungroup() %>% 
  dplyr::mutate(abs_log2fc_median_intensity_difference = abs(log2(MedianIntensity_WT_postrans/MedianIntensity_DEx_postrans))) %>% 
  #dplyr::select(Approach_and_bin_id, Gene_name_postrans, Replicate, MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans) %>% 
  #pivot_longer(cols = c(MedianIntensity_DEx_postrans, MedianIntensity_WT_postrans),
  #             names_to = 'Isoform',
  #             values_to = 'MedianIntensity') %>% 
  #dplyr::mutate(Isoform = case_when(
  #  Isoform == 'MedianIntensity_DEx_postrans' ~ 'A',
  #  Isoform == 'MedianIntensity_WT_postrans' ~ 'B'
  #)) %>% 
  #dplyr::mutate(Approach_and_bin_id_and_isoform = paste0(Approach_and_bin_id,'_Iso',Isoform)) %>% 
#
  group_by(Gene_name_postrans, Approach_and_bin_id) %>%
  summarize(median_intensity_iso = median(abs_log2fc_median_intensity_difference),
            median_norm_roc = median(Ceiling_normalised_ROC)) %>% 
  #
  left_join(x = ., y = bootstrap_scores, by = join_by('Gene_name_postrans' == 'group')) %>% 
  dplyr::mutate(control = if_else(Gene_name_postrans == 'PosControl' | Gene_name_postrans == 'NegControl', TRUE, FALSE)) %>% 
  #
  ggplot(aes(x = median_norm_roc, y = median_intensity_iso))+
  geom_hline(yintercept = 0, color = 'darkgrey')+
  geom_vline(xintercept = 0, color = 'darkgrey')+
  geom_point(aes(fill = adj_significant),shape = 21, size = 7, color = 'black', alpha = 0.8)+  #
  stat_poly_line(method = 'lm', se = FALSE)+
  stat_poly_eq(use_label(c('R2')), label.x = 0.5, label.y = 'top', size = 6.5)+
  geom_label_repel(data = control_labels %>% dplyr::filter(control == TRUE),
                   aes(label = Gene_name_postrans), box.padding = 0.4)+

  #scale_fill_viridis_c()+
  labs(title = 'mCherry intensity imbalance and classifier performance',
     x = 'Norm. ROC-AUC',
     y = 'Absolute log2FC(median intensity)',
     fill = 'Adjusted p\nsignificant?')+
  theme_bw(base_size = 16)
```
