---
title: "Identifying which features are describing isoform-specific behaviours"
author: "Peter Kjer Hansen"
date: "2025-04-01"
output:
  html_document:
    fig_width: 12
    fig_height: 5
---

# Introduction
Please set working directory to correct folders AND set thresholds for variable importance
```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "svg")

#packages
library(tidyverse)
library(caret)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(broom)
library(readxl)
library(ggpmisc) #For easy plots of coefficients on plots
library(lsr) #Contains cohensD() function
library(nnet) #Feedforward neural network
library(UpSetR) #Package for doing upset plots
library(ggrepel) #Pacakge for making repel text
library(scales) # Default ggplot colours

#Working directory
#Exon description dataset
Path_to_exon_description_sheet <- 'INSERT PATH TO SHEET WITH EXON DESCRIPTIONS'
File_with_exon_description_sheet <- 'INSERT FILE NAME OF .XLSX WITH EXON DESCRIPTIONS'
Event_sheet <- 'INSERT SHEET NAME'
LUMIER_sheet <- 'INSERT SHEET NAME'

# Model folders
#Postrans
Postransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON TRANSFECTED CELLS'
#Negtrans 10 percentile with rep aware sampling, No Golgin
Negtransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON NON-TRANSFECTED CELLS'

# Cell datasets and summaries
Cell_data_folder <- 'INSERT PATH TO FOLDER WITH .CSVS CONTAINING THE SINGLE CELL MEASUREMENTS'

# Bootstrap confidence threshold
bootstrap_confidence_threshold <- 0.99

### Thresholds for important variables
# Threshold for the contribution ratio (pos_trans / neg_trans). Higher is more stringent
ratio_threshold <- 2.6
# Threshold for the contribution ratio X contribution prop (positive) variable. Higher is more stringent
ratio_times_importance_threshold <- 1.5

#
transfection_threshold <- 0.00065
```

```{r ISoform pair descriptions, echo = FALSE}
# Replications of sampling + classifier training + assessment
#Pairs to be test for the various sets
#These are the actual isoform tests
PAIRS_1A <- c('PAIR_01','PAIR_02','PAIR_03','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10', 'PAIR_PosControl', 'PAIR_RAB5A')
PAIRS_1A_alternative_comps <- c('PAIR_03DExVSPanEx','PAIR_03bothEx','PAIR_03ExVsEx','PAIR_03Ex1VsBoth')
PAIRS_B <- c('PAIR_01','PAIR_02','PAIR_03','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10')
PAIRS_C <- c('PAIR_02','PAIR_04','PAIR_05','PAIR_06','PAIR_07','PAIR_08','PAIR_09','PAIR_10')
#
PAIRS_D_wo_01 <- c('PAIR_02','PAIR_05','PAIR_08','PAIR_09')
PAIRS_D_alternative_comps <- c('PAIR_01wtVS57','PAIR_01wtVS168','PAIR_01dex57VS168','PAIR_08DExVSaltEx','PAIR_08bothEx','PAIR_08ExVsEx','PAIR_08Ex1VsBoth')

```

```{r Function to load in the classifier performance and importance, echo=FALSE}
#
Replicate_performance_and_importance <- function(MODEL_FOLDER, SET, PAIR, TRANSFECTION_STATUS, PERCENTILE_CUTOFF = 0){
  if(TRANSFECTION_STATUS == 'POSITIVE'){
    load(paste0(MODEL_FOLDER,'/',SET,'_',PAIR))
  }
  if(TRANSFECTION_STATUS == 'NEGATIVE'){
    load(paste0(MODEL_FOLDER,'/NegTransModel_',SET,'_',PAIR))
  }
  #
  modeL_fit_and_tune <- function(variable){
    a <- variable$results %>%
      dplyr::filter(!is.na(ROC)) %>% 
      dplyr::arrange(desc(ROC)) %>% 
      dplyr::slice_head(n = 1) %>% 
      dplyr::mutate(size_decay_tune = paste0('size:',size,'_decay:',decay))
    return(a)
  }
  #
  variable_importance_ranking <- function(variable){
    variable_importance <- variable$variable_importance %>% 
      arrange(desc(Overall)) %>%
      rownames_to_column(var = 'Feature') %>% 
      as_tibble()
    
    rank <- seq(1, dim(variable_importance)[1])
    
    variable_importance <- bind_cols(variable_importance, 'Rank' = rank)
    return(variable_importance)
  }
  #
  n_cells <- function(variable){
    cell_count <- variable$training_data_intensity %>% 
    count()
    return(cell_count)
  }
  #
  
  ISOFORM_MODELS <- as.list(replicate_nnet[1,]) #Converts matrix rows into lists
  NEGATIVE_MODELS <- as.list(replicate_nnet[2,])
  POSITIVE_MODELS <- as.list(replicate_nnet[3,])
  
  #
  isoform_model_fit_and_tune <- lapply(ISOFORM_MODELS, FUN = modeL_fit_and_tune)
  isoform_variable_importance <- lapply(ISOFORM_MODELS, FUN = variable_importance_ranking)
  isoform_n_cells <- lapply(ISOFORM_MODELS, FUN = n_cells)
  #
  negative_fit_and_tune <- lapply(NEGATIVE_MODELS, FUN = modeL_fit_and_tune)
  negative_variable_importance <- lapply(NEGATIVE_MODELS, FUN = variable_importance_ranking)
  negative_n_cells <- lapply(NEGATIVE_MODELS, FUN = n_cells)
  #
  positive_fit_and_tune <- lapply(POSITIVE_MODELS, FUN = modeL_fit_and_tune)
  positive_variable_importance <- lapply(POSITIVE_MODELS, FUN = variable_importance_ranking)
  positive_n_cells <- lapply(POSITIVE_MODELS, FUN = n_cells)
  
  #
  iso_performance <- bind_rows(isoform_model_fit_and_tune, .id = 'Replicate')
  neg_performance <- bind_rows(negative_fit_and_tune, .id = 'Replicate')
  pos_performance <- bind_rows(positive_fit_and_tune, .id = 'Replicate') %>% 
    rename_with(~paste0(.,"_pos"), -Replicate)
  
  #
  iso_n <- bind_rows(isoform_n_cells, .id = 'Replicate')
  neg_n <- bind_rows(negative_n_cells, .id = 'Replicate')
  pos_n <- bind_rows(positive_n_cells, .id = 'Replicate')
  n_cells_all_models <- bind_rows(iso_n, neg_n, pos_n, .id = 'Group')%>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  ###
  pair_x_performance <- bind_rows(iso_performance, neg_performance, bind_rows(positive_fit_and_tune, .id = 'Replicate'),.id = 'Group') %>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  #
  
  ###
  relative_performance <- full_join(x = iso_performance, y = neg_performance, by = c('Replicate'), suffix = c('_iso', '_neg')) %>% 
    full_join(x = ., y = pos_performance, by = c('Replicate')) %>% 
    dplyr::mutate('ROC_difference_from_neg' = ROC_iso - ROC_neg,
                  'ROC_difference_from_pos' = ROC_iso - ROC_pos,
                  'ROC_difference_pos_from_neg' = ROC_pos - ROC_neg)
  
  #
  
  ###
  number_of_classifier_iterations <- length(isoform_variable_importance)
  number_of_features <- length(unique(isoform_variable_importance[[1]]$Feature))
  #
  iso_importance <- bind_rows(isoform_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance <- bind_rows(negative_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance_reduced <- neg_importance %>% 
    dplyr::select(Feature, Rank_sum, Rank_avg, Rank_median, Rank_90_10, Rank_95_05, Overall_sum, Overall_avg, Overall_sd)
  
    #
  iso_neg_comb_importance <- dplyr::full_join(x = iso_importance, y = neg_importance_reduced, by = c('Feature'), suffix = c('','_neg')) %>% 
    dplyr::mutate('Rank_median_difference' = Rank_median_neg - Rank_median,
                  'Rank_sum_difference' = Rank_sum_neg - Rank_sum,
                  'Rank_90_10_difference' = Rank_90_10_neg - Rank_90_10,
                  'Rank_95_05_difference' = Rank_95_05_neg - Rank_95_05)
  
  
  #
  
  results_list <- list('performance' = pair_x_performance, 'SET' = SET, 'PAIR' = PAIR, 'relative_performance' = relative_performance, 'TRANSFECTION_STATUS' = TRANSFECTION_STATUS, 'PERCENTILE_CUTOFF' = PERCENTILE_CUTOFF,
                       'var_importance_iso' = iso_importance, 'var_importance_neg' = negative_variable_importance, 'var_importance_pos' = positive_variable_importance,
                       'var_importance_iso_w_contrast' = iso_neg_comb_importance, 'n_cells' = n_cells_all_models)
  return(results_list)
}
```

```{r Loading Positive transfectant models, echo = FALSE}
#Reading in all the models (For 1, A, 1A, B, C, and E)
#Positive transfectant models
#####

#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set 1A alternative comparisons
for(i in PAIRS_1A_alternative_comps){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')

  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set B
for(i in PAIRS_B){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_B',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set C
for(i in PAIRS_C){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_C',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set D
for(i in PAIRS_D_wo_01){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_D',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set D, alternative comparisons
for(i in PAIRS_D_alternative_comps){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_D',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
```

```{r Loading negative transfectant models 10 percentile, echo = FALSE}
#Reading in all the models (For 1, A, 1A, B, C, and E)
#Negative transfectant models
#####

#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set 1A alternative comparisons
for(i in PAIRS_1A_alternative_comps){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)

  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set B
for(i in PAIRS_B){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_B',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#Set C
for(i in PAIRS_C){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_C',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#
for(i in PAIRS_D_wo_01){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_D',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
#SET D, ALTERNATIVE COMPARISONS
for(i in PAIRS_D_alternative_comps){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_D',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}

```

```{r Loading exon descriptions, echo = FALSE}
#Exon description
Exon_descriptions <- readxl::read_xlsx(path = paste0(Path_to_exon_description_sheet, File_with_exon_description_sheet),
                                       sheet = Event_sheet) %>% 
  dplyr::mutate('microexon' = Exon_length_NT <= 30) %>% 
  dplyr::mutate(Gene_name_Rclassifier = case_when( #Note, currently because names in SET D are marked w. asteriks, they have to be so in this exon description file. But excel didn't like starting the name w. an asteriks.
    Gene_name_Rclassifier == 'ATXN2' ~ '*ATXN2', #Only done for the isoform pairs that are not recurring
    Gene_name_Rclassifier == 'EVI5' ~ '*EVI5',
    Gene_name_Rclassifier == 'PPFIA1' ~ '*PPFIA1',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExA' ~ 'CLASP1_ExA_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExB' ~ 'CLASP1_noEx_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExA' ~ 'CLASP1_ExA_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExB' ~ 'CLASP1_noEx_vs_ExB',
    .default = Gene_name_Rclassifier))

Exon_descriptions_reduced <- Exon_descriptions %>% 
  dplyr::select(microexon, Splice_event_enriched_in_neural_tissue, Splice_event_enriched_in_pancreatic_islet_cells, Enrichment_comment, Exon_length_NT, Gene_name_Rclassifier, Exon_name_Rclassifier, EVENT_ID_vastDB, Location_in_protein) #%>% 
  #dplyr::filter(!c(Gene_name_Rclassifier == 'VAV2')) #Current_naming_doesn't_work_well_with_genes_with_multiple_exons

### ISOFORM_PAIRS_EXCLUDE
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_DOUBLES <- c('VAV2','*SH3KBP1_D/E','*OCRL_D/E','*SH3GLB1_D/E')
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_INTENSITY <- c('VAV2','PACSIN2') ##THIS DEFINES WHICH ISOFORM PAIRS ARE EXCLUDED.

```

```{r combining absolute classifier outputs into proper datasets, echo = FALSE}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set 1A
combined_model_performance_SET_1A <- bind_rows(mget(ls(pattern = 'model_performance_SET_1A_PAIR'))) #Will contain both SET_1A normal comps and alternative CLASP1 comparisons
rm(list = ls(pattern = 'model_performance_SET_1A_PAIR'))
#Set B
combined_model_performance_SET_B <- bind_rows(mget(ls(pattern = 'model_performance_SET_B_PAIR')))
rm(list = ls(pattern = 'model_performance_SET_B_PAIR'))
#Set C
combined_model_performance_SET_C <- bind_rows(mget(ls(pattern = 'model_performance_SET_C_PAIR')))
rm(list = ls(pattern = 'model_performance_SET_C_PAIR'))
#Set D
combined_model_performance_SET_D <- bind_rows(mget(ls(pattern = 'model_performance_SET_D_PAIR')))
rm(list = ls(pattern = 'model_performance_SET_D_PAIR'))

#All
combined_model_performance_all <- bind_rows(mget(ls(pattern = 'combined_model_performance_SET_'))) %>%  #WRITE CASE_WHEN TO GIVE ALL SET + PAIR COMBINATIONS THEIR GENE NAME (COULD POTENTIALLY BE GENE + EXON ID -> ALTHOUGH COMBINATIONS GET TRICKY STILL)
  dplyr::mutate('Gene_name' = case_when(
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_1' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    #
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    #
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_01' ~ 'ANK2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_02' ~ 'Apbb1',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03' ~ 'CLASP1_noEx_vs_ExA', #
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03bothEx' ~ 'CLASP1_noEx_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03DExVSPanEx' ~ 'CLASP1_noEx_vs_ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03Ex1VsBoth' ~ 'CLASP1_ExA_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_03ExVsEx' ~ 'CLASP1_ExA_vs_ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_05' ~ 'DCTN1',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_06' ~ 'VAV2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_07' ~ 'FBXW11',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_08' ~ 'NUMB',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_10' ~ 'SPAG9',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_RAB5A' ~ 'NegControl',
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_PosControl' ~ 'PosControl',
    #
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_01' ~ 'AP1G1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_02' ~ 'DAAM1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_03' ~ 'DNM1L',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_04' ~ 'DYNC1LI2',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_05' ~ 'EEA1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_06' ~ 'KIF3A',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_07' ~ 'ROBO1',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_08' ~ 'SCYL2',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_09' ~ 'SRC',
    SET == 'SET_B' & ISOFORM_PAIR == 'PAIR_10' ~ 'TNK2',
    #
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_02' ~ 'CLTA',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_04' ~ 'DNM2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_05' ~ 'Dnm2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_06' ~ 'Dnm3',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_07' ~ 'OCRL',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_08' ~ 'PACSIN2',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_09' ~ 'SH3GLB1',
    SET == 'SET_C' & ISOFORM_PAIR == 'PAIR_10' ~ 'SH3KBP1',
    #
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01dex57VS168' ~ '*APP_noEx_vs_ExA', #Ex168nt is ExA, Ex57nt is ExB
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01wtVS168' ~ '*APP_noEx_vs_ExA+ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_01wtVS57' ~ '*APP_ExA_vs_ExA+ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_02' ~ '*ATXN2',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_03' ~ '*EVI5',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_04' ~ '*OCRL_D/E',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_05' ~ '*PPFIA1',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_06' ~ '*SH3GLB1_D/E',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_07' ~ '*SH3KBP1_D/E',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08' ~ '*VAV2_noEx_vs_ExA', #ExA (is likely the downstream micro-exon), ExB is upstream micro-exon (I think)
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08bothEx' ~ '*VAV2_noEx_vs_ExA+ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08DExVSaltEx' ~ '*VAV2_noEx_vs_ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08Ex1VsBoth' ~ '*VAV2_ExA_vs_ExA+ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_08ExVsEx' ~ '*VAV2_ExA_vs_ExB',
    SET == 'SET_D' & ISOFORM_PAIR == 'PAIR_09' ~ '*VAV2_ExB_vs_ExA+ExB'
  )) %>% 
  #left_join(., y = SUMMARY_of_all_sample_ratios, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) %>% 
  left_join(., y = Exon_descriptions_reduced, by = join_by('Gene_name' == 'Gene_name_Rclassifier')) %>% 
  #The fusion doesn't work perfectly for genes with multiple events - the line below removes an unwanted duplication of the VAV2 data (NOTE, THIS IS WHAT GIVES RISE TO THE MANY-TO-MANY RELATIONSHIP)
  dplyr::filter(!c(SET == 'SET_1A' & Gene_name == 'VAV2' & Exon_name_Rclassifier == 'ExB')) %>% 
  #
  dplyr::mutate(microexon = case_when( #Hacky way of making all events have microexon, yes/no label
    word(Gene_name, 1, 1, sep = fixed('_')) == '*APP' ~ FALSE,
    word(Gene_name, 1, 1, sep = fixed('_')) == '*VAV2' ~ TRUE,
    word(Gene_name, 1, 1, sep = fixed('_')) == 'CLASP1' ~ TRUE,
    .default = microexon))
#


#Dataframe w. the gene name SET + PAIR combination
gene_ids_match <- combined_model_performance_all %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB) %>%
  unique()

#Dataframe w. n used for classifier and the gene names
n_used_for_classifier <- combined_model_performance_all %>% 
  dplyr::select(n, Gene_name) %>% 
  unique() %>% 
  dplyr::group_by(Gene_name) %>% 
  summarize(n = mean(n))

```

```{r creating relative ROC that compares negative transfectant and positive transfectant ROCs, echo = FALSE}
#Splitting the combined ROC dataset according to transfection status
#Positive transfectants
combined_model_performance_all_postrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE')
#Negative transfectants
combined_model_performance_all_negtrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE')

#Joining positive and negative transfectants in a wide-format
combined_model_performance_all_posneg_relative <- full_join(x = combined_model_performance_all_postrans, y = combined_model_performance_all_negtrans,
                                                            by = join_by(SET, ISOFORM_PAIR, Group, Replicate),
                                                            suffix = c('_postrans', '_negtrans')) %>%
  # Creating ROC relative column (pos - neg). Can be negative.
  dplyr::mutate(ROC_posneg_relative = ROC_postrans - ROC_negtrans,
                tmp_norm_ROC = (ROC_postrans - ROC_negtrans)/(1 - ROC_negtrans),
                Ceiling_normalised_ROC = if_else(tmp_norm_ROC >= 0, tmp_norm_ROC, (ROC_postrans - ROC_negtrans)/(1 - ROC_postrans)))
    
```

### Testing ceiling normalised ROC-AUC distributions for isoform classifiers using boot strap confidence intervals

```{r Function to perform bootstrap confidence interval caluclations, echo = FALSE}
#' Bootstrap Test for Pre-Normalized ROC Scores with Group Support
#'
#' This function calculates bootstrap confidence intervals for normalized ROC scores
#' that have already been calculated. It supports grouping by a variable (e.g., gene name).
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param group_value Value to filter by in the group column (e.g., specific gene name)
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#'
#' @return A list containing bootstrap statistics and test results
#'
#' @examples
#' # Example with pre-calculated normalized values
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2))
#' )
#' result <- bootstrap_norm_roc_grouped(data, "norm_roc", "Gene_name", "Gene1")
#' print(result)
#'
bootstrap_norm_roc_grouped <- function(data, 
                                       norm_col = "norm_roc", 
                                       group_col = NULL,
                                       group_value = NULL,
                                       conf_level = 0.95,
                                       n_bootstrap = 2000,
                                       one_sided = TRUE) {
  
  # Require boot package
  if (!requireNamespace("boot", quietly = TRUE)) {
    stop("Please install the 'boot' package: install.packages('boot')")
  }
  
  # Filter data by group if specified
  if (!is.null(group_col) && !is.null(group_value)) {
    if (!(group_col %in% colnames(data))) {
      stop(paste("Group column", group_col, "not found in data"))
    }
    data <- data[data[[group_col]] == group_value, ]
    if (nrow(data) == 0) {
      stop(paste("No data found for", group_col, "=", group_value))
    }
  }
  
  # Check if norm_col exists
  if (!(norm_col %in% colnames(data))) {
    stop(paste("Normalized score column", norm_col, "not found in data"))
  }
  
  # Extract normalized scores
  norm_scores <- data[[norm_col]]
  
  # Function for bootstrapping
  boot_func <- function(data, indices) {
    return(mean(data[indices]))
  }
  
  # Perform bootstrap
  boot_result <- boot::boot(norm_scores, boot_func, R = n_bootstrap)
  
  # Calculate confidence interval
  if (one_sided) {
    # One-sided interval (lower bound only)
    alpha <- 1 - conf_level
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound of percentile interval
    upper_bound <- Inf
  } else {
    # Two-sided interval
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound
    upper_bound <- ci$percent[5]  # Upper bound
  }
  
  # Determine if zero is in the confidence interval
  zero_in_ci <- (lower_bound <= 0 && upper_bound >= 0)
  
  # Create summary results
  result <- list(
    mean = mean(norm_scores),
    median = median(norm_scores),
    sd = sd(norm_scores),
    ci_lower = lower_bound,
    ci_upper = ifelse(one_sided, Inf, upper_bound),
    one_sided = one_sided,
    conf_level = conf_level,
    zero_in_ci = zero_in_ci,
    significant = !zero_in_ci,
    n_iterations = length(norm_scores),
    n_bootstrap = n_bootstrap,
    group_col = group_col,
    group_value = group_value,
    raw_scores = norm_scores,
    boot_result = boot_result
  )
  
  return(result)
}

#' Run Bootstrap Tests for Multiple Groups
#'
#' This function runs bootstrap tests for multiple groups and returns results in a data frame
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#' @param adjust_method Method for multiple testing correction (default "BH"). Options include 
#'                     "holm", "hochberg", "hommel", "bonferroni", "BH", "BY", "fdr", "none"
#'
#' @return A data frame with bootstrap test results for each group, including adjusted p-values
#'
#' @examples
#' # Example with pre-calculated normalized values for multiple genes
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2", "Gene3"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2), rnorm(50, 0.15, 0.15))
#' )
#' results <- bootstrap_multiple_groups(data, "norm_roc", "Gene_name")
#' print(results)
#'
bootstrap_multiple_groups <- function(data, 
                                      norm_col = "norm_roc", 
                                      group_col,
                                      conf_level = 0.95,
                                      n_bootstrap = 2000,
                                      one_sided = TRUE,
                                      adjust_method = "BH") {
  
  # Get unique groups
  groups <- unique(data[[group_col]])
  
  # Create empty results data frame
  results <- data.frame(
    group = character(),
    mean = numeric(),
    median = numeric(),
    sd = numeric(),
    ci_lower = numeric(),
    ci_upper = numeric(),
    p_value = numeric(),
    significant = logical(),
    adj_p_value = numeric(),
    adj_significant = logical(),
    n_iterations = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Loop through groups
  group_results <- list()
  p_values <- numeric(length(groups))
  
  for (i in seq_along(groups)) {
    group <- groups[i]
    # Run bootstrap test
    boot_result <- bootstrap_norm_roc_grouped(
      data = data,
      norm_col = norm_col,
      group_col = group_col,
      group_value = group,
      conf_level = conf_level,
      n_bootstrap = n_bootstrap,
      one_sided = one_sided
    )
    
    # Calculate p-value from bootstrap distribution
    if (one_sided) {
      # For one-sided test, calculate p-value as proportion of bootstrap values <= 0
      p_value <- mean(boot_result$boot_result$t <= 0)
    } else {
      # For two-sided test, calculate p-value based on whether 0 is in the CI
      # This is approximate but aligns with the confidence interval approach
      z_stat <- boot_result$mean / (boot_result$sd / sqrt(boot_result$n_iterations))
      p_value <- if (boot_result$mean >= 0) 2 * pnorm(-abs(z_stat)) else 2 * pnorm(-abs(z_stat))
    }
    
    p_values[i] <- p_value
    
    # Store result
    group_results[[i]] <- data.frame(
      group = group,
      mean = boot_result$mean,
      median = boot_result$median,
      sd = boot_result$sd,
      ci_lower = boot_result$ci_lower,
      ci_upper = ifelse(one_sided, Inf, boot_result$ci_upper),
      p_value = p_value,
      significant = boot_result$significant,
      n_iterations = boot_result$n_iterations
    )
  }
  
  # Adjust p-values for multiple testing
  adj_p_values <- p.adjust(p_values, method = adjust_method)
  
  # Combine results
  results <- do.call(rbind, group_results)
  results$adj_p_value <- adj_p_values
  results$adj_significant <- results$adj_p_value < (1 - conf_level)
  
  # Return results
  return(results)
}

#' Visualize Bootstrap Distribution
#'
#' Creates a histogram of bootstrap means with confidence interval
#'
#' @param boot_result Result from bootstrap_norm_roc_grouped function
#' @param bins Number of histogram bins (default 30)
#'
#' @return A ggplot2 object
#'
plot_bootstrap_dist <- function(boot_result, bins = 30) {
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Extract bootstrap samples
  t_values <- boot_result$boot_result$t
  
  # Create dataframe for plotting
  df <- data.frame(value = t_values)
  
  # Determine title suffix based on grouping
  group_suffix <- ""
  if (!is.null(boot_result$group_col) && !is.null(boot_result$group_value)) {
    group_suffix <- paste(" for", boot_result$group_col, "=", boot_result$group_value)
  }
  
  # Create plot
  p <- ggplot2::ggplot(df, ggplot2::aes(x = value)) +
    ggplot2::geom_histogram(bins = bins, fill = "steelblue", color = "white", alpha = 0.7) +
    ggplot2::geom_vline(xintercept = boot_result$ci_lower, color = "red", linetype = "dashed") +
    ggplot2::geom_vline(xintercept = 0, color = "black", linetype = "solid") +
    ggplot2::labs(
      title = paste0("Bootstrap Distribution of Normalized ROC Score", group_suffix),
      subtitle = paste0(
        ifelse(boot_result$one_sided, "One-sided ", "Two-sided "), 
        boot_result$conf_level * 100, "% CI: [", 
        round(boot_result$ci_lower, 4), ", ", 
        ifelse(boot_result$one_sided, "∞", round(boot_result$ci_upper, 4)), "]"
      ),
      x = "Normalized ROC Score",
      y = "Frequency",
      caption = paste("Mean:", round(boot_result$mean, 4), 
                      "| Significant:", boot_result$significant)
    ) +
    ggplot2::theme_minimal()
  
  return(p)
}

#' Create Forest Plot of Bootstrap Results
#'
#' Creates a forest plot of bootstrap results for multiple groups
#'
#' @param results Data frame from bootstrap_multiple_groups function
#' @param sort_by Column to sort by (default "mean")
#' @param decreasing Logical; if TRUE, sorts in decreasing order (default TRUE)
#' @param color_by_significance Logical; if TRUE, colors points by significance (default TRUE)
#'
#' @return A ggplot2 object
#'
plot_forest <- function(results, 
                        sort_by = "mean", 
                        decreasing = TRUE,
                        color_by_significance = TRUE,
                        use_adjusted_significance = TRUE) {
  
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Sort results
  results <- results[order(results[[sort_by]], decreasing = decreasing), ]
  
  # Make sure group is a factor in the right order for plotting
  results$group <- factor(results$group, levels = results$group)
  
  # Determine which significance column to use
  sig_col <- if(use_adjusted_significance && "adj_significant" %in% colnames(results)) {
    "adj_significant"
  } else {
    "significant"
  }
  
  # Create plot
  p <- ggplot2::ggplot(results, ggplot2::aes(x = mean, y = group)) +
    ggplot2::geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_lower, xmax = ci_upper), height = 0.2) +
    ggplot2::geom_point(ggplot2::aes(color = if(color_by_significance) .data[[sig_col]] else NULL), 
                        size = 3) +
    scale_y_discrete(limits = rev(levels(results$group)))+
    ggplot2::labs(
      title = paste0("Normalized ROC Scores with Bootstrap Confidence Intervals",
                     ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                            "\n(adjusted for multiple testing)", "")),
      x = "Normalized ROC Score",
      y = NULL,
      subtitle = ifelse("adj_p_value" %in% colnames(results), 
                        paste0("Multiple testing correction: ", 
                               ifelse(any(results$adj_p_value != results$p_value), "Applied", "None")),
                        "")
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      axis.text.y = ggplot2::element_text(size = 10),
      legend.position = "bottom"
    )
  
  # Add color scale if coloring by significance
  if (color_by_significance) {
    p <- p + ggplot2::scale_color_manual(
      values = c("FALSE" = "gray50", "TRUE" = "steelblue"),
      name = ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                    "Significant (Adjusted)", "Significant"),
      labels = c("FALSE" = "No", "TRUE" = "Yes")
    )
  }
  
  return(p)
}

# Example usage:
# # Create sample data with pre-calculated normalized ROC values
# set.seed(123)
# data <- data.frame(
#   Gene_name = rep(c("Gene1", "Gene2", "Gene3", "Gene4"), each = 50),
#   norm_roc = c(rnorm(50, 0.3, 0.1), 
#               rnorm(50, -0.1, 0.2), 
#               rnorm(50, 0.15, 0.15),
#               rnorm(50, 0.05, 0.1))
# )
# 
# # Test a single gene
# result_gene1 <- bootstrap_norm_roc_grouped(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name",
#   group_value = "Gene1"
# )
# print(result_gene1)
# plot1 <- plot_bootstrap_dist(result_gene1)
# print(plot1)
# 
# # Test all genes
# results_all <- bootstrap_multiple_groups(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name"
# )
# print(results_all)
# 
# # Create forest plot
# plot2 <- plot_forest(results_all)
# print(plot2)

# Remove a specific item from legend
# If you need to remove an item from a ggplot2 legend (such as color), 
# you can use the following approach after creating your plot:

# Example:
# p <- plot_forest(results_all, use_adjusted_significance = TRUE)
# 
# # To remove the color legend completely:
# p <- p + ggplot2::theme(legend.position = "none")
# 
# # To keep the legend but remove specific guides:
# p <- p + ggplot2::guides(color = "none")
# 
# # To create a table of results
# library(knitr)
# results_table <- results_all[, c("group", "mean", "ci_lower", "ci_upper", 
#                                 "p_value", "adj_p_value", "adj_significant")]
# results_table <- results_table[order(results_table$adj_p_value), ]
# kable(results_table, digits = 4)
# 
# print(p)
```

This code runs the bootstrap confidence interval testing so we can select statisticallyt signfiicant isos
```{r Calculating bootstrap confidence intervals and creates confidence interval plot, echo=FALSE}
bootstrap_scores <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform'), 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = 0.99,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH") 

#Note, p-values are zero or 1 in most cases - anyhow, we can just indicate significance, I guess.

#Could include this plot as supplementary (?)
```


```{r Loading variable importance classifier data, echo = FALSE}
#Variable importance
combined_variable_importance_set_1A <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR'))
#B
combined_variable_importance_set_B <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_B_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_B_PAIR'))
#C
combined_variable_importance_set_C <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_C_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_C_PAIR'))
#D
combined_variable_importance_set_D <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_D_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_D_PAIR'))
#
combined_variable_importance_all <- bind_rows(mget(ls(pattern = 'combined_variable_importance_set_'))) %>%
  left_join(x = ., y = gene_ids_match, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) 

#
combined_overall <- combined_variable_importance_all %>% 
  ungroup() %>% 
  group_by(Gene_name, TRANSFECTION_STATUS) %>% 
  summarize('Combined_overall' = sum(Overall_avg),
            'Combined_overall_neg' = sum(Overall_avg_neg))%>% 
  dplyr::arrange(Combined_overall)


combined_variable_importance_all_w_overall <- combined_variable_importance_all %>% 
  left_join(., x = combined_overall, by = join_by('Gene_name' == 'Gene_name', 'TRANSFECTION_STATUS' == 'TRANSFECTION_STATUS')) %>%
  dplyr::mutate('contribution_prop' = (Overall_avg/Combined_overall)*100,
                'contribution_prop_sd' = (Overall_sd/Combined_overall)*100,
                'contribution_prop_neg' = (Overall_avg_neg/Combined_overall_neg)*100,
                'contribution_prop_neg_sd' = (Overall_sd_neg/Combined_overall_neg)*100)

# Combining the variable importance data for negtrans and postrans in a wider format
# Positive transfectants
combined_variable_importance_all_w_overall_postrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)
# Negative transfectants
combined_variable_importance_all_w_overall_negtrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)

# Combined positive and negative transfectants
combined_variable_importance_all_w_overall_posneg <- combined_variable_importance_all_w_overall_postrans %>% 
  # Joining variable importance for postrans and negtrans
  dplyr::left_join(x = ., y = combined_variable_importance_all_w_overall_negtrans, by = join_by(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, Feature), suffix = c('_pos', '_neg')) %>% 
  # Introducing the contribution proportion ratio (postrans/negtrans)
  dplyr::mutate(contribution_prop_ratio = contribution_prop_pos/contribution_prop_neg,
                contribution_prop_ratio_negcontrol = contribution_prop_negcontrol_pos/contribution_prop_negcontrol_neg,
                ratio_times_importance = contribution_prop_ratio * contribution_prop_pos,
                noteworthy_feature = if_else(ratio_times_importance >= ratio_times_importance_threshold & contribution_prop_ratio > ratio_threshold, TRUE, FALSE)) %>% 
  # Add p-values from the bootstrapping confidence intervals
    left_join(x = .,
            y = bootstrap_scores %>% dplyr::select(group, adj_p_value, adj_significant),
            by = join_by('Gene_name' == 'group'))

```

```{r xy plot of ratio x contribution prop versus contribution prop positive, echo =FALSE}
#Importance plot for controls 
combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name %in% c('NegControl', 'PosControl')) %>% 
    ggplot(aes(x = contribution_prop_ratio, y = contribution_prop_ratio * contribution_prop_pos)) +
    geom_segment(aes(x = ratio_threshold, y = ratio_times_importance_threshold, 
                     xend = Inf, yend = ratio_times_importance_threshold), color = 'red', linewidth = 0.7) +
    geom_segment(aes(x = ratio_threshold, y = ratio_times_importance_threshold, 
                     xend = ratio_threshold, yend = Inf), color = 'red', linewidth = 0.7) +
    geom_point(aes(fill = noteworthy_feature), shape = 21, size = 5, color = 'black', alpha = 0.8)+
    scale_y_continuous(transform = 'log2',
                       limits = c(0.03125,32)) +
    coord_cartesian(xlim = c(0,7))+
    xlab('Contribution ratio') +
    labs(fill = 'Noteworthy\nfeature') +
    ylab('Feature contribution (%)\nx\nContribution ratio') +
    ggtitle(paste('Identifying "Noteworthy" features')) +
    theme_bw(base_size = 16)+
  facet_wrap(~Gene_name)

```

```{r Function for generating importance plots for single isoforms, echo=FALSE}
generate_gene_plots <- function(IMPORTANCE_DATA, 
                                CELL_DATA, 
                                gene_name,
                                ratio_threshold = 1, 
                                ratio_times_importance_threshold = 1,
                                n = 10) {
  
  library(dplyr)
  library(ggplot2)
  library(purrr)
  # Create empty list to store plots
  plot_list <- list()
  
  # Filter data for the specified gene
  gene_data <- IMPORTANCE_DATA %>% 
    dplyr::filter(Gene_name == gene_name)
  
  # 1. Generate the main importance plot
  main_plot <- gene_data %>% 
    ggplot(aes(x = contribution_prop_ratio, y = contribution_prop_ratio * contribution_prop_pos)) +
    geom_segment(aes(x = ratio_threshold, y = ratio_times_importance_threshold, 
                     xend = Inf, yend = ratio_times_importance_threshold), color = 'red', linewidth = 0.7) +
    geom_segment(aes(x = ratio_threshold, y = ratio_times_importance_threshold, 
                     xend = ratio_threshold, yend = Inf), color = 'red', linewidth = 0.7) +
    geom_point(aes(fill = noteworthy_feature), shape = 21, size = 4, color = 'black', alpha = 0.8)+
    scale_y_continuous(transform = 'log2',
                       limits = c(0.03125,32)) +
    coord_cartesian(xlim = c(0,7))+
    xlab('Contribution ratio') +
    labs(fill = 'Noteworthy\nfeature') +
    ylab('Feature contribution (%)\nx\nContribution ratio') +
    ggtitle(paste('"Noteworthy" features for', gene_name)) +
    theme_bw(base_size = 16) +
    facet_wrap(~Gene_name)
  
  # Add to plot list
  plot_list$main_importance_plot <- main_plot
  
  # 2. Generate bar plot of top n features with highest ratio_times_importance
  # Filter for noteworthy features and sort by ratio_times_importance
  top_features_data <- gene_data %>%
    dplyr::filter(noteworthy_feature == TRUE) %>%
    dplyr::mutate(ratio_times_importance = contribution_prop_ratio * contribution_prop_pos) %>%
    dplyr::arrange(desc(ratio_times_importance)) %>%
    dplyr::slice_head(n = n)
  
  # Create the bar plot
  if (nrow(top_features_data) > 0) {
    feature_bar_plot <- top_features_data %>%
      ggplot(aes(x = reorder(Feature, ratio_times_importance), y = ratio_times_importance)) +
      geom_bar(stat = "identity", fill = "steelblue") +
      geom_hline(yintercept = ratio_times_importance_threshold, color = 'red', linewidth = 0.8)+
      scale_y_continuous(transform = 'log2',
                       limits = c(1,32)
                         ) +
      #coord_cartesian(xlim = c(1,32))+
      coord_flip() +
      #     coord_cartesian(ylim = c(1,32))+
      xlab("Feature") +
      ylab("Feature contribution (%) x Contribution ratio") +
      ggtitle(paste("Top", n, "'Noteworthy' features for", gene_name)) +
      theme_bw(base_size = 16)
    
    plot_list$top_features_bar_plot <- feature_bar_plot
  } else {
    # Add empty plot with message if no noteworthy features
    plot_list$top_features_bar_plot <- ggplot() + 
      annotate("text", x = 0.5, y = 0.5, label = "No noteworthy features found") +
      theme_bw(base_size = 16)
  }
  
  # 3. Generate dot plots for top features vs MCHERRY intensity
  # Filter CELL_DATA for the specific gene
  cell_gene_data <- CELL_DATA %>%
    dplyr::mutate('Gene_name' = case_when(
      SET_PAIR == 'SET_1_PAIR_01' ~ 'ANK2',
      SET_PAIR == 'SET_1_PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
      SET_PAIR == 'SET_1_PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
      SET_PAIR == 'SET_1_PAIR_08' ~ 'NUMB',
      SET_PAIR == 'SET_1_PAIR_09' ~ 'SNX2',
      #
      SET_PAIR == 'SET_A_PAIR_01' ~ 'ANK2',
      SET_PAIR == 'SET_A_PAIR_03' ~ 'CLASP1_noEx_vs_ExA',
      SET_PAIR == 'SET_A_PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
      SET_PAIR == 'SET_A_PAIR_08' ~ 'NUMB',
      SET_PAIR == 'SET_A_PAIR_09' ~ 'SNX2',
      #
      SET_PAIR == 'SET_1A_PAIR_01' ~ 'ANK2',
      SET_PAIR == 'SET_1A_PAIR_02' ~ 'Apbb1',
      SET_PAIR == 'SET_1A_PAIR_03' ~ 'CLASP1_noEx_vs_ExA', #
      SET_PAIR == 'SET_1A_PAIR_03bothEx' ~ 'CLASP1_noEx_vs_ExA+ExB',
      SET_PAIR == 'SET_1A_PAIR_03DExVSPanEx' ~ 'CLASP1_noEx_vs_ExB',
      SET_PAIR == 'SET_1A_PAIR_03Ex1VsBoth' ~ 'CLASP1_ExA_vs_ExA+ExB',
      SET_PAIR == 'SET_1A_PAIR_03ExVsEx' ~ 'CLASP1_ExA_vs_ExB',
      SET_PAIR == 'SET_1A_PAIR_04' ~ 'CLASP1_ExB_vs_ExA+ExB',
      SET_PAIR == 'SET_1A_PAIR_05' ~ 'DCTN1',
      SET_PAIR == 'SET_1A_PAIR_06' ~ 'VAV2',
      SET_PAIR == 'SET_1A_PAIR_07' ~ 'FBXW11',
      SET_PAIR == 'SET_1A_PAIR_08' ~ 'NUMB',
      SET_PAIR == 'SET_1A_PAIR_09' ~ 'SNX2',
      SET_PAIR == 'SET_1A_PAIR_10' ~ 'SPAG9',
      SET_PAIR == 'SET_1A_PAIR_RAB5A' ~ 'NegControl',
      SET_PAIR == 'SET_1A_PAIR_PosControl' ~ 'PosControl',
      #
      SET_PAIR == 'SET_B_PAIR_01' ~ 'AP1G1',
      SET_PAIR == 'SET_B_PAIR_02' ~ 'DAAM1',
      SET_PAIR == 'SET_B_PAIR_03' ~ 'DNM1L',
      SET_PAIR == 'SET_B_PAIR_04' ~ 'DYNC1LI2',
      SET_PAIR == 'SET_B_PAIR_05' ~ 'EEA1',
      SET_PAIR == 'SET_B_PAIR_06' ~ 'KIF3A',
      SET_PAIR == 'SET_B_PAIR_07' ~ 'ROBO1',
      SET_PAIR == 'SET_B_PAIR_08' ~ 'SCYL2',
      SET_PAIR == 'SET_B_PAIR_09' ~ 'SRC',
      SET_PAIR == 'SET_B_PAIR_10' ~ 'TNK2',
      #
      SET_PAIR == 'SET_C_PAIR_02' ~ 'CLTA',
      SET_PAIR == 'SET_C_PAIR_04' ~ 'DNM2',
      SET_PAIR == 'SET_C_PAIR_05' ~ 'Dnm2',
      SET_PAIR == 'SET_C_PAIR_06' ~ 'Dnm3',
      SET_PAIR == 'SET_C_PAIR_07' ~ 'OCRL',
      SET_PAIR == 'SET_C_PAIR_08' ~ 'PACSIN2',
      SET_PAIR == 'SET_C_PAIR_09' ~ 'SH3GLB1',
      SET_PAIR == 'SET_C_PAIR_10' ~ 'SH3KBP1',
      #
      SET_PAIR == 'SET_D_PAIR_01dex57VS168' ~ '*APP_noEx_vs_ExA', #Ex168nt is ExA, Ex57nt is ExB
      SET_PAIR == 'SET_D_PAIR_01wtVS168' ~ '*APP_noEx_vs_ExA+ExB',
      SET_PAIR == 'SET_D_PAIR_01wtVS57' ~ '*APP_ExA_vs_ExA+ExB',
      SET_PAIR == 'SET_D_PAIR_02' ~ '*ATXN2',
      SET_PAIR == 'SET_D_PAIR_03' ~ '*EVI5',
      SET_PAIR == 'SET_D_PAIR_04' ~ '*OCRL_D/E',
      SET_PAIR == 'SET_D_PAIR_05' ~ '*PPFIA1',
      SET_PAIR == 'SET_D_PAIR_06' ~ '*SH3GLB1_D/E',
      SET_PAIR == 'SET_D_PAIR_07' ~ '*SH3KBP1_D/E',
      SET_PAIR == 'SET_D_PAIR_08' ~ '*VAV2_noEx_vs_ExA', #ExA (is likely the downstream micro-exon), ExB is upstream micro-exon (I think)
      SET_PAIR == 'SET_D_PAIR_08bothEx' ~ '*VAV2_noEx_vs_ExA+ExB',
      SET_PAIR == 'SET_D_PAIR_08DExVSaltEx' ~ '*VAV2_noEx_vs_ExB',
      SET_PAIR == 'SET_D_PAIR_08Ex1VsBoth' ~ '*VAV2_ExA_vs_ExA+ExB',
      SET_PAIR == 'SET_D_PAIR_08ExVsEx' ~ '*VAV2_ExA_vs_ExB',
      SET_PAIR == 'SET_D_PAIR_09' ~ '*VAV2_ExB_vs_ExA+ExB'
    )) %>% 
    dplyr::filter(Gene_name == gene_name) %>% 
    dplyr::mutate(Rep_number = as.character(gsub('REP_',"",Experiment_Rep)))
  
  # Get the top features
  top_features <- top_features_data$Feature
  
  # Generate a dot plot for each top feature
  if (length(top_features) > 0) {
    feature_dot_plots <- map(top_features, function(feature_name) {
      # Get the ranking of this feature
      feature_rank <- which(top_features == feature_name)
      
      # Check if the feature exists in CELL_DATA
      if (feature_name %in% colnames(cell_gene_data)) {
        dot_plot <- cell_gene_data %>%
          ggplot(aes_string(y = feature_name, x = "Intensity_MeanIntensity_MCHERRY_BACKCORR",
                            color = "ISOFORM")) +
          geom_point(alpha = 0.5, size = 3, aes(shape = Rep_number)) +
          geom_smooth(aes(color = ISOFORM), method = "lm", se = TRUE, linewidth = 1.2, fill = 'black',alpha = 0.8)+
          scale_x_log10() +
          scale_shape_discrete(name = "Experimental\nRepeat") +
          ylab(paste('"Noteworthy" ',feature_rank)) +
          xlab("mCherry intensity (a.u.)") +
          ggtitle(paste("No.", feature_rank, "'Noteworthy' feature for", gene_name), 
                  subtitle = paste("Feature:", feature_name)) +
          theme_bw(base_size = 16)
      } else {
        # Create an empty plot with message if feature doesn't exist in CELL_DATA
        dot_plot <- ggplot() + 
          annotate("text", x = 0.5, y = 0.5, 
                   label = paste("Feature", feature_name, "not found in CELL_DATA")) +
          theme_bw(base_size = 16) +
          ggtitle(paste("No.", feature_rank, "feature for", gene_name), 
                  subtitle = paste("Feature:", feature_name))
      }
      
      return(dot_plot)
    })
    
    # Add feature dot plots to plot list
    plot_list$feature_dot_plots <- feature_dot_plots
  } else {
    plot_list$feature_dot_plots <- list(
      ggplot() + 
        annotate("text", x = 0.5, y = 0.5, label = "No features to plot") +
        theme_bw(base_size = 16)
    )
  }
  
  return(plot_list)
}

# Example usage:
# plot_list <- generate_gene_plots(
#   IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg,
#   CELL_DATA = cell_data,
#   gene_name = "SNX2",
#   ratio_threshold = 1,
#   ratio_times_importance_threshold = 1,
#   n = 5
# )
# 
# # Accessing individual plots
# plot_list$main_importance_plot
# plot_list$top_features_bar_plot
# plot_list$feature_dot_plots[[1]]  # First feature dot plot
```

## Identifying top features for single isoform pairs

### Loading in single cell measurements

```{r Functions to load in single cell data, echo = FALSE}

#Function for loading in TRANSFECTED CELLS and SUMMARY datasets for each SET.
Load_transfected_cells_and_summary <- function(SET){
  setwd(paste0('//srv/scratch/weatheritt/pethan/HeLa_isoform_screen/ALL_CP_MEASUREMENTS_AND_FILTERED_TRANSFECTED_DATASETS'))
  #setwd(paste0('C:/Users/pethan/OneDrive - garvan.org.au/Documents/Australia_phd/Data/Isoform_imaging_screen_HeLa/ALL_CP_MEASUREMENTS_AND_FILTERED_TRANSFECTED_DATASETS'))
  
  Transfected_cell_files <- list.files() %>% 
    str_subset(pattern = '_TRANSFECTED_CELLS')
  Transfection_summary_files <- list.files() %>% 
    str_subset(pattern = '_TRANSFECTION_SUMMARY')
  
  load(paste0(str_subset(Transfected_cell_files, pattern = paste0(SET,'_REP_1_TRANSFECTED_CELLS'))))
  TRANSFECTED_CELLS_REP_1 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  
  load(paste0(str_subset(Transfected_cell_files, pattern = paste0(SET,'_REP_2_TRANSFECTED_CELLS'))))
  TRANSFECTED_CELLS_REP_2 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  
  load(paste0(str_subset(Transfected_cell_files, pattern = paste0(SET,'_REP_3_TRANSFECTED_CELLS'))))
  TRANSFECTED_CELLS_REP_3 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  
  Transfected_cells <- bind_rows(TRANSFECTED_CELLS_REP_1,
                                 TRANSFECTED_CELLS_REP_2,
                                 TRANSFECTED_CELLS_REP_3)
  
  load(paste0(str_subset(Transfection_summary_files, pattern = paste0(SET,'_REP_1_TRANSFECTION_SUMMARY'))))
  TRANSFECTION_SUMMARY_REP_1 <- Transfection_summary
  rm(Transfection_summary)
  
  load(paste0(str_subset(Transfection_summary_files, pattern = paste0(SET,'_REP_2_TRANSFECTION_SUMMARY'))))
  TRANSFECTION_SUMMARY_REP_2 <- Transfection_summary
  rm(Transfection_summary)
  
  load(paste0(str_subset(Transfection_summary_files, pattern = paste0(SET,'_REP_3_TRANSFECTION_SUMMARY'))))
  TRANSFECTION_SUMMARY_REP_3 <- Transfection_summary
  rm(Transfection_summary)
  
  Transfection_summary <- bind_rows(TRANSFECTION_SUMMARY_REP_1,
                                    TRANSFECTION_SUMMARY_REP_2,
                                    TRANSFECTION_SUMMARY_REP_3)
  return(list(Transfected_cells, Transfection_summary))
}
#Function for collected summary of REPEAT summaries
COLLECTED_SUMMARY <- function(DATASET){
  coll_summ <- DATASET %>%  
    ungroup() %>% 
    group_by(Experiment_Set, Metadata_Well) %>% 
    summarise(Transfected = sum(Transfected_TRUE),
              n_cells = sum(n_cells),
              Transfection_rate = round(Transfected/n_cells * 100, digits = 1)) %>%
    dplyr::mutate('Transfected_REP_1' = DATASET$Transfected_TRUE[DATASET$Experiment_Rep == 'REP_1'],
                  'Transfected_REP_2' = DATASET$Transfected_TRUE[DATASET$Experiment_Rep == 'REP_2'],
                  'Transfected_REP_3' = DATASET$Transfected_TRUE[DATASET$Experiment_Rep == 'REP_3'],
                  'n_cells_REP_1' = DATASET$n_cells[DATASET$Experiment_Rep == 'REP_1'],
                  'n_cells_REP_2' = DATASET$n_cells[DATASET$Experiment_Rep == 'REP_2'],
                  'n_cells_REP_3' = DATASET$n_cells[DATASET$Experiment_Rep == 'REP_3'],
                  'Transfection_rate_REP_1' = round(Transfected_REP_1/n_cells_REP_1 * 100, digits = 1),
                  'Transfection_rate_REP_2' = round(Transfected_REP_2/n_cells_REP_2 * 100, digits = 1),
                  'Transfection_rate_REP_3' = round(Transfected_REP_3/n_cells_REP_3 * 100, digits = 1))
  
  #coll_summ %>% 
  #  ungroup() %>% 
  #  group_by(Experiment_Set) %>% 
  #
  return(coll_summ)
}

remove_non_mcherry_vars <- function(TRANSFECTED_SET, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = FALSE){
  if(REDUCE_FEATURES == TRUE){
    Reduced_dataset <- TRANSFECTED_SET %>% 
      dplyr::select(ImageNumber, ObjectNumber, OBJECT_ID, Metadata_Well, CONTROL,Experiment_Set, Experiment_Rep, SET_PAIR, ISOFORM,TRANSFECTED, 
                    starts_with('Intensity_') & ends_with('_MCHERRY_BACKCORR'),
                    starts_with('Correlation_'),
                    starts_with('Granularity_'), starts_with('RadialDistribution'), starts_with('Texture_'), starts_with('AreaShape_')) %>% 
      dplyr::select(!c(starts_with('Correlation') & contains('GOLGIN97_AUTOF_CORR'))) %>% 
      na.omit()
  }
  if(REDUCE_FEATURES == FALSE){
    Reduced_dataset <- TRANSFECTED_SET %>% 
      dplyr::select(ImageNumber, ObjectNumber, OBJECT_ID, Metadata_Well, CONTROL,Experiment_Set, Experiment_Rep, SET_PAIR, ISOFORM,TRANSFECTED, everything()) %>% 
      dplyr::select(!c(Experiment_SetRep, ends_with('_BACKGROUND'), Number_Object_Number, Parent_Segmentation)) %>% 
      na.omit()
  }
  if(ONLY_TRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == TRUE)
  }
  if(ONLY_NEGTRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == FALSE)
  }
  return(Reduced_dataset)
}
#
alternative_comparisons_set_1A <- function(DATASET, SET_NAME){
  alt_pairClasp_altEx <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'DEx' | SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'DEx') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'DEx' ~ 'DEx',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'DEx' ~ 'PanEx'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_03DExVSPanEx'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pairClasp_bothex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'DEx' | SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'WT') %>% 
    dplyr::mutate(ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'DEx' ~ 'DEx',
                                      SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'WT' ~ 'Both'),
                  SET_PAIR = paste0(SET_NAME,'_PAIR_03bothEx'),
                  SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pairClasp_exvsex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'WT' | SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'DEx') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'WT' ~ 'Ex1',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'DEx' ~ 'PanEx'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_03ExVsEx'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pairClasp_ex1vsboth <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'WT' | SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'WT') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_03') & ISOFORM == 'WT' ~ 'Ex1',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_04') & ISOFORM == 'WT' ~ 'Both'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_03Ex1VsBoth'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  Transfected_only_without_outliers_1A_ALTERNATIVE_COMPARISONS <- DATASET %>% 
    dplyr::filter(SET_PAIR %in% c('SET_1_PAIR_MCHERRY','SET_1_PAIR_RAB5A', 'SET_A_PAIR_MCHERRY','SET_A_PAIR_RAB5A','SET_1A_PAIR_MCHERRY','SET_1A_PAIR_RAB5A')) %>% 
    bind_rows(., alt_pairClasp_altEx, alt_pairClasp_bothex, alt_pairClasp_exvsex,alt_pairClasp_ex1vsboth) %>% 
    na.omit()
  
  return(Transfected_only_without_outliers_1A_ALTERNATIVE_COMPARISONS)
}

#
alternative_comparisons_set_D <- function(DATASET, SET_NAME){ # DATASET is the transfected cells, SET_NAME is either SET_D or SET_E (Other sets don't have specific pairs)
  alt_pair01_wt57 <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_01') & ISOFORM %in% c('WT', 'DEx57nt')) %>% 
    dplyr::mutate(
      ISOFORM = case_when(ISOFORM == 'WT' ~ 'WT',
                          ISOFORM == 'DEx57nt' ~ 'DEx'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_01wtVS57'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pair01_wt168 <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_01') & ISOFORM %in% c('WT', 'DEx168nt')) %>% 
    dplyr::mutate(
      ISOFORM = case_when(ISOFORM == 'WT' ~ 'WT',
                          ISOFORM == 'DEx168nt' ~ 'DEx'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_01wtVS168'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pair01_dexdex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_01') & ISOFORM %in% c('DEx57nt', 'DEx168nt')) %>% 
    dplyr::mutate(
      ISOFORM = case_when(ISOFORM == 'DEx57nt' ~ 'DEx57nt',
                          ISOFORM == 'DEx168nt' ~ 'DEx168nt'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_01dex57VS168'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  #
  alt_pair08altex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'DEx' | SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'DEx') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'DEx' ~ 'DEx',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'DEx' ~ 'AltEx'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_08DExVSaltEx'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  
  alt_pair08bothex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'DEx' | SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'WT') %>% 
    dplyr::mutate(ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'DEx' ~ 'DEx',
                                      SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'WT' ~ 'Both'),
                  SET_PAIR = paste0(SET_NAME,'_PAIR_08bothEx'),
                  SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pair08exvsex <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'WT' | SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'DEx') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'WT' ~ 'Ex1',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'DEx' ~ 'Ex2'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_08ExVsEx'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  alt_pair08ex1vsboth <- DATASET %>% 
    dplyr::filter(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'WT' | SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'WT') %>% 
    dplyr::mutate(
      ISOFORM = case_when(SET_PAIR == paste0(SET_NAME,'_PAIR_08') & ISOFORM == 'WT' ~ 'Ex1',
                          SET_PAIR == paste0(SET_NAME,'_PAIR_09') & ISOFORM == 'WT' ~ 'Both'),
      SET_PAIR = paste0(SET_NAME,'_PAIR_08Ex1VsBoth'),
      SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  #Creating dataset with alterantive comparisons (and controls)
  Transfected_only_without_outliers_D_ALTERNATIVE_COMPARISONS <- DATASET %>% 
    dplyr::filter(SET_PAIR %in% c('SET_D_PAIR_MCHERRY','SET_D_PAIR_RAB5A', 'SET_E_PAIR_MCHERRY','SET_E_PAIR_RAB5A')) %>% 
    bind_rows(., alt_pair01_wt57, alt_pair01_wt168, alt_pair01_dexdex, alt_pair08altex, alt_pair08bothex, alt_pair08exvsex, alt_pair08ex1vsboth) %>% 
    na.omit()
  
  return(Transfected_only_without_outliers_D_ALTERNATIVE_COMPARISONS)
}

#Note, function also removes NAN columns and zero colummns
Identify_and_remove_outliers <- function(DATASET,
                                         USE_LOWER_MAX_UPPER_HINGE,
                                         ONLY_NEGTRANS = FALSE,
                                         REMOVE_TOP_x_PERCENTILE_NEGATIVE = FALSE,
                                         TOP_x_PERCENTILE = 0.1,
                                         REMOVE_SAME_COLS_AS_TRANSFECTED = FALSE,
                                         TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = NULL
                                         ){
  TRANSFECTED_ONLY <- DATASET %>% 
    dplyr::filter(TRANSFECTED == TRUE)
  #In the case that only nontransfected cells are in the original dataset, we don't want to remove them by filtering (as we don't have any cells left then)
  if(ONLY_NEGTRANS == TRUE){
    TRANSFECTED_ONLY <- DATASET 
  }
  if(ONLY_NEGTRANS == TRUE & REMOVE_TOP_x_PERCENTILE_NEGATIVE == TRUE){
    #Read in dataset
    TRANSFECTED_ONLY <- DATASET %>% 
      # Group by the variables of interest
      group_by(SET_PAIR, Experiment_Rep, ISOFORM) %>%
      # Arrange within groups by intensity (descending)
      arrange(desc(Intensity_MeanIntensity_MCHERRY_BACKCORR), .by_group = TRUE) %>%
      # Calculate the percentile within each group
      mutate(percentile = row_number()/n()) %>%
      # Keep only the bottom 80%
      filter(percentile > TOP_x_PERCENTILE) %>%
      # Remove the helper column
      select(-percentile) %>%
      # Ungroup to remove grouping structure
      ungroup()
  }
  
  SUMMARY_STATISTICS <- TRANSFECTED_ONLY %>%
    dplyr::mutate('LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    ungroup() %>% 
    group_by(SET_PAIR, Experiment_Rep, ISOFORM) %>% 
    summarise(n_cells = length(SET_PAIR),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25))) %>% 
    dplyr::mutate('SET_PAIR_REP_ISOFORM' = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  #Can be used to remove the skew of very bright cells if present in one isoform but not another (simply allows using the highest UPPER hing value from one isoform as the filter for the other isoform)
  MAX_INTENSITY_CUTOFF_SET_BASED <- SUMMARY_STATISTICS %>%
    ungroup() %>% 
    group_by(SET_PAIR, ISOFORM) %>%
    summarise('MAX_UPPER_HINGE' = max(UPPER_HINGE_IQRx1.5)) %>% 
    ungroup() %>% 
    group_by(SET_PAIR) %>% 
    summarise('LOWER_MAX_UPPER_HINGE' = min(MAX_UPPER_HINGE))
  #
  
  SUMMARY_STATISTICS_OUTLIER_CRITERIUM <- SUMMARY_STATISTICS %>%
    ungroup() %>% 
    dplyr::select(SET_PAIR_REP_ISOFORM,
                  UPPER_HINGE_IQRx1.5)
  
  Transfected_cells_outliers_removed <-TRANSFECTED_ONLY %>%
    dplyr::mutate('SET_PAIR_REP_ISOFORM' = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM),
                  'LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    dplyr::mutate('Intensity_Edge_mean_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Edge_max_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Max_mean_norm' = Intensity_MaxIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MassDisp_mean_norm' = Intensity_MassDisplacement_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Std_mean_norm' = Intensity_StdIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MAD_mean_norm' = Intensity_MADIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR) %>% 
    dplyr::left_join(x = ., y = SUMMARY_STATISTICS_OUTLIER_CRITERIUM, by = c('SET_PAIR_REP_ISOFORM' = 'SET_PAIR_REP_ISOFORM')) %>%
    dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < UPPER_HINGE_IQRx1.5) %>%
    dplyr::select(c(1:10,'SET_PAIR_REP_ISOFORM','LOG_INTENSITY','UPPER_HINGE_IQRx1.5', everything()))
  
  if(USE_LOWER_MAX_UPPER_HINGE == TRUE){
    Transfected_cells_outliers_removed <- Transfected_cells_outliers_removed %>% 
      dplyr::left_join(x = ., y = MAX_INTENSITY_CUTOFF_SET_BASED, by = c('SET_PAIR' = 'SET_PAIR')) %>% 
      dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < LOWER_MAX_UPPER_HINGE)
  }
  
  
  
  #Seems to remove columns with NANs and no variance
  FEATURE_START <- 14
  SET_PAIRS <- Transfected_cells_outliers_removed %>% 
    dplyr::filter(!c(word(SET_PAIR, 4,4, sep = fixed('_')) == 'NEGATIVE'),
                  !c(word(SET_PAIR, 4,4, sep = fixed('_')) == 'MCHERRY')) %>% 
    dplyr::pull(SET_PAIR) %>% 
    unique()
  
  CONSTANT_COLS <-c()
  NAN_COLS <- c()
  FEATURES <- colnames(Transfected_cells_outliers_removed)
  FEATURE_END <- length(colnames(Transfected_cells_outliers_removed))
  for(i in SET_PAIRS){
    PAIR_x_df <- Transfected_cells_outliers_removed %>% 
      dplyr::filter(SET_PAIR == i)
    
    for(j in FEATURE_START:FEATURE_END){
      constant_value <- length(unique(PAIR_x_df[[j]]))
      NAN_value <- any(is.na(PAIR_x_df[[j]]))
      
      if(constant_value == 1){
        CONSTANT_COLS <- c(CONSTANT_COLS, j)
      }
      if(NAN_value == TRUE){
        NAN_COLS <- c(NAN_COLS, j)
      }
    }
  }
  CONSTANT_FEATURES <- FEATURES[CONSTANT_COLS]
  NAN_FEATURES <- FEATURES[NAN_COLS]
  FEATURES_TO_REMOVE <- c(unique(CONSTANT_FEATURES), unique(NAN_FEATURES)) #REMOVES 8 VARIABLES FOR SET A (MOSTLY Manders Correlation)
  TEXT_CONSTANT <- paste0('The variables with CONSTANT values for at least one PAIR are: ', unique(CONSTANT_FEATURES))
  TEXT_NULL <- paste0('The variables with MISSING values for at least one PAIR are: ', unique(NAN_FEATURES))
  print(TEXT_CONSTANT)
  print(TEXT_NULL)
  
  
  Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>% 
    dplyr::select(!c(all_of(FEATURES_TO_REMOVE))) #%>% 
  #dplyr::select(!(c(starts_with('Intensity') & ends_with('MCHERRY_BACKCORR'))))
  
  if(ONLY_NEGTRANS == TRUE & REMOVE_SAME_COLS_AS_TRANSFECTED == TRUE){
    Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>%
      dplyr::select(c(colnames(TRANSFECTED_DATASET_FOR_COLS_TO_KEEP)))
  }
  
  
  SUMMARY_STATISTICS_OUTLIERS_REMOVED <- Transfected_cells_outliers_removed %>%
    ungroup() %>% 
    group_by(SET_PAIR, Experiment_Rep, ISOFORM) %>% 
    summarise(n_cells = length(SET_PAIR),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25))) %>% 
    dplyr::mutate('SET_PAIR_REP_ISOFORM' = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM))
  
  
  return(list(Transfected_cells_outliers_removed_REDUCED_COLS, SUMMARY_STATISTICS, SUMMARY_STATISTICS_OUTLIERS_REMOVED))
}

```



```{r Loading in and creating filtered cell datasets, echo=FALSE, warning = FALSE}
# Loading in single cell data
# SET 1A
#AGGREGATING SET 1 AND SET A
SET_1_FOR_FUSION <- Load_transfected_cells_and_summary(SET = 'SET_1')[[1]] %>% 
  dplyr::filter(!c(SET_PAIR %in% c('SET_1_PAIR_06')))
#
SET_A_FOR_FUSION <- Load_transfected_cells_and_summary(SET = 'SET_A')[[1]]
TRANSFECTED_SET_1Aagg <- bind_rows(SET_1_FOR_FUSION,
                                   SET_A_FOR_FUSION)
#SET B
TRANSFECTED_SET_B <- Load_transfected_cells_and_summary(SET = 'SET_B')[[1]]
#SET C
TRANSFECTED_SET_C <- Load_transfected_cells_and_summary(SET = 'SET_C')[[1]]
#SET D
TRANSFECTED_SET_D <- Load_transfected_cells_and_summary(SET = 'SET_D')[[1]] %>% 
  dplyr::filter(!c(SET_PAIR == 'SET_D_PAIR_NegativeGolgin97'))


# Reduced transfected datasets
# Postrans
Reduced_transfected_B <- remove_non_mcherry_vars(TRANSFECTED_SET_B, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)
Reduced_transfected_C <- remove_non_mcherry_vars(TRANSFECTED_SET_C, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)
Reduced_transfected_D <- remove_non_mcherry_vars(TRANSFECTED_SET_D, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)
Reduced_transfected_1Aagg <- remove_non_mcherry_vars(TRANSFECTED_SET_1Aagg, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)

# Negtrans
Reduced_negtrans_B <- remove_non_mcherry_vars(TRANSFECTED_SET_B, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)
Reduced_negtrans_C <- remove_non_mcherry_vars(TRANSFECTED_SET_C, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)
Reduced_negtrans_D <- remove_non_mcherry_vars(TRANSFECTED_SET_D, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)
Reduced_negtrans_1Aagg <- remove_non_mcherry_vars(TRANSFECTED_SET_1Aagg, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)



# Identify and remove outliers
# Pos trans
Transfected_only_without_outliers_1A <- Identify_and_remove_outliers(Reduced_transfected_1Aagg, 
                                                                     USE_LOWER_MAX_UPPER_HINGE = TRUE)[[1]]

Transfected_only_without_outliers_B <- Identify_and_remove_outliers(Reduced_transfected_B, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE)[[1]]

Transfected_only_without_outliers_C <- Identify_and_remove_outliers(Reduced_transfected_C, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE)[[1]]

Transfected_only_without_outliers_D <- Identify_and_remove_outliers(Reduced_transfected_D, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE)[[1]]

# Neg trans
#Set 1A
NegTransfected_only_without_outliers_1A <- Identify_and_remove_outliers(Reduced_negtrans_1Aagg, 
                                                                     USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                     ONLY_NEGTRANS = TRUE,
                                                                     REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                     TOP_x_PERCENTILE = 0.1,
                                                                     REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                     TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_1A)[[1]]
#Set B
NegTransfected_only_without_outliers_B <- Identify_and_remove_outliers(Reduced_negtrans_B, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    ONLY_NEGTRANS = TRUE,
                                                                    REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                    TOP_x_PERCENTILE = 0.1,
                                                                    REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                    TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_B)[[1]]
#Set C
NegTransfected_only_without_outliers_C <- Identify_and_remove_outliers(DATASET = Reduced_negtrans_C, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    ONLY_NEGTRANS = TRUE,
                                                                    REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                    TOP_x_PERCENTILE = 0.1,
                                                                    REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                    TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_C)[[1]]
#Set D
NegTransfected_only_without_outliers_D <- Identify_and_remove_outliers(Reduced_negtrans_D, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    ONLY_NEGTRANS = TRUE,
                                                                    REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                    TOP_x_PERCENTILE = 0.1,
                                                                    REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                    TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_D)[[1]]

#For SET 1 + A FUSION,
#Note, we collapse the two sets into a collective SET_1A. The information is retained in Reps, as Set1's reps are rep1-3, and SetA's reps are reps 4-6
Transfected_without_outliers_1A_for_classifier <- Transfected_only_without_outliers_1A %>% 
  dplyr::mutate(Experiment_Rep = case_when(Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_1' ~ 'REP_1',
                                           Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_2' ~ 'REP_2',
                                           Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_3' ~ 'REP_3',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_1' ~ 'REP_4',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_2' ~ 'REP_5',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_3' ~ 'REP_6')) %>% 
  dplyr::mutate(Experiment_Set = 'SET_1A') %>%
  dplyr::mutate(SET_PAIR = paste0(Experiment_Set,'_',word(SET_PAIR, start = 3, end = 4, sep = fixed("_"))),
                SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM)) %>% 
  dplyr::filter(!c(ISOFORM == 'NEGATIVE')) %>% 
  na.omit()
#Negative transfectants set 1 + A fusion
NegTransfected_without_outliers_1A_for_classifier <- NegTransfected_only_without_outliers_1A %>% 
  dplyr::mutate(Experiment_Rep = case_when(Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_1' ~ 'REP_1',
                                           Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_2' ~ 'REP_2',
                                           Experiment_Set == 'SET_1' & Experiment_Rep == 'REP_3' ~ 'REP_3',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_1' ~ 'REP_4',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_2' ~ 'REP_5',
                                           Experiment_Set == 'SET_A' & Experiment_Rep == 'REP_3' ~ 'REP_6')) %>% 
  dplyr::mutate(Experiment_Set = 'SET_1A') %>%
  dplyr::mutate(SET_PAIR = paste0(Experiment_Set,'_',word(SET_PAIR, start = 3, end = 4, sep = fixed("_"))),
                SET_PAIR_REP_ISOFORM = paste0(SET_PAIR,'_',Experiment_Rep,'_',ISOFORM)) %>% 
  dplyr::filter(!c(ISOFORM == 'NEGATIVE')) %>% 
  na.omit()


### Set 1A, alternative comparisons
#PositiveTransfectants
Transfected_only_without_outliers_1A_ALTERNATIVE_COMPARISONS <- alternative_comparisons_set_1A(Transfected_without_outliers_1A_for_classifier, SET_NAME = 'SET_1A')%>% 
  dplyr::mutate(ISOFORM = case_when(ISOFORM == 'WT' ~ 'WT',
                                    ISOFORM == 'DEx' ~ 'DEx',
                                    ISOFORM == 'Both' ~ 'WT',
                                    ISOFORM == 'PanEx' ~ 'WT',
                                    ISOFORM == 'Ex1' ~ 'DEx',
                                    ISOFORM == 'MCHERRY' ~ 'MCHERRY'))
#NegativeTransfectants
NegTransfected_only_without_outliers_1A_ALTERNATIVE_COMPARISONS <- alternative_comparisons_set_1A(NegTransfected_without_outliers_1A_for_classifier, SET_NAME = 'SET_1A') %>% 
  dplyr::mutate(ISOFORM = case_when(ISOFORM == 'WT' ~ 'WT',
                                    ISOFORM == 'DEx' ~ 'DEx',
                                    ISOFORM == 'Both' ~ 'WT',
                                    ISOFORM == 'PanEx' ~ 'WT',
                                    ISOFORM == 'Ex1' ~ 'DEx',
                                    ISOFORM == 'MCHERRY' ~ 'MCHERRY'))


### Set D/E, Alternative comparisons)
#Set D, positive transfectants
#View(Transfected_only_without_outliers_D_ALTERNATIVE_COMPARISONS )
Transfected_only_without_outliers_D_ALTERNATIVE_COMPARISONS <- alternative_comparisons_set_D(DATASET = Transfected_only_without_outliers_D, SET_NAME = 'SET_D') %>% #dplyr::select(SET_PAIR, ISOFORM) %>% distinct()
  dplyr::mutate(ISOFORM = case_when(
    SET_PAIR == 'SET_D_PAIR_01dex57VS168' & ISOFORM == 'DEx168nt' ~ 'DEx',
    SET_PAIR == 'SET_D_PAIR_01dex57VS168' & ISOFORM == 'DEx57nt' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08DExVSaltEx' & ISOFORM == 'AltEx' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08Ex1VsBoth' & ISOFORM == 'Both' ~ 'WT',
    SET_PAIR == 'SET_D_PAIR_08Ex1VsBoth' & ISOFORM == 'Ex1' ~ 'DEx',
    #
    SET_PAIR == 'SET_D_PAIR_08ExVsEx' & ISOFORM == 'Ex1' ~ 'DEx',
    SET_PAIR == 'SET_D_PAIR_08ExVsEx' & ISOFORM == 'Ex2' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08bothEx' & ISOFORM == 'Both' ~ 'WT',
    .default = ISOFORM
  ))

#Set D, negative transfectants
NegTransfected_only_without_outliers_D_ALTERNATIVE_COMPARISONS <- alternative_comparisons_set_D(DATASET = NegTransfected_only_without_outliers_D, SET_NAME = 'SET_D') %>% 
  dplyr::mutate(ISOFORM = case_when(
    SET_PAIR == 'SET_D_PAIR_01dex57VS168' & ISOFORM == 'DEx168' ~ 'DEx',
    SET_PAIR == 'SET_D_PAIR_01dex57VS168' & ISOFORM == 'DEx57' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08DExVSaltEx' & ISOFORM == 'AltEx' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08Ex1VsBoth' & ISOFORM == 'Both' ~ 'WT',
    SET_PAIR == 'SET_D_PAIR_08Ex1VsBoth' & ISOFORM == 'Ex1' ~ 'DEx',
    #
    SET_PAIR == 'SET_D_PAIR_08ExVsEx' & ISOFORM == 'Ex1' ~ 'DEx',
    SET_PAIR == 'SET_D_PAIR_08ExVsEx' & ISOFORM == 'Ex2' ~ 'WT',
    #
    SET_PAIR == 'SET_D_PAIR_08bothEx' & ISOFORM == 'Both' ~ 'WT',
    .default = ISOFORM
  ))
```


#### SNX2 variable importance
```{r SNX2 variable importance plots, echo=FALSE}
SNX2_var_import_plots <- generate_gene_plots(IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg, 
                                CELL_DATA = Transfected_without_outliers_1A_for_classifier, 
                                gene_name = 'SNX2',
                                ratio_threshold = ratio_threshold, 
                                ratio_times_importance_threshold = ratio_times_importance_threshold,
                                n = 5)
SNX2_var_import_plots$main_importance_plot
SNX2_var_import_plots$top_features_bar_plot
SNX2_var_import_plots$feature_dot_plots[[1]]
SNX2_var_import_plots$feature_dot_plots[[2]]
SNX2_var_import_plots$feature_dot_plots[[3]]

```
#### ANK2 variable importance
```{r ANK2 variable importance plots, echo=FALSE}
ANK2_var_import_plots <- generate_gene_plots(IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg, 
                                CELL_DATA = Transfected_without_outliers_1A_for_classifier, 
                                gene_name = 'ANK2',
                                ratio_threshold = ratio_threshold, 
                                ratio_times_importance_threshold = ratio_times_importance_threshold,
                                n = 5)
ANK2_var_import_plots$main_importance_plot
ANK2_var_import_plots$top_features_bar_plot
ANK2_var_import_plots$feature_dot_plots[[1]]
ANK2_var_import_plots$feature_dot_plots[[2]]
ANK2_var_import_plots$feature_dot_plots[[3]]
```
#### NUMB variable importance
```{r NUMB variable importance plots, echo=FALSE}
NUMB_var_import_plots <- generate_gene_plots(IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg, 
                                CELL_DATA = Transfected_without_outliers_1A_for_classifier, 
                                gene_name = 'NUMB',
                                ratio_threshold = ratio_threshold, 
                                ratio_times_importance_threshold = ratio_times_importance_threshold,
                                n = 1)
NUMB_var_import_plots$main_importance_plot
NUMB_var_import_plots$top_features_bar_plot
NUMB_var_import_plots$feature_dot_plots[[1]]
#NUMB_var_import_plots$feature_dot_plots[[2]]
#NUMB_var_import_plots$feature_dot_plots[[3]]



```
#### OCRL variable importance
```{r OCRL variable importance plots, echo=FALSE}
OCRL_var_import_plots <- generate_gene_plots(IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg, 
                                CELL_DATA = Transfected_only_without_outliers_C, 
                                gene_name = 'OCRL',
                                ratio_threshold = ratio_threshold, 
                                ratio_times_importance_threshold = ratio_times_importance_threshold,
                                n = 5)
OCRL_var_import_plots$main_importance_plot
OCRL_var_import_plots$top_features_bar_plot
OCRL_var_import_plots$feature_dot_plots[[1]]
OCRL_var_import_plots$feature_dot_plots[[2]]
OCRL_var_import_plots$feature_dot_plots[[3]]
```
#### FBXW11 variable importance
```{r FBXW11 variable importance plots, echo=FALSE}
FBXW11_var_import_plots <- generate_gene_plots(IMPORTANCE_DATA = combined_variable_importance_all_w_overall_posneg, 
                                CELL_DATA = Transfected_without_outliers_1A_for_classifier, 
                                gene_name = 'FBXW11',
                                ratio_threshold = ratio_threshold, 
                                ratio_times_importance_threshold = ratio_times_importance_threshold,
                                n = 5)
FBXW11_var_import_plots$main_importance_plot
FBXW11_var_import_plots$top_features_bar_plot
FBXW11_var_import_plots$feature_dot_plots[[1]]
FBXW11_var_import_plots$feature_dot_plots[[2]]
FBXW11_var_import_plots$feature_dot_plots[[3]]
```


## Recurring important features
```{r ranking features and some numbers, echo=FALSE}
# Number of isoform classifiers that are statistically significant (bootstrap) - exlcuding controls
Isoform_classifiers_w_diff_isoforms <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::pull(Gene_name)

# Total number of features
Total_features_used_for_classification <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  dplyr::pull(Feature) %>% 
  unique()

# Feature classes df
Feature_classes <- bind_cols('Feature' = Total_features_used_for_classification) %>%
  dplyr::mutate(major_class = word(Feature, start = 1, end = 1, sep = fixed('_'))) %>%
  dplyr::mutate(minor_class = word(Feature, start = 1, end = 2, sep = fixed('_')))

# Vector of the major feature claseses
Major_feature_classes <- Feature_classes %>% 
  dplyr::pull(major_class) %>% 
  unique()

# Vector of the minor feature claseses
Minor_feature_classes <- Feature_classes %>% 
  dplyr::pull(minor_class) %>% 
  unique()

# Feature order based on how many times they are recurring as noteworthy
Represented_feature_classes <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  dplyr::mutate(major_class = word(Feature, start = 1, end = 1, sep = fixed('_'))) %>% 
  dplyr::mutate(minor_class = word(Feature, start = 1, end = 2, sep = fixed('_')))

#Creating dataframe of the minor feature classes that are noteworthy (only doing for minor as all major ones are represented)
Represented_minor_classes <- Represented_feature_classes$minor_class %>% 
  unique()


###USE THE FEATURE_CLASSES DF TO JUST BRIEFLY DETERMINE HOW LARGE A PROPORTION OF THE SUB_CLASSES IN EACH MAJOR CLASS ARE Represented_feature_classes ###

# Recurring features order
Recurring_features_order <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  #Arrange with lowest on top
  dplyr::arrange(n) %>% 
  dplyr::pull(Feature)


# Summary of these numbers
print(paste('The number of features used for clasisfication are:', length(Total_features_used_for_classification)))
print(paste(length(Recurring_features_order), 'are noteworthy in at least one of the:',length(unique(Isoform_classifiers_w_diff_isoforms)),'statistically siginficant (boostrap confidence intervals) classifiers.'))
print(paste('That is',(length(Recurring_features_order)/length(Total_features_used_for_classification))*100,'%.'))
print(paste('We used features within 6 major feature groups for the classifiers. These were:',Major_feature_classes))
print(paste('All major classes were represented as a noteworthy feature at least once',all(Major_feature_classes %in% Represented_feature_classes$major_class)))
print(paste('We used',length(Minor_feature_classes),' minor features classes the mmajor clases for the classifiers.'))
print(paste('All minor classes were represented as a noteworthy feature at least once',all(Minor_feature_classes %in% Represented_feature_classes$minor_class)))
print(paste(length(Represented_minor_classes),'were represented as a noteworthy feature at least one.'))
print(paste('That is',(length(Represented_minor_classes)/length(Minor_feature_classes))*100,'% of minor classes.'))
```
### USE THE FEATURE_CLASSES DF TO JUST BRIEFLY DETERMINE HOW LARGE A PROPORTION OF THE SUB_CLASSES IN EACH MAJOR CLASS ARE Represented_feature_classes

```{r Plot of recurring features, echo = FALSE}
# How many of the features are used for classification?
bind_cols(n_features = c((length(Total_features_used_for_classification) - length(unique(Represented_feature_classes$Feature))),
                         length(unique(Represented_feature_classes$Feature))),
          noteworthy_feature = c(FALSE, TRUE)) %>% 
  ggplot(aes(x = noteworthy_feature, y = n_features))+
  geom_col()+
  labs(title = 'Features "Noteworthy" at least 1 time',
       y = 'Count (n)',
       x = 'Noteworthy')+
  theme_bw(base_size = 16)


# Count of feature represenation in major categories. Occurs at least 1
Represented_feature_classes %>% 
  ungroup() %>% 
  # Counts the number of times each feature occur
  dplyr::select(Feature, major_class) %>% 
  distinct() %>% 
  group_by(major_class) %>%
  summarize(n_features_noteworthy = n()) %>% 
  # The plot
  ggplot(aes(y = fct_reorder(major_class, n_features_noteworthy), x = n_features_noteworthy))+
  geom_col()+
  labs(title = 'Number of "Noteworthy" features in each major category',
       subtitle = 'Occurs at least 1 time',
       y = 'Main Feature groups',
       x = 'Count')+
  theme_bw(base_size = 16)




# How large a proportion of the subclasses within a major class are used?
# Counting the degree to which minor from each major class are represented
Represented_feature_classes %>% 
  ungroup() %>% 
  # Counts the number of times each feature occur
  group_by(Feature, major_class, minor_class) %>%
  summarize(n_feature_recurrence = n()) %>% 
  dplyr::filter(n_feature_recurrence >= 1) %>% 
  # Counts how many of the minor classes are represented 
  ungroup() %>% 
  dplyr::select(major_class, minor_class) %>%
  distinct() %>% 
  group_by(major_class) %>% 
  summarize(n_occurence = n()) %>% 
  #
  dplyr::right_join(x = ., y = Feature_classes %>% 
                      ungroup() %>% 
                      dplyr::select(major_class, minor_class) %>% 
                      distinct() %>% 
                      group_by(major_class) %>% 
                      summarize(n_total = n()),
                    by = join_by(major_class)
) %>% 
  dplyr::mutate(n_occurence = if_else(is.na(n_occurence),0,n_occurence),
                proportion_represented = n_occurence/n_total) %>% 
  dplyr::arrange(proportion_represented) %>% 
  ungroup() %>% 
  # The plot
  ggplot(aes(y = fct_reorder(major_class,proportion_represented), x = proportion_represented))+
  geom_col()+
  geom_text(aes(x = 0.9, label = paste(n_occurence,'/',n_total)))+
  coord_cartesian(xlim = c(0,1))+
  labs(title = 'Proportion of sub-feature groups occuring as "Noteworthy"',
       subtitle = 'Occurs at least 1 time',
       y = 'Main Feature groups',
       x = 'Proportion of subgroups occuring')+
  theme_bw(base_size = 16)



# How often are the noteworthy features used?
combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  dplyr::mutate(Feature = factor(Feature, levels = Recurring_features_order)) %>% 
  ggplot(aes(x = n))+
  geom_histogram(bins = 4)+
    labs(title = 'Recurrence of "Noteworthy" features',
          y = 'Count (n)',
          x = 'No. of occurences')+
  theme_bw(base_size = 16)


# Count plot of all features and their recurrence that shows feature name
combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  dplyr::mutate(Feature = factor(Feature, levels = Recurring_features_order)) %>% 
  ggplot(aes(y = Feature, x = percent_of_all))+
  geom_col()+
  labs(title = 'Features in classifiers',
         subtitle = '"Noteworthy" in at least 1 classifier detecting different',
          y = 'Feature',
          x = 'Proportion of classifiers')+
  theme_bw(base_size = 16)


#For most recurring features (e.g. the ones that are found in at least 3 (lower) or 4 of stat isoform classifiers, we can examine)
combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  dplyr::mutate(Feature = factor(Feature, levels = Recurring_features_order)) %>% 
  dplyr::filter(n >= 2) %>% 
  ggplot(aes(y = Feature, x = percent_of_all))+
  geom_col()+
  labs(title = 'Features in classifiers',
         subtitle = '"Noteworthy" in at least 2 classifiers detecting different',
          y = 'Feature',
          x = 'Proportion of classifiers')+
  theme_bw(base_size = 16)


# Count of feature represenation in major categories. Occurs at least 2x
Represented_feature_classes %>% 
  ungroup() %>% 
  # Counts the number of times each feature occur
  group_by(Feature, major_class, minor_class) %>%
  summarize(n_feature_recurrence = n()) %>% 
  dplyr::filter(n_feature_recurrence >= 2) %>% 
  # Counts how many of the minor classes are represented 
  ungroup() %>% 
  dplyr::select(Feature, major_class) %>%
  distinct() %>% 
  group_by(major_class) %>% 
  summarize(n_features_noteworthy = n()) %>% 
  # The plot
  ggplot(aes(y = fct_reorder(major_class, n_features_noteworthy), x = n_features_noteworthy))+
  geom_col()+
  labs(title = 'Number of "Noteworthy" features in each major category',
       subtitle = 'Occurs at least 2 time',
       y = 'Main Feature groups',
       x = 'Count (n)')+
  theme_bw(base_size = 16)
  
# How large a proportion of the subclasses within a major class are used?
# Counting the degree to which minor from each major class are represented
Represented_feature_classes %>% 
  ungroup() %>% 
  # Counts the number of times each feature occur
  group_by(Feature, major_class, minor_class) %>%
  summarize(n_feature_recurrence = n()) %>% 
  dplyr::filter(n_feature_recurrence >= 2) %>% 
  # Counts how many of the minor classes are represented 
  ungroup() %>% 
  dplyr::select(major_class, minor_class) %>%
  distinct() %>% 
  group_by(major_class) %>% 
  summarize(n_occurence = n()) %>% 
  #
  dplyr::right_join(x = ., y = Feature_classes %>% 
                      ungroup() %>% 
                      dplyr::select(major_class, minor_class) %>% 
                      distinct() %>% 
                      group_by(major_class) %>% 
                      summarize(n_total = n()),
                    by = join_by(major_class)
) %>% 
  dplyr::mutate(n_occurence = if_else(is.na(n_occurence),0,n_occurence),
                proportion_represented = n_occurence/n_total) %>% 
  dplyr::arrange(proportion_represented) %>% 
  ungroup() %>% 
  # The plot
  ggplot(aes(y = fct_reorder(major_class,proportion_represented), x = proportion_represented))+
  geom_col()+
  geom_text(aes(x = 0.9, label = paste(n_occurence,'/',n_total)), size = 5)+
  coord_cartesian(xlim = c(0,1))+
  labs(title = 'Proportion of sub-feature groups occuring as "Noteworthy"',
       subtitle = 'Occurs at least 2 times',
       y = 'Main Feature groups',
       x = 'Proportion of subgroups occuring')+
  theme_bw(base_size = 16)


# Percent of features that remain noteworthy (when required to occur at least 2x)
Represented_feature_classes %>% 
  ungroup() %>% 
  # Counts the number of times each feature occur
  group_by(Feature, major_class, minor_class) %>%
  summarize(n_feature_recurrence = n()) %>% 
  dplyr::filter(n_feature_recurrence >= 2) %>% 
  # Counts how many of the minor classes are represented 
  ungroup() %>% 
  dplyr::select(Feature, major_class) %>%
  distinct() %>% 
  group_by(major_class) %>% 
  summarize(n_occurence_more_than_1x = n()) %>% 
  #
  dplyr::right_join(x = ., y = Represented_feature_classes %>% 
                      ungroup() %>% 
                      dplyr::select(Feature, major_class) %>%
                      distinct() %>% 
                      group_by(major_class) %>% 
                      summarize(n_occurence_1x = n()),
                    by = join_by(major_class)) %>% 
  dplyr::mutate(n_occurence_more_than_1x = if_else(is.na(n_occurence_more_than_1x),0, n_occurence_more_than_1x),
                proportion_represented = n_occurence_more_than_1x/n_occurence_1x) %>% 
  dplyr::arrange(proportion_represented) %>% 
  ungroup() %>% 
  # The plot
  ggplot(aes(y = fct_reorder(major_class,proportion_represented), x = proportion_represented))+
  geom_col()+
  geom_text(aes(x = 0.9, label = paste(n_occurence_more_than_1x,'/',n_occurence_1x)), size = 5)+
  coord_cartesian(xlim = c(0,1))+
  labs(title = 'Proportion of sub-feature groups occuring as "Noteworthy"',
       subtitle = 'Occurs at least 2 times',
       y = 'Main Feature groups',
       x = 'Proportion of subgroups occuring')+
  theme_bw(base_size = 16)
```

### Plot of importance metric for the recurring features (occuring at least 3 or 4 times)
```{r Importance metric ratio x score plotted for each recurring feature with linerange and mean, echo=FALSE}
### 3x recurring
# Recurring features order, occurence at least 3x
Recurring_features_order_n3 <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  #Arrange with lowest on top
  dplyr::ungroup() %>% 
  dplyr::filter(n >= 3) %>% 
  dplyr::arrange(n) %>% 
  dplyr::pull(Feature)

#Mean importance metric for 3 recurring
Feature_order_importance_metric_n3 <- combined_variable_importance_all_w_overall_posneg %>% 
  ungroup() %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n3)) %>%
  group_by(Feature) %>% 
  summarise(mean_importance = mean(ratio_times_importance)) %>% 
  ungroup() %>% 
  dplyr::arrange(mean_importance) %>% 
  dplyr::pull(Feature)

#
Feature_summary_n3 <- combined_variable_importance_all_w_overall_posneg %>% 
  ungroup() %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n3)) %>%
  group_by(Feature) %>% 
  summarise(n_occurence = n(),
            min_importance = min(ratio_times_importance),
            max_importance = max(ratio_times_importance),
            mean_importance = mean(ratio_times_importance)) %>% 
  ungroup() %>% 
  dplyr::mutate(Feature = factor(Feature, levels = Feature_order_importance_metric_n3))

# Plot of importance metric (ratio x score) for recurring features
#View(combined_variable_importance_all_w_overall_posneg )

combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n3)) %>%
  dplyr::mutate(Feature = factor(Feature, levels = Feature_order_importance_metric_n3)) %>% 
  ggplot(aes(x = ratio_times_importance, y = Feature))+
  geom_linerange(data = Feature_summary_n3, aes(xmin = min_importance, x = mean_importance, xmax = max_importance), alpha = 0.5)+
  geom_point(aes(fill = Gene_name), shape = 21, size = 4.5, color = 'black', alpha = 0.9, position = position_jitter(width = 0, height = 0.25))+
  geom_point(data = Feature_summary_n3, aes(x = mean_importance), shape = 'l', size = 6, color = 'black', alpha = 0.75)+
  geom_text(data = Feature_summary_n3, aes(x = 64, label = paste('n=',n_occurence)), size = 4.5)+
  geom_vline(xintercept = ratio_times_importance_threshold, color = 'red', linewidth = 1)+
  theme_bw(base_size = 16)+
  scale_x_continuous(transform = 'log2')+
  coord_cartesian(xlim = c(1,100))+
  labs(title = 'Importance of "Noteworthy" features',
       subtitle = 'Occurs at least 3 times',
       y = 'Feature',
       x = 'Feature contribution (%) x Contribution ratio',
       fill = 'Gene with isoforms')+
  theme_bw(base_size = 16)



### 4x recurring
# Recurring features order, occurence at least 4x
Recurring_features_order_n2 <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarize(n = n(),
            percent_of_all = n/length(unique(Isoform_classifiers_w_diff_isoforms))) %>% 
  #Arrange with lowest on top
  dplyr::ungroup() %>% 
  dplyr::filter(n >= 2) %>% 
  dplyr::arrange(n) %>% 
  dplyr::pull(Feature)

#Mean importance metric for4 recurring
Feature_order_importance_metric_n2 <- combined_variable_importance_all_w_overall_posneg %>% 
  ungroup() %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n2)) %>%
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarise(mean_importance = mean(ratio_times_importance)) %>% 
  ungroup() %>% 
  dplyr::arrange(mean_importance) %>% 
  dplyr::pull(Feature)

# Feature summaries with recurrence at least 4x
Feature_summary_n2 <- combined_variable_importance_all_w_overall_posneg %>% 
  ungroup() %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n2)) %>%
    dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  group_by(Feature) %>% 
  summarise(n_occurence = n(),
            min_importance = min(ratio_times_importance),
            max_importance = max(ratio_times_importance),
            mean_importance = mean(ratio_times_importance)) %>% 
  ungroup() %>% 
  dplyr::mutate(Feature = factor(Feature, levels = Feature_order_importance_metric_n2))


# Plot of importance metric (ratio x score) for recurring features, at least 4x recurrence
combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name != 'PosControl') %>% 
  dplyr::filter(adj_significant == TRUE) %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::filter(Feature %in% c(Recurring_features_order_n2)) %>%
  dplyr::mutate(Feature = factor(Feature, levels = Feature_order_importance_metric_n2)) %>% 
  # Removes intensity edge max norm, as I accidentally specified it to be the same as intensity edge mean norm (it has been like that for classifiers as well, but no point in doing everything again)
  dplyr::filter(!Feature == 'Intensity_Edge_max_norm') %>% 
  #
  ggplot(aes(x = ratio_times_importance, y = Feature))+
  geom_linerange(data = Feature_summary_n2 %>% 
                     dplyr::filter(!Feature == 'Intensity_Edge_max_norm'), aes(xmin = min_importance, x = mean_importance, xmax = max_importance), alpha = 0.5)+
  geom_point(aes(fill = Gene_name), shape = 21, size = 4, color = 'black', alpha = 0.9, position = position_jitter(width = 0, height = 0.25))+
  geom_point(data = Feature_summary_n2 %>% 
                     dplyr::filter(!Feature == 'Intensity_Edge_max_norm'), aes(x = mean_importance), shape = 'l', size = 6, color = 'black', alpha = 0.75)+
  geom_text(data = Feature_summary_n2 %>% 
                     dplyr::filter(!Feature == 'Intensity_Edge_max_norm'), aes(x = 64, label = paste('n=',n_occurence)), size = 4.5)+
  geom_vline(xintercept = ratio_times_importance_threshold, color = 'red', linewidth = 1)+
  theme_bw(base_size = 16)+
  scale_x_continuous(transform = 'log2')+
  coord_cartesian(xlim = c(1,100))+
  labs(title = 'Importance of "Noteworthy" features',
       subtitle = 'Occurs at least 2 times',
       y = 'Feature',
       x = 'Feature contribution (%) x Contribution ratio',
       fill = 'Gene with isoforms')+
  theme_bw(base_size = 16)

```

