---
title: "12_Analysis_of_transfected_cells_SNX2mutants_v1_20250319"
author: "Peter Kjer Hansen"
date: "2025-04-01"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "svg")


# Packages
library(tidyverse)
library(caret)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(broom)
library(readxl)
library(lsr) #Contains cohensD() function
library(nnet) #Feedforward neural network
library(UpSetR) #Package for doing upset plots
library(ggrepel) #Package for making repel text
library(factoextra) #
library(ggdendro) # Package for dendrograms

# Working directory with transfected cell data
Directory_with_transfected_cell_measurements <- 'INSERT PATH TO FOLDER WITH .CSV OF SNX2 MUTANT SINGLE CELL MEASUREMENTS'

#Working directory
#Exon description dataset
Path_to_exon_description_sheet <- 'INSERT PATH TO EXCEL SHEET WITH EXON DESCRIPTIONS FOR ISOFORM LIBRARY'
File_with_exon_description_sheet <- 'INSERT FILE NAME OF .XLSX WITH EXON DESCRIPTION'
Event_sheet <- 'INSERT SHEET NAME'
LUMIER_sheet <- 'INSERT SHEET NAME'

# Model folders
#Postrans
Postransfected_model_folder <- 'INSERT PATH TO CLASSIFIERS TRAINED ON TRANSFECTED CELLS'
#Negtrans 10 percentile with rep aware sampling
Negtransfected_model_folder <- 'INSERT PATH TO CLASSIFIERS TRAINED ON NON-TRANSFECTED CELLS'

# SNX2 isoform classifier pair
PAIRS_1A <- c('PAIR_09')

### Thresholds for important variables
# Threshold for the contribution ratio (pos_trans / neg_trans). Higher is more stringent
ratio_threshold <- 2.6
# Threshold for the contribution ratio X contribution prop (positive) variable. Higher is more stringent
ratio_times_importance_threshold <- 1.5
#
confidence_interval_threshold_for_bootstrap <- 0.99

# mCherry intensity value that marks the transfection threshold. It is used to specify expression level relative to the lower detection limit (transfection threshold)
transfection_threshold <- 0.00065
```

```{r well construct ids, echo = FALSE}
Well_mutant_pairing <- bind_cols(Well_ID = c('A01','A02','A03','A04','A05','A06',
                                             'B01','B02','B03','B04','B05','B06',
                                             'C01','C02','C03','C04','C05','C06',
                                             'D01','D02','D03','D04','D05','D06'),
                                 Construct = c('Nontransfected', 'mCherry', '-EX: EIaE|----|W','-EX: EIqE|----|W', '-EX: EIeE|----|W', '-EX: EIkE|----|W',
                                             '+EX: EIRk|EIEE|W', '+EX: EIRa|EIEE|W', '+EX: EIRq|EIEE|W', '+EX: EIRE|aaaa|W', '+EX: EIRE|aIaa|W', '+EX: EIRE|qIqq|W',
                                             '+EX: EIRE|qIEE|W','+EX: EIRE|EIqE|W', '+EX: EIRE|EIEq|W', '+EX: EIRE|qIEq|W', '+EX: EIRE|qIqE|W', '+EX: EIRE|EIqq|W',
                                              '-EX (rep1)', '-EX (rep2)','+EX: EIRE|EIaE|W', '+EX: EIRE|EIrE|W','+EX', '-EX (rep3)'))
```


```{r Function for loading in cells, echo=FALSE}
Load_transfected_cells_and_summary_SNX2muts <- function(WORKING_DIRECTORY, SET){
  setwd(WORKING_DIRECTORY)

  Transfected_cell_files <- list.files(path = WORKING_DIRECTORY) %>% 
    str_subset(pattern = '_TRANSFECTED_CELLS')
  
  Transfection_summary_files <- list.files(path = WORKING_DIRECTORY)%>% 
    str_subset(pattern = '_TRANSFECTION_SUMMARY')
  
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP1_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_1 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP2_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_2 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP3_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_3 <- Transfected_cellbodies
  rm(Transfected_cellbodies)

  #
  Transfected_cells <- bind_rows(TRANSFECTED_CELLS_REP_1,
                                 TRANSFECTED_CELLS_REP_2,
                                 TRANSFECTED_CELLS_REP_3)
  # SUMMARIES
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP1_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_1 <- Transfection_summary
  rm(Transfection_summary)
  
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP2_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_2 <- Transfection_summary
  rm(Transfection_summary)
  
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP3_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_3 <- Transfection_summary
  rm(Transfection_summary)
  
  Transfection_summary <- bind_rows(TRANSFECTION_SUMMARY_REP_1,
                                    TRANSFECTION_SUMMARY_REP_2,
                                    TRANSFECTION_SUMMARY_REP_3)
  return(list(Transfected_cells, Transfection_summary))
}
```

```{r Loading in cells and summaries, echo=FALSE}
#
TRANSFECTED_SNX2muts <- Load_transfected_cells_and_summary_SNX2muts(WORKING_DIRECTORY = Directory_with_transfected_cell_measurements,
                                   SET = 'SET_SNX2mutants')[[1]]
#
SUMMARY_SNX2muts <- Load_transfected_cells_and_summary_SNX2muts(WORKING_DIRECTORY = Directory_with_transfected_cell_measurements,
                                   SET = 'SET_SNX2mutants')[[2]]
```

```{r Function to reduce features, echo=FALSE}
remove_non_mcherry_vars_SNX2muts <- function(CELL_DATA, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = FALSE){
  if(REDUCE_FEATURES == TRUE){
    Reduced_dataset <- CELL_DATA %>% 
      dplyr::select(ImageNumber, ObjectNumber, Metadata_Well, Experiment_Set, Experiment_Rep, TRANSFECTED, 
                    starts_with('Intensity_') & ends_with('_MCHERRY_BACKCORR'),
                    starts_with('Correlation_'),
                    starts_with('Granularity_'), starts_with('RadialDistribution'), starts_with('Texture_'), starts_with('AreaShape_')) %>% 
      dplyr::select(!c(starts_with('Correlation') & contains('GOLGIN97_AUTOF_CORR'))) %>% 
      na.omit()
  }
  if(REDUCE_FEATURES == FALSE){
    Reduced_dataset <- CELL_DATA %>% 
      dplyr::select(ImageNumber, ObjectNumber, Metadata_Well, Experiment_Set, Experiment_Rep, TRANSFECTED, everything()) %>% 
      dplyr::select(!c(Experiment_SetRep, ends_with('_BACKGROUND'), Number_Object_Number, Parent_Segmentation)) %>% 
      na.omit()
  }
  if(ONLY_TRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == TRUE)
  }
  if(ONLY_NEGTRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == FALSE)
  }
  return(Reduced_dataset)
}
```

```{r Generating datasets with reduced number of features, echo=FALSE}
Reduced_transfected_SNX2muts <- remove_non_mcherry_vars_SNX2muts(CELL_DATA = TRANSFECTED_SNX2muts, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)

Reduced_negtrans_SNX2muts <- remove_non_mcherry_vars_SNX2muts(CELL_DATA = TRANSFECTED_SNX2muts, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)
```



```{r Function to remove outliers bright cells, echo=FALSE}

#Outliers (DEFINED AS AS HAVING Intensity_MeanIntensity_MCHERRY_BACKCORR > 1.5 x IQR + 75% quantile Intensity_MCHERRY_BACKCORR for construct with lowest RANGE - Note, non-trans, mCherry, and B04 (4xA) not part of this 
###
#Note, function also removes NAN columns and zero colummns
Identify_and_remove_outliers_SNX2muts <- function(DATASET,
                                         USE_LOWER_MAX_UPPER_HINGE,
                                         ONLY_NEGTRANS = FALSE,
                                         REMOVE_TOP_x_PERCENTILE_NEGATIVE = FALSE,
                                         TOP_x_PERCENTILE = 0.1,
                                         REMOVE_SAME_COLS_AS_TRANSFECTED = FALSE,
                                         TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = NULL,
                                         WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04')
                                         ){
  TRANSFECTED_ONLY <- DATASET %>% 
    dplyr::filter(TRANSFECTED == TRUE)
  #In the case that only nontransfected cells are in the original dataset, we don't want to remove them by filtering (as we don't have any cells left then)
  if(ONLY_NEGTRANS == TRUE){
    TRANSFECTED_ONLY <- DATASET 
  }
  if(ONLY_NEGTRANS == TRUE & REMOVE_TOP_x_PERCENTILE_NEGATIVE == TRUE){
    #Read in dataset
    TRANSFECTED_ONLY <- DATASET %>% 
      # Group by the variables of interest
      group_by(Experiment_Rep, Metadata_Well) %>%
      # Arrange within groups by intensity (descending)
      arrange(desc(Intensity_MeanIntensity_MCHERRY_BACKCORR), .by_group = TRUE) %>%
      # Calculate the percentile within each group
      mutate(percentile = row_number()/n()) %>%
      # Keep only the bottom 80%
      filter(percentile > TOP_x_PERCENTILE) %>%
      # Remove the helper column
      select(-percentile) %>%
      # Ungroup to remove grouping structure
      ungroup()
  }
  
  SUMMARY_STATISTICS <- TRANSFECTED_ONLY %>%
    dplyr::mutate('LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    ungroup() %>% 
    group_by(Experiment_Rep, Metadata_Well) %>% 
    summarise(n_cells = n(),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              QUANTILE_75_INTENSITY = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25)))  %>% 
    ungroup() %>% 
    dplyr::mutate('REP_WELL' = paste0(Experiment_Rep,'_',Metadata_Well))
  
  #Can be used to remove the skew of very bright cells if present in one isoform but not another (simply allows using the highest UPPER hing value from one isoform as the filter for the other isoform)
  MAX_INTENSITY_CUTOFF_SET_BASED <- SUMMARY_STATISTICS %>%
    dplyr::filter(!Metadata_Well %in% WELLS_NOT_USED_FOR_DEFINING_OUTLIERS) %>% 
    group_by(Experiment_Rep) %>% 
    summarise('LOWER_MAX_UPPER_HINGE' = min(UPPER_HINGE_IQRx1.5))
  #
  

    Transfected_cells_outliers_removed <-TRANSFECTED_ONLY %>%
    dplyr::mutate('LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    ungroup() %>%
    dplyr::mutate('Intensity_Edge_mean_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Edge_max_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Max_mean_norm' = Intensity_MaxIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MassDisp_mean_norm' = Intensity_MassDisplacement_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Std_mean_norm' = Intensity_StdIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MAD_mean_norm' = Intensity_MADIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR) %>% 
    dplyr::left_join(x = ., y = SUMMARY_STATISTICS, by = join_by('Experiment_Rep' == 'Experiment_Rep', 'Metadata_Well' == 'Metadata_Well')) %>%
    dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < UPPER_HINGE_IQRx1.5) %>%
    dplyr::select(-c(MEAN_INTENSITY, MEDIAN_INTENSITY, SD_INTENSITY, LOG_MEAN_INTENSITY, LOG_SD_INTENSITY, QUANTILE_75_INTENSITY, n_cells)) %>% 
    dplyr::select(c(1:6, 'REP_WELL', 'LOG_INTENSITY','UPPER_HINGE_IQRx1.5', everything()))
  
  if(USE_LOWER_MAX_UPPER_HINGE == TRUE){
    Transfected_cells_outliers_removed <- Transfected_cells_outliers_removed %>% 
      dplyr::left_join(x = ., y = MAX_INTENSITY_CUTOFF_SET_BASED, by = join_by('Experiment_Rep' == 'Experiment_Rep')) %>% 
      dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < LOWER_MAX_UPPER_HINGE) %>% 
      dplyr::select(c(1:9, 'LOWER_MAX_UPPER_HINGE', everything()))
  }
  
  #Seems to remove columns with NANs and no variance
  if(USE_LOWER_MAX_UPPER_HINGE == TRUE){
    FEATURE_START <- 11
  }
  if(USE_LOWER_MAX_UPPER_HINGE == FALSE){
    FEATURE_START <- 10
  }
  Wells <- Transfected_cells_outliers_removed %>% 
    dplyr::filter(!Metadata_Well %in% WELLS_NOT_USED_FOR_DEFINING_OUTLIERS) %>% 
    dplyr::pull(Metadata_Well) %>% 
    unique()
  
  CONSTANT_COLS <-c()
  NAN_COLS <- c()
  FEATURES <- colnames(Transfected_cells_outliers_removed)
  FEATURE_END <- length(colnames(Transfected_cells_outliers_removed))
  for(i in Wells){
    PAIR_x_df <- Transfected_cells_outliers_removed %>% 
      dplyr::filter(Metadata_Well == i)
    
    for(j in FEATURE_START:FEATURE_END){
      constant_value <- length(unique(PAIR_x_df[[j]]))
      NAN_value <- any(is.na(PAIR_x_df[[j]]))
      
      if(constant_value == 1){
        CONSTANT_COLS <- c(CONSTANT_COLS, j)
      }
      if(NAN_value == TRUE){
        NAN_COLS <- c(NAN_COLS, j)
      }
    }
  }
  CONSTANT_FEATURES <- FEATURES[CONSTANT_COLS]
  NAN_FEATURES <- FEATURES[NAN_COLS]
  FEATURES_TO_REMOVE <- c(unique(CONSTANT_FEATURES), unique(NAN_FEATURES)) #REMOVES 8 VARIABLES FOR SET A (MOSTLY Manders Correlation)
  TEXT_CONSTANT <- paste0('The variables with CONSTANT values for at least one PAIR are: ', unique(CONSTANT_FEATURES))
  TEXT_NULL <- paste0('The variables with MISSING values for at least one PAIR are: ', unique(NAN_FEATURES))
  print(TEXT_CONSTANT)
  print(TEXT_NULL)
  
  
  Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>% 
    dplyr::select(!c(all_of(FEATURES_TO_REMOVE))) #%>% 
  #dplyr::select(!(c(starts_with('Intensity') & ends_with('MCHERRY_BACKCORR'))))
  
  if(ONLY_NEGTRANS == TRUE & REMOVE_SAME_COLS_AS_TRANSFECTED == TRUE){
    Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>%
      dplyr::select(c(colnames(TRANSFECTED_DATASET_FOR_COLS_TO_KEEP)))
  }
  
  
  SUMMARY_STATISTICS_OUTLIERS_REMOVED <- Transfected_cells_outliers_removed %>%
    ungroup() %>% 
    group_by(Experiment_Rep, Metadata_Well) %>% 
    summarise(n_cells = n(),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25))) %>% 
    dplyr::mutate('REP_WELL' = paste0(Experiment_Rep,'_',Metadata_Well))
  
  
  return(list(Transfected_cells_outliers_removed_REDUCED_COLS, SUMMARY_STATISTICS, SUMMARY_STATISTICS_OUTLIERS_REMOVED))
}
#####
```


```{r Creating transfected datasets with outlier removal, echo=FALSE, message=FALSE}
#Transfected cells for each isoform pair and controls
Transfected_only_without_outliers_SNX2muts_loose_intensity <- Identify_and_remove_outliers_SNX2muts(Reduced_transfected_SNX2muts, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = FALSE,
                                                                    WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04'))[[1]] 

#Non transfected
NegTransfected_only_without_outliers_SNX2muts <- Identify_and_remove_outliers_SNX2muts(Reduced_negtrans_SNX2muts, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    ONLY_NEGTRANS = TRUE,
                                                                    REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                    TOP_x_PERCENTILE = 0.1,
                                                                    REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                    TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_SNX2muts_loose_intensity,
                                                                    WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04'))[[1]]


### ADDDING CONSTRUCT IDS
Transfected_only_without_outliers_SNX2muts_loose_intensity <- Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::select(c(1:9, 'Construct', everything()))
#
NegTransfected_only_without_outliers_SNX2muts <- NegTransfected_only_without_outliers_SNX2muts %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::select(c(1:9, 'Construct', everything()))%>% 
  dplyr::select(-LOWER_MAX_UPPER_HINGE)

```


## Population expression plots but using intensity filtered cells
### Loose intensity threshold
```{r population mean expression plots of loose threshold cells, echo=FALSE}
population_intensity_df <- Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  #dplyr::filter(TRANSFECTED == TRUE) %>% 
  #dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::filter(!Metadata_Well %in% c('A01','A02')) %>% 
  dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)) %>% 
  dplyr::mutate(Construct = factor(Construct, levels = plot_construct_order))


population_intensity_df %>%
  ggplot(aes(y = Construct,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR/transfection_threshold))+
  geom_boxplot(outlier.shape = NA, aes(fill = `4_residue_insert`))+
  #geom_vline(xintercept = 0.003)+
  geom_text(data = population_intensity_df %>%
              ungroup() %>% 
              group_by(Construct) %>% 
              summarize(n_cell = n()),
            aes(x = 188, y = Construct, label = paste0('n=',n_cell)), color = 'black', size = 4)+
  coord_cartesian(xlim = c(1, 185), expand =TRUE)+
  scale_x_log10()+
  scale_y_discrete(limits = rev)+
  labs(title = 'Expression levels of SNX2 constructs',
       subtitle = 'Cells pooled from 3 experimental repeats',
       x = 'mCherry intensity (relative to transfection threshold)',
       y = 'SNX2 construct',
       fill = '4-residue\ninsertion')+
  theme_bw(base_size = 14)
```


## Importing SNX2 isoform classifiers and extracting the noteworthy features
```{r Function to load in the classifier performance and importance, echo=FALSE}
#
Replicate_performance_and_importance <- function(MODEL_FOLDER, SET, PAIR, TRANSFECTION_STATUS, PERCENTILE_CUTOFF = 0){
  if(TRANSFECTION_STATUS == 'POSITIVE'){
    load(paste0(MODEL_FOLDER,'/',SET,'_',PAIR))
  }
  if(TRANSFECTION_STATUS == 'NEGATIVE'){
    load(paste0(MODEL_FOLDER,'/NegTransModel_',SET,'_',PAIR))
  }
  #
  modeL_fit_and_tune <- function(variable){
    a <- variable$results %>%
      dplyr::filter(!is.na(ROC)) %>% 
      dplyr::arrange(desc(ROC)) %>% 
      dplyr::slice_head(n = 1) %>% 
      dplyr::mutate(size_decay_tune = paste0('size:',size,'_decay:',decay))
    return(a)
  }
  #
  variable_importance_ranking <- function(variable){
    variable_importance <- variable$variable_importance %>% 
      arrange(desc(Overall)) %>%
      rownames_to_column(var = 'Feature') %>% 
      as_tibble()
    
    rank <- seq(1, dim(variable_importance)[1])
    
    variable_importance <- bind_cols(variable_importance, 'Rank' = rank)
    return(variable_importance)
  }
  #
  n_cells <- function(variable){
    cell_count <- variable$training_data_intensity %>% 
    count()
    return(cell_count)
  }
  #
  
  ISOFORM_MODELS <- as.list(replicate_nnet[1,]) #Converts matrix rows into lists
  NEGATIVE_MODELS <- as.list(replicate_nnet[2,])
  POSITIVE_MODELS <- as.list(replicate_nnet[3,])
  
  #
  isoform_model_fit_and_tune <- lapply(ISOFORM_MODELS, FUN = modeL_fit_and_tune)
  isoform_variable_importance <- lapply(ISOFORM_MODELS, FUN = variable_importance_ranking)
  isoform_n_cells <- lapply(ISOFORM_MODELS, FUN = n_cells)
  #
  negative_fit_and_tune <- lapply(NEGATIVE_MODELS, FUN = modeL_fit_and_tune)
  negative_variable_importance <- lapply(NEGATIVE_MODELS, FUN = variable_importance_ranking)
  negative_n_cells <- lapply(NEGATIVE_MODELS, FUN = n_cells)
  #
  positive_fit_and_tune <- lapply(POSITIVE_MODELS, FUN = modeL_fit_and_tune)
  positive_variable_importance <- lapply(POSITIVE_MODELS, FUN = variable_importance_ranking)
  positive_n_cells <- lapply(POSITIVE_MODELS, FUN = n_cells)
  
  #
  iso_performance <- bind_rows(isoform_model_fit_and_tune, .id = 'Replicate')
  neg_performance <- bind_rows(negative_fit_and_tune, .id = 'Replicate')
  pos_performance <- bind_rows(positive_fit_and_tune, .id = 'Replicate') %>% 
    rename_with(~paste0(.,"_pos"), -Replicate)
  
  #
  iso_n <- bind_rows(isoform_n_cells, .id = 'Replicate')
  neg_n <- bind_rows(negative_n_cells, .id = 'Replicate')
  pos_n <- bind_rows(positive_n_cells, .id = 'Replicate')
  n_cells_all_models <- bind_rows(iso_n, neg_n, pos_n, .id = 'Group')%>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  ###
  pair_x_performance <- bind_rows(iso_performance, neg_performance, bind_rows(positive_fit_and_tune, .id = 'Replicate'),.id = 'Group') %>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  #
  
  ###
  relative_performance <- full_join(x = iso_performance, y = neg_performance, by = c('Replicate'), suffix = c('_iso', '_neg')) %>% 
    full_join(x = ., y = pos_performance, by = c('Replicate')) %>% 
    dplyr::mutate('ROC_difference_from_neg' = ROC_iso - ROC_neg,
                  'ROC_difference_from_pos' = ROC_iso - ROC_pos,
                  'ROC_difference_pos_from_neg' = ROC_pos - ROC_neg)
  
  #
  
  ###
  number_of_classifier_iterations <- length(isoform_variable_importance)
  number_of_features <- length(unique(isoform_variable_importance[[1]]$Feature))
  #
  iso_importance <- bind_rows(isoform_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance <- bind_rows(negative_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance_reduced <- neg_importance %>% 
    dplyr::select(Feature, Rank_sum, Rank_avg, Rank_median, Rank_90_10, Rank_95_05, Overall_sum, Overall_avg, Overall_sd)
  
    #
  iso_neg_comb_importance <- dplyr::full_join(x = iso_importance, y = neg_importance_reduced, by = c('Feature'), suffix = c('','_neg')) %>% 
    dplyr::mutate('Rank_median_difference' = Rank_median_neg - Rank_median,
                  'Rank_sum_difference' = Rank_sum_neg - Rank_sum,
                  'Rank_90_10_difference' = Rank_90_10_neg - Rank_90_10,
                  'Rank_95_05_difference' = Rank_95_05_neg - Rank_95_05)
  
  
  #
  
  results_list <- list('performance' = pair_x_performance, 'SET' = SET, 'PAIR' = PAIR, 'relative_performance' = relative_performance, 'TRANSFECTION_STATUS' = TRANSFECTION_STATUS, 'PERCENTILE_CUTOFF' = PERCENTILE_CUTOFF,
                       'var_importance_iso' = iso_importance, 'var_importance_neg' = negative_variable_importance, 'var_importance_pos' = positive_variable_importance,
                       'var_importance_iso_w_contrast' = iso_neg_comb_importance, 'n_cells' = n_cells_all_models)
  return(results_list)
}
```

```{r Loading Positive transfectant models, echo = FALSE}
#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
```

```{r Loading negative transfectant models 10 percentile, echo = FALSE}
#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
```

```{r Loading exon descriptions, echo = FALSE}
#Exon description
Exon_descriptions <- readxl::read_xlsx(path = paste0(Path_to_exon_description_sheet, File_with_exon_description_sheet),
                                       sheet = Event_sheet) %>% 
  dplyr::mutate('microexon' = Exon_length_NT <= 30) %>% 
  dplyr::mutate(Gene_name_Rclassifier = case_when( #Note, currently because names in SET D are marked w. asteriks, they have to be so in this exon description file. But excel didn't like starting the name w. an asteriks.
    Gene_name_Rclassifier == 'ATXN2' ~ '*ATXN2', #Only done for the isoform pairs that are not recurring
    Gene_name_Rclassifier == 'EVI5' ~ '*EVI5',
    Gene_name_Rclassifier == 'PPFIA1' ~ '*PPFIA1',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExA' ~ 'CLASP1_ExA_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExB' ~ 'CLASP1_noEx_vs_ExB',
    .default = Gene_name_Rclassifier))

Exon_descriptions_reduced <- Exon_descriptions %>% 
  dplyr::select(microexon, Splice_event_enriched_in_neural_tissue, Splice_event_enriched_in_pancreatic_islet_cells, Enrichment_comment, Exon_length_NT, Gene_name_Rclassifier, Exon_name_Rclassifier, EVENT_ID_vastDB, Location_in_protein) %>% 
  dplyr::filter(!c(Gene_name_Rclassifier == 'VAV2')) #Current_naming_doesn't_work_well_with_genes_with_multiple_exons

### ISOFORM_PAIRS_EXCLUDE
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_DOUBLES <- c('VAV2','*SH3KBP1_D/E','*OCRL_D/E','*SH3GLB1_D/E')
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_INTENSITY <- c('VAV2','PACSIN2') ##THIS DEFINES WHICH ISOFORM PAIRS ARE EXCLUDED.

```


```{r combining absolute classifier outputs into proper datasets, echo = FALSE}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set 1A
combined_model_performance_SET_1A <- bind_rows(mget(ls(pattern = 'model_performance_SET_1A_PAIR'))) #Will contain both SET_1A normal comps and alternative CLASP1 comparisons
rm(list = ls(pattern = 'model_performance_SET_1A_PAIR'))

#All
combined_model_performance_all <- bind_rows(mget(ls(pattern = 'combined_model_performance_SET_'))) %>%  #WRITE CASE_WHEN TO GIVE ALL SET + PAIR COMBINATIONS THEIR GENE NAME (COULD POTENTIALLY BE GENE + EXON ID -> ALTHOUGH COMBINATIONS GET TRICKY STILL)
  dplyr::mutate('Gene_name' = case_when(
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2'
   )) %>% 
  #left_join(., y = SUMMARY_of_all_sample_ratios, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) %>% 
  left_join(., y = Exon_descriptions_reduced, by = join_by('Gene_name' == 'Gene_name_Rclassifier')) %>% 
  #The fusion doesn't work perfectly for genes with multiple events - the line below removes an unwanted duplication of the VAV2 data (NOTE, THIS IS WHAT GIVES RISE TO THE MANY-TO-MANY RELATIONSHIP)
  dplyr::filter(!c(SET == 'SET_1A' & Gene_name == 'VAV2' & Exon_name_Rclassifier == 'ExB')) %>% 
  #
  dplyr::mutate(microexon = case_when( #Hacky way of making all events have microexon, yes/no label
    word(Gene_name, 1, 1, sep = fixed('_')) == '*APP' ~ FALSE,
    word(Gene_name, 1, 1, sep = fixed('_')) == '*VAV2' ~ TRUE,
    word(Gene_name, 1, 1, sep = fixed('_')) == 'CLASP1' ~ TRUE,
    .default = microexon))
#

#Dataframe w. the gene name SET + PAIR combination
gene_ids_match <- combined_model_performance_all %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB) %>%
  unique()

#Dataframe w. n used for classifier and the gene names
n_used_for_classifier <- combined_model_performance_all %>% 
  dplyr::select(n, Gene_name) %>% 
  unique() %>% 
  dplyr::group_by(Gene_name) %>% 
  summarize(n = mean(n))

```


```{r creating relative ROC that compares negative transfectant and positive transfectant ROCs, echo = FALSE}
#Splitting the combined ROC dataset according to transfection status
#Positive transfectants
combined_model_performance_all_postrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE')
#Negative transfectants
combined_model_performance_all_negtrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE')

#Joining positive and negative transfectants in a wide-format
combined_model_performance_all_posneg_relative <- full_join(x = combined_model_performance_all_postrans, y = combined_model_performance_all_negtrans,
                                                            by = join_by(SET, ISOFORM_PAIR, Group, Replicate),
                                                            suffix = c('_postrans', '_negtrans')) %>%
  # Creating ROC relative column (pos - neg). Can be negative.
  dplyr::mutate(ROC_posneg_relative = ROC_postrans - ROC_negtrans,
                tmp_norm_ROC = (ROC_postrans - ROC_negtrans)/(1 - ROC_negtrans),
                Ceiling_normalised_ROC = if_else(tmp_norm_ROC >= 0, tmp_norm_ROC, (ROC_postrans - ROC_negtrans)/(1 - ROC_postrans)))
  # Creating ROC relative column (pos - neg). If Neg > pos, it is set to 0   
  #dplyr::mutate(ROC_posneg_relative = if_else(ROC_postrans >= ROC_negtrans, ROC_postrans - ROC_negtrans, 0))
    
```



```{r Function to perform bootstrap confidence interval caluclations, echo = FALSE}
#' Bootstrap Test for Pre-Normalized ROC Scores with Group Support
#'
#' This function calculates bootstrap confidence intervals for normalized ROC scores
#' that have already been calculated. It supports grouping by a variable (e.g., gene name).
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param group_value Value to filter by in the group column (e.g., specific gene name)
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#'
#' @return A list containing bootstrap statistics and test results
#'
#' @examples
#' # Example with pre-calculated normalized values
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2))
#' )
#' result <- bootstrap_norm_roc_grouped(data, "norm_roc", "Gene_name", "Gene1")
#' print(result)
#'
bootstrap_norm_roc_grouped <- function(data, 
                                       norm_col = "norm_roc", 
                                       group_col = NULL,
                                       group_value = NULL,
                                       conf_level = 0.95,
                                       n_bootstrap = 2000,
                                       one_sided = TRUE) {
  
  # Require boot package
  if (!requireNamespace("boot", quietly = TRUE)) {
    stop("Please install the 'boot' package: install.packages('boot')")
  }
  
  # Filter data by group if specified
  if (!is.null(group_col) && !is.null(group_value)) {
    if (!(group_col %in% colnames(data))) {
      stop(paste("Group column", group_col, "not found in data"))
    }
    data <- data[data[[group_col]] == group_value, ]
    if (nrow(data) == 0) {
      stop(paste("No data found for", group_col, "=", group_value))
    }
  }
  
  # Check if norm_col exists
  if (!(norm_col %in% colnames(data))) {
    stop(paste("Normalized score column", norm_col, "not found in data"))
  }
  
  # Extract normalized scores
  norm_scores <- data[[norm_col]]
  
  # Function for bootstrapping
  boot_func <- function(data, indices) {
    return(mean(data[indices]))
  }
  
  # Perform bootstrap
  boot_result <- boot::boot(norm_scores, boot_func, R = n_bootstrap)
  
  # Calculate confidence interval
  if (one_sided) {
    # One-sided interval (lower bound only)
    alpha <- 1 - conf_level
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound of percentile interval
    upper_bound <- Inf
  } else {
    # Two-sided interval
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound
    upper_bound <- ci$percent[5]  # Upper bound
  }
  
  # Determine if zero is in the confidence interval
  zero_in_ci <- (lower_bound <= 0 && upper_bound >= 0)
  
  # Create summary results
  result <- list(
    mean = mean(norm_scores),
    median = median(norm_scores),
    sd = sd(norm_scores),
    ci_lower = lower_bound,
    ci_upper = ifelse(one_sided, Inf, upper_bound),
    one_sided = one_sided,
    conf_level = conf_level,
    zero_in_ci = zero_in_ci,
    significant = !zero_in_ci,
    n_iterations = length(norm_scores),
    n_bootstrap = n_bootstrap,
    group_col = group_col,
    group_value = group_value,
    raw_scores = norm_scores,
    boot_result = boot_result
  )
  
  return(result)
}

#' Run Bootstrap Tests for Multiple Groups
#'
#' This function runs bootstrap tests for multiple groups and returns results in a data frame
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#' @param adjust_method Method for multiple testing correction (default "BH"). Options include 
#'                     "holm", "hochberg", "hommel", "bonferroni", "BH", "BY", "fdr", "none"
#'
#' @return A data frame with bootstrap test results for each group, including adjusted p-values
#'
#' @examples
#' # Example with pre-calculated normalized values for multiple genes
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2", "Gene3"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2), rnorm(50, 0.15, 0.15))
#' )
#' results <- bootstrap_multiple_groups(data, "norm_roc", "Gene_name")
#' print(results)
#'
bootstrap_multiple_groups <- function(data, 
                                      norm_col = "norm_roc", 
                                      group_col,
                                      conf_level = 0.95,
                                      n_bootstrap = 2000,
                                      one_sided = TRUE,
                                      adjust_method = "BH") {
  
  # Get unique groups
  groups <- unique(data[[group_col]])
  
  # Create empty results data frame
  results <- data.frame(
    group = character(),
    mean = numeric(),
    median = numeric(),
    sd = numeric(),
    ci_lower = numeric(),
    ci_upper = numeric(),
    p_value = numeric(),
    significant = logical(),
    adj_p_value = numeric(),
    adj_significant = logical(),
    n_iterations = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Loop through groups
  group_results <- list()
  p_values <- numeric(length(groups))
  
  for (i in seq_along(groups)) {
    group <- groups[i]
    # Run bootstrap test
    boot_result <- bootstrap_norm_roc_grouped(
      data = data,
      norm_col = norm_col,
      group_col = group_col,
      group_value = group,
      conf_level = conf_level,
      n_bootstrap = n_bootstrap,
      one_sided = one_sided
    )
    
    # Calculate p-value from bootstrap distribution
    if (one_sided) {
      # For one-sided test, calculate p-value as proportion of bootstrap values <= 0
      p_value <- mean(boot_result$boot_result$t <= 0)
    } else {
      # For two-sided test, calculate p-value based on whether 0 is in the CI
      # This is approximate but aligns with the confidence interval approach
      z_stat <- boot_result$mean / (boot_result$sd / sqrt(boot_result$n_iterations))
      p_value <- if (boot_result$mean >= 0) 2 * pnorm(-abs(z_stat)) else 2 * pnorm(-abs(z_stat))
    }
    
    p_values[i] <- p_value
    
    # Store result
    group_results[[i]] <- data.frame(
      group = group,
      mean = boot_result$mean,
      median = boot_result$median,
      sd = boot_result$sd,
      ci_lower = boot_result$ci_lower,
      ci_upper = ifelse(one_sided, Inf, boot_result$ci_upper),
      p_value = p_value,
      significant = boot_result$significant,
      n_iterations = boot_result$n_iterations
    )
  }
  
  # Adjust p-values for multiple testing
  adj_p_values <- p.adjust(p_values, method = adjust_method)
  
  # Combine results
  results <- do.call(rbind, group_results)
  results$adj_p_value <- adj_p_values
  results$adj_significant <- results$adj_p_value < (1 - conf_level)
  
  # Return results
  return(results)
}

#' Visualize Bootstrap Distribution
#'
#' Creates a histogram of bootstrap means with confidence interval
#'
#' @param boot_result Result from bootstrap_norm_roc_grouped function
#' @param bins Number of histogram bins (default 30)
#'
#' @return A ggplot2 object
#'
plot_bootstrap_dist <- function(boot_result, bins = 30) {
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Extract bootstrap samples
  t_values <- boot_result$boot_result$t
  
  # Create dataframe for plotting
  df <- data.frame(value = t_values)
  
  # Determine title suffix based on grouping
  group_suffix <- ""
  if (!is.null(boot_result$group_col) && !is.null(boot_result$group_value)) {
    group_suffix <- paste(" for", boot_result$group_col, "=", boot_result$group_value)
  }
  
  # Create plot
  p <- ggplot2::ggplot(df, ggplot2::aes(x = value)) +
    ggplot2::geom_histogram(bins = bins, fill = "steelblue", color = "white", alpha = 0.7) +
    ggplot2::geom_vline(xintercept = boot_result$ci_lower, color = "red", linetype = "dashed") +
    ggplot2::geom_vline(xintercept = 0, color = "black", linetype = "solid") +
    ggplot2::labs(
      title = paste0("Bootstrap Distribution of Normalized ROC Score", group_suffix),
      subtitle = paste0(
        ifelse(boot_result$one_sided, "One-sided ", "Two-sided "), 
        boot_result$conf_level * 100, "% CI: [", 
        round(boot_result$ci_lower, 4), ", ", 
        ifelse(boot_result$one_sided, "∞", round(boot_result$ci_upper, 4)), "]"
      ),
      x = "Normalized ROC Score",
      y = "Frequency",
      caption = paste("Mean:", round(boot_result$mean, 4), 
                      "| Significant:", boot_result$significant)
    ) +
    ggplot2::theme_minimal()
  
  return(p)
}

#' Create Forest Plot of Bootstrap Results
#'
#' Creates a forest plot of bootstrap results for multiple groups
#'
#' @param results Data frame from bootstrap_multiple_groups function
#' @param sort_by Column to sort by (default "mean")
#' @param decreasing Logical; if TRUE, sorts in decreasing order (default TRUE)
#' @param color_by_significance Logical; if TRUE, colors points by significance (default TRUE)
#'
#' @return A ggplot2 object
#'
plot_forest <- function(results, 
                        sort_by = "mean", 
                        decreasing = TRUE,
                        color_by_significance = TRUE,
                        use_adjusted_significance = TRUE) {
  
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Sort results
  results <- results[order(results[[sort_by]], decreasing = decreasing), ]
  
  # Make sure group is a factor in the right order for plotting
  results$group <- factor(results$group, levels = results$group)
  
  # Determine which significance column to use
  sig_col <- if(use_adjusted_significance && "adj_significant" %in% colnames(results)) {
    "adj_significant"
  } else {
    "significant"
  }
  
  # Create plot
  p <- ggplot2::ggplot(results, ggplot2::aes(x = mean, y = group)) +
    ggplot2::geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_lower, xmax = ci_upper), height = 0.2) +
    ggplot2::geom_point(ggplot2::aes(color = if(color_by_significance) .data[[sig_col]] else NULL), 
                        size = 3) +
    scale_y_discrete(limits = rev(levels(results$group)))+
    ggplot2::labs(
      title = paste0("Normalized ROC Scores with Bootstrap Confidence Intervals",
                     ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                            "\n(adjusted for multiple testing)", "")),
      x = "Normalized ROC Score",
      y = NULL,
      subtitle = ifelse("adj_p_value" %in% colnames(results), 
                        paste0("Multiple testing correction: ", 
                               ifelse(any(results$adj_p_value != results$p_value), "Applied", "None")),
                        "")
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      axis.text.y = ggplot2::element_text(size = 10),
      legend.position = "bottom"
    )
  
  # Add color scale if coloring by significance
  if (color_by_significance) {
    p <- p + ggplot2::scale_color_manual(
      values = c("FALSE" = "gray50", "TRUE" = "steelblue"),
      name = ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                    "Significant (Adjusted)", "Significant"),
      labels = c("FALSE" = "No", "TRUE" = "Yes")
    )
  }
  
  return(p)
}

# Example usage:
# # Create sample data with pre-calculated normalized ROC values
# set.seed(123)
# data <- data.frame(
#   Gene_name = rep(c("Gene1", "Gene2", "Gene3", "Gene4"), each = 50),
#   norm_roc = c(rnorm(50, 0.3, 0.1), 
#               rnorm(50, -0.1, 0.2), 
#               rnorm(50, 0.15, 0.15),
#               rnorm(50, 0.05, 0.1))
# )
# 
# # Test a single gene
# result_gene1 <- bootstrap_norm_roc_grouped(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name",
#   group_value = "Gene1"
# )
# print(result_gene1)
# plot1 <- plot_bootstrap_dist(result_gene1)
# print(plot1)
# 
# # Test all genes
# results_all <- bootstrap_multiple_groups(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name"
# )
# print(results_all)
# 
# # Create forest plot
# plot2 <- plot_forest(results_all)
# print(plot2)

# Remove a specific item from legend
# If you need to remove an item from a ggplot2 legend (such as color), 
# you can use the following approach after creating your plot:

# Example:
# p <- plot_forest(results_all, use_adjusted_significance = TRUE)
# 
# # To remove the color legend completely:
# p <- p + ggplot2::theme(legend.position = "none")
# 
# # To keep the legend but remove specific guides:
# p <- p + ggplot2::guides(color = "none")
# 
# # To create a table of results
# library(knitr)
# results_table <- results_all[, c("group", "mean", "ci_lower", "ci_upper", 
#                                 "p_value", "adj_p_value", "adj_significant")]
# results_table <- results_table[order(results_table$adj_p_value), ]
# kable(results_table, digits = 4)
# 
# print(p)
```

This code runs the bootstrap confidence interval testing so we can select statisticallyt signfiicant isos
```{r Calculating bootstrap confidence intervals and creates confidence interval plot, echo=FALSE}
bootstrap_scores <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform'), 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = confidence_interval_threshold_for_bootstrap,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH") 

#Note, p-values are zero or 1 in most cases - anyhow, we can just indicate significance, I guess.

#Could include this plot as supplementary (?)
```


```{r Loading variable importance classifier data, echo = FALSE}
#Variable importance
combined_variable_importance_set_1A <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR'))
#
combined_variable_importance_all <- bind_rows(mget(ls(pattern = 'combined_variable_importance_set_'))) %>%
  left_join(x = ., y = gene_ids_match, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) 

#
combined_overall <- combined_variable_importance_all %>% 
  ungroup() %>% 
  group_by(Gene_name, TRANSFECTION_STATUS) %>% 
  summarize('Combined_overall' = sum(Overall_avg),
            'Combined_overall_neg' = sum(Overall_avg_neg))%>% 
  dplyr::arrange(Combined_overall)


combined_variable_importance_all_w_overall <- combined_variable_importance_all %>% 
  left_join(., x = combined_overall, by = join_by('Gene_name' == 'Gene_name', 'TRANSFECTION_STATUS' == 'TRANSFECTION_STATUS')) %>%
  dplyr::mutate('contribution_prop' = (Overall_avg/Combined_overall)*100,
                'contribution_prop_sd' = (Overall_sd/Combined_overall)*100,
                'contribution_prop_neg' = (Overall_avg_neg/Combined_overall_neg)*100,
                'contribution_prop_neg_sd' = (Overall_sd_neg/Combined_overall_neg)*100)

# Combining the variable importance data for negtrans and postrans in a wider format
# Positive transfectants
combined_variable_importance_all_w_overall_postrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)
# Negative transfectants
combined_variable_importance_all_w_overall_negtrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)

# Combined positive and negative transfectants
combined_variable_importance_all_w_overall_posneg <- combined_variable_importance_all_w_overall_postrans %>% 
  # Joining variable importance for postrans and negtrans
  dplyr::left_join(x = ., y = combined_variable_importance_all_w_overall_negtrans, by = join_by(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, Feature), suffix = c('_pos', '_neg')) %>% 
  # Introducing the contribution proportion ratio (postrans/negtrans)
  dplyr::mutate(contribution_prop_ratio = contribution_prop_pos/contribution_prop_neg,
                contribution_prop_ratio_negcontrol = contribution_prop_negcontrol_pos/contribution_prop_negcontrol_neg,
                ratio_times_importance = contribution_prop_ratio * contribution_prop_pos,
                noteworthy_feature = if_else(ratio_times_importance >= ratio_times_importance_threshold & contribution_prop_ratio > ratio_threshold, TRUE, FALSE)) %>% 
  # Add p-values from the bootstrapping confidence intervals
    left_join(x = .,
            y = bootstrap_scores %>% dplyr::select(group, adj_p_value, adj_significant),
            by = join_by('Gene_name' == 'group'))
```


```{r Selecting noteworthy SNX2 isoform features to use for PCA, echo = FALSE}
SNX2_noteworthy_features <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name == 'SNX2') %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::arrange(desc(ratio_times_importance)) %>% 
  dplyr::pull(Feature)
```


# Reducing the number of features used to describe constructs by identifying and removing correlated features
## Loose intensity filtering
### Creating distance matrix related to feature pearson correlations on measurements on single cells
#### Creating distance matrix and heatmap
```{r Correlation heatmap calculated on single cells Loose intensity filtering, echo=FALSE}
# Creating reduced dataframe of single cell measurements containing only isoform distinguishing features and key metadata (well and construct)
df_snx2_distinguishing_sc_loose <- Transfected_only_without_outliers_SNX2muts_loose_intensity  %>% 
    dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')) %>% 
    dplyr::select(Metadata_Well, Construct, all_of(SNX2_noteworthy_features))

# Creating single cell feature matrix of the isoform distinguishing features
feature_matrix_sc_loose <- df_snx2_distinguishing_sc_loose %>% 
  dplyr::select(where(is.numeric))

# Creating correlation matrix on single cell measurements
correlation_matrix_sc_loose <- cor(feature_matrix_sc_loose, use = 'pairwise.complete.obs', method = 'pearson')

## Heat map colours ##
heatmap_colors <- colorRampPalette(c("#2166ac","white","#b2182b"))(100)

```


```{r Distance matrix based on pearsons correlation, echo=FALSE}
# Creates a distance matrix based on the correlation matrix. Scales it to be consistent (between 1 and -1)
dist_mat_new_loose <- as.dist(1 - correlation_matrix_sc_loose)
hclust_obj_new_loose <- hclust(dist_mat_new_loose, method = 'complete')
# Creates clusters (they are used later, but defined here because the script is a bit messy)
cut_height_new_loose <- 0.3
clusters_new_loose <- cutree(hclust_obj_new_loose, h = cut_height_new_loose)

# Creates heatmap using the distance matrix above. This uses the correlation-based distance rahter than euclidean distance
p_heatmap_new_loose <- pheatmap::pheatmap(
  correlation_matrix_sc_loose,
  clustering_distance_rows = dist_mat_new_loose,
  clustering_distance_col = dist_mat_new_loose,
  clustering_method = 'complete',
  color = heatmap_colors,
  treeheight_row = 40, #show row dendrogram
  treeheight_col = 0, #hide col dendrogram (redundant with row)
  show_rownames = TRUE,
  show_colnames = FALSE,
  fontsize_row = 6, # shrink depending on number of features
  border_color = NA
)
print(p_heatmap_new_loose)
```

#### Creates dendrogram and identify features to remove based on correlation for single cells
```{r Identify features to remove using single cell calculated feature pearson correlations loose intensities, echo=FALSE}
# Creates dendrogram from heatmap object. Note agian, that the distance metric is correlation rather than euclidean distance
dendrogram_data_sc_loose <- dendro_data(hclust_obj_new_loose, type = 'rectangle')

# Create dendrogram plot
dendrogram_plot_sc_loose <- ggplot()+
  geom_segment(data = segment(dendrogram_data_sc_loose), aes(x = x, y = y, xend = xend, yend = yend))+
  geom_hline(yintercept = cut_height_new_loose, color = '#b2182b', linetype = 'dashed',linewidth = 0.6)+
  annotate('text', x = max(segment(dendrogram_data_sc_loose)$x) * 0.95,
           y = cut_height_new_loose + 0.15,
           label = paste0('cut = ',cut_height_new_loose),
           color = '#b2182b',
           size = 5)+
  scale_y_continuous(
    expand = expansion(mult = c(0, 0.05)),
    name = 'Cluster height')+
  scale_x_continuous(expand = expansion(mult = c(0.02, 0.02)))+
  coord_flip()+
  theme_bw(base_size = 16)+
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.title.y = element_blank(),
    panel.grid = element_blank()
  )+
  labs(title = 'Feature clustering dendrogram')
dendrogram_plot_sc_loose


# Pre-compute per-feature variance across all cells
feature_var_new_loose <- map_dbl(scale(feature_matrix_sc_loose) %>%  as_tibble(), var)

# Selects what features. Selects one feature per cluster, selcting the one with the highest variance between cells
features_to_keep_sc_new_loose <- split(names(clusters_new_loose), clusters_new_loose) %>% 
  map_chr(function(cluster_feats_sc_new_loose){
    if(length(cluster_feats_sc_new_loose) == 1) return(cluster_feats_sc_new_loose)
       cluster_feats_sc_new_loose[which.max(feature_var_new_loose[cluster_feats_sc_new_loose])]
  }) %>% 
  unname()
# Creates object of removed features
features_to_remove_sc_new_loose <- setdiff(names(clusters_new_loose), features_to_keep_sc_new_loose)

# PRints results of feature selection
cat('Features retained: ', length(features_to_keep_sc_new_loose),'\n')
cat('Features removed: ', length(features_to_remove_sc_new_loose),'\n')
cat('\nRemoved features:\n')
print(sort(features_to_remove_sc_new_loose))

cat('\nKept features:\n')
print(sort(features_to_keep_sc_new_loose))
```
# PCA of constructs using the reduced features as input
The PCA is performed on single cells, then centroids are created for each construct by taking the mean PC scores for all cells. These are plotted
```{r PCA using centroids function, echo = FALSE}
# Function for PCA analysis using single-cell measurements with centroid-based plots
run_pca_analysis <- function(
    data,                       # Your data frame (one row per cell)
    condition_col = "condition_id", # Column name for condition IDs
    selected_features,          # Vector of feature column names to use for PCA
    do_center = TRUE,           # Whether to center the data
    do_scale = TRUE,            # Whether to scale the data
    num_clusters = 4,           # Number of clusters to create
    pc_x = 1,                   # PC for x-axis in plots
    pc_y = 2,                   # PC for y-axis in plots
    add_ellipses = TRUE,        # Whether to add confidence ellipses to centroid plot
    add_labels = TRUE,          # Whether to add labels to points
    point_size = 3,             # Size of points in plots
    use_numbered_biplot = TRUE, # Whether to use numbers instead of text in biplot
    biplot_color_by = "none",   # Color biplot points: "none", "cluster", or "condition"
    color_arrows_by_category = FALSE, # Color arrows by first word in variable name
    show_point_numbers = TRUE,  # Show or hide the numbers on points in the biplot
    num_pcs_for_clustering = 3,  # Number of PCs to use for hierarchical clustering
    reference_conditions = c("-EX (rep1)", "-EX (rep2)", "-EX (rep3)", "+EX"), # Conditions to show in the reference heatmap
    colour_col = "exon_present",  # Column to colour points by (binary TRUE/FALSE)
    colour_values = c("TRUE" = "#00BFC4", "FALSE" = "#F8766D"), # Colours for the two values
    point_stroke = 0.8,           # Stroke thickness for condition/cluster plot points
    heatmap_subset_features = NULL   # Character vector of features (columns) to include in subset heatmap (NULL = all)
) {
  
  # Load required packages
  require(dplyr)
  require(tidyr)
  require(ggplot2)
  require(factoextra)
  require(ggdendro)
  require(ggrepel)
  require(stringr)
  require(RColorBrewer)
  require(ggnewscale)
  
  # ── Input checks ─────────────────────────────────────────────────────────────
  if (!condition_col %in% colnames(data)) {
    stop(paste("Condition column", condition_col, "not found in the data."))
  }
  
  if (!all(selected_features %in% colnames(data))) {
    missing <- selected_features[!selected_features %in% colnames(data)]
    stop(paste("Feature(s) not found in data:", paste(missing, collapse = ", ")))
  }
  
  if (!biplot_color_by %in% c("none", "cluster", "condition")) {
    warning("biplot_color_by must be 'none', 'cluster', or 'condition'. Defaulting to 'none'.")
    biplot_color_by <- "none"
  }
  
  # ── Step 1: Run PCA on ALL single cells ──────────────────────────────────────
  # Store condition labels aligned to cells (used later for centroids)
  cell_conditions <- data[[condition_col]]
  
  pca_result <- prcomp(data[, selected_features],
                       center = do_center,
                       scale. = do_scale)
  
  # ── Step 2: Calculate variance explained ─────────────────────────────────────
  var_explained     <- pca_result$sdev^2
  var_explained_pct <- 100 * var_explained / sum(var_explained)
  cum_var_explained <- cumsum(var_explained_pct)
  
  variance_df <- data.frame(
    PC              = paste0("PC", 1:length(var_explained)),
    var_explained_pct = var_explained_pct,
    cum_var_explained = cum_var_explained
  )
  
  # Individual variance bar chart
  p_var_ind <- ggplot(variance_df, aes(x = PC, y = var_explained_pct)) +
    geom_col(fill = "steelblue") +
    geom_text(aes(label = sprintf("%.1f%%", var_explained_pct)), vjust = -0.5, size = 3) +
    labs(title = "Percentage of Variance Explained by Each PC",
         x = "Principal Component",
         y = "Percent of Variance Explained") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  # Cumulative variance line chart
  p_var_cum <- ggplot(variance_df, aes(x = PC, y = cum_var_explained)) +
    geom_line(group = 1, color = "steelblue") +
    geom_point(color = "steelblue", size = 3) +
    geom_text(aes(label = sprintf("%.1f%%", cum_var_explained)), vjust = -0.7, size = 3) +
    labs(title = "Cumulative Percentage of Variance Explained",
         x = "Principal Component",
         y = "Cumulative Percent of Variance") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1))
  
  # factoextra scree plot (based on full single-cell PCA)
  p_scree <- fviz_eig(pca_result,
                      addlabels  = TRUE,
                      labelsize  = 8,
                      ncp        = 5,
                      barfill    = "steelblue",
                      barcolor   = "steelblue",
                      linecolor  = "red") +
    scale_y_continuous(limits = c(0, 100),
                       breaks = seq(0, 100, 20),
                       expand = c(0, 0)) +
    labs(title = "Scree Plot: Variance Explained by Principal Components") +
    theme_bw(base_size = 16)
  
  # ── Step 3: Compute per-condition centroids in PC space ───────────────────────
  # Full cell scores (all PCs)
  all_cell_scores <- as.data.frame(pca_result$x)
  all_cell_scores[[condition_col]] <- cell_conditions
  
  # Centroid = mean PC score per condition across all PCs
  centroids <- all_cell_scores %>%
    group_by(!!sym(condition_col)) %>%
    summarise(across(starts_with("PC"), mean, na.rm = TRUE), .groups = "drop")
  
  # Extract variance % for axis labels
  var_exp_x <- var_explained_pct[pc_x]
  var_exp_y <- var_explained_pct[pc_y]
  
  pc_x_name <- paste0("PC", pc_x)
  pc_y_name <- paste0("PC", pc_y)
  
  # ── Step 4: Hierarchical clustering on centroids (up to 5 PCs) ───────────────
  num_pcs_for_clustering <- min(num_pcs_for_clustering, ncol(pca_result$x))
  pc_cols_for_clust      <- paste0("PC", 1:num_pcs_for_clustering)
  
  centroid_pc_mat <- centroids[, pc_cols_for_clust]
  dist_matrix     <- dist(centroid_pc_mat)
  hc              <- hclust(dist_matrix, method = "ward.D2")
  
  # Dendrogram plot (labels are condition names)
  dend      <- as.dendrogram(hc)
  dend_data <- dendro_data(dend, type = "rectangle")
  
  p_dend <- ggplot(segment(dend_data)) +
    geom_segment(aes(x = x, y = y, xend = xend, yend = yend)) +
    geom_text(data  = label(dend_data),
              aes(x = x, y = y, label = label),
              hjust = 0, size = 3, angle = 90) +
    labs(title = "Hierarchical Clustering of Conditions (centroid-based)",
         x = "", y = "Height") +
    theme_minimal() +
    theme(axis.text.x  = element_blank(),
          axis.ticks.x = element_blank())
  
  # Cut dendrogram and attach cluster labels to centroids
  # cutree() returns a named integer vector: names are row indices (1, 2, 3...),
  # not condition names, so we assign by position rather than by name lookup.
  clusters          <- cutree(hc, k = num_clusters)
  centroids$cluster <- as.factor(clusters)   # centroids rows match hclust order
  
  
  # ── Condition and cluster plots ───────────────────────────────────────────────
  # Encoding:
  #   fill   = binary colour_col variable (TRUE/FALSE) → interior of shape
  #   shape  = condition identity WITHIN each fill group (shapes 0-14, restarting
  #             for each fill group so shape+fill together uniquely ID condition)
  #   colour = fixed dark border so shapes are visible against any background
  #
  # FALSE conditions get shapes 0, 1, 2...
  # TRUE  conditions get shapes 0, 1, 2... (same set, different fill)
  # Shape overlaps between groups are intentional and fine — fill distinguishes them.
  
  pca_centroid <- pca_result
  centroid_matrix <- as.matrix(centroids[, paste0("PC", 1:ncol(pca_result$x))])
  rownames(centroid_matrix) <- centroids[[condition_col]]
  pca_centroid$x <- centroid_matrix
  
  # Compute per-condition value of colour_col (majority vote, robust to edge cases)
  if (!is.null(colour_col) && colour_col %in% colnames(data)) {
    condition_colour_map <- data %>%
      group_by(!!sym(condition_col)) %>%
      summarise(colour_val = as.character(names(which.max(table(.data[[colour_col]])))),
                .groups = "drop")
    centroids <- centroids %>%
      left_join(condition_colour_map, by = condition_col)
  } else {
    centroids$colour_val <- "unknown"
  }
  
  # Assign shapes within each fill group (FALSE first, then TRUE)
  ggplot2_shapes <- 0:14
  
  shape_assignment <- centroids %>%
    select(all_of(condition_col), colour_val) %>%
    arrange(colour_val) %>%          # FALSE sorts before TRUE alphabetically
    group_by(colour_val) %>%
    mutate(shape_val = ggplot2_shapes[row_number()]) %>%
    ungroup()
  
  condition_shapes <- setNames(shape_assignment$shape_val,
                               shape_assignment[[condition_col]])
  
  # Fill colours for the binary variable
  fill_colours <- colour_values
  
  # Point data for manual layers
  point_data <- centroids %>%
    select(
      x         = all_of(pc_x_name),
      y         = all_of(pc_y_name),
      condition = all_of(condition_col),
      fill_val  = colour_val,
      cluster
    )
  
  # fviz base (geom="none") gives us the correct axis scaling and theme
  p_fviz_base <- fviz_pca_ind(
    pca_centroid,
    axes  = c(pc_x, pc_y),
    geom  = "none",
    label = "none",
    title = ""
  )
  
  # Build p_cond
  # The legend shows shape + fill together per condition so both encodings
  # are readable. We suppress the fill legend and fold everything into the
  # shape legend via override.aes.
  legend_fills <- fill_colours[shape_assignment$colour_val]
  names(legend_fills) <- shape_assignment[[condition_col]]
  
  p_cond <- p_fviz_base +
    geom_point(
      data        = point_data,
      aes(x = x, y = y, shape = condition, colour = fill_val),
      size        = point_size,
      stroke      = point_stroke,
      inherit.aes = FALSE
    ) +
    scale_shape_manual(
      values = condition_shapes,
      name   = "Condition",
      guide  = guide_legend(
        ncol         = 2,
        override.aes = list(
          colour = unname(legend_fills[levels(factor(point_data$condition))]),
          size   = 3
        )
      )
    ) +
    scale_colour_manual(values = fill_colours, name = colour_col) +
    labs(
      x     = paste0("PC", pc_x, " (", round(var_exp_x, 1), "%)"),
      y     = paste0("PC", pc_y, " (", round(var_exp_y, 1), "%)"),
      title = paste0("PCA centroids by condition (PC", pc_x, " vs PC", pc_y, ")")
    ) +
    theme(legend.text = element_text(size = 8))
  
  if (add_labels) {
    p_cond <- p_cond +
      geom_text_repel(
        data        = point_data,
        aes(x = x, y = y, label = condition),
        size        = 3,
        max.overlaps = 20,
        inherit.aes = FALSE,
        show.legend = FALSE
      )
  }
  
  # ── Cluster plot: hull polygons drawn BEFORE points so shapes aren't obscured ──
  hull_data <- point_data %>%
    group_by(cluster) %>%
    slice(chull(x, y)) %>%
    ungroup()
  
  cluster_levels  <- levels(centroids$cluster)
  cluster_colours <- setNames(
    RColorBrewer::brewer.pal(max(3, length(cluster_levels)), "Dark2")[seq_along(cluster_levels)],
    cluster_levels
  )
  
  p_clust <- p_fviz_base +
    geom_polygon(
      data        = hull_data,
      aes(x = x, y = y, fill = cluster, colour = cluster),
      alpha       = 0.15,
      linewidth   = 0.6,
      linetype    = "dashed",
      inherit.aes = FALSE,
      show.legend = TRUE
    ) +
    scale_fill_manual(values = cluster_colours, name = "Cluster") +
    scale_colour_manual(values = cluster_colours, name = "Cluster") +
    ggnewscale::new_scale_colour() +
    geom_point(
      data        = point_data,
      aes(x = x, y = y, shape = condition, colour = fill_val),
      size        = point_size,
      stroke      = point_stroke,
      inherit.aes = FALSE
    ) +
    scale_shape_manual(
      values = condition_shapes,
      name   = "Condition",
      guide  = guide_legend(
        ncol         = 2,
        override.aes = list(
          colour = unname(legend_fills[levels(factor(point_data$condition))]),
          size   = 3
        )
      )
    ) +
    scale_colour_manual(values = fill_colours, name = colour_col) +
    labs(
      x     = paste0("PC", pc_x, " (", round(var_exp_x, 1), "%)"),
      y     = paste0("PC", pc_y, " (", round(var_exp_y, 1), "%)"),
      title = paste0("PCA centroids by cluster (PC", pc_x, " vs PC", pc_y,
                     ", k=", num_clusters, ")")
    ) +
    theme(legend.text = element_text(size = 8))
  
  if (add_labels) {
    p_clust <- p_clust +
      geom_text_repel(
        data        = point_data,
        aes(x = x, y = y, label = condition),
        size        = 3,
        max.overlaps = 20,
        inherit.aes = FALSE,
        show.legend = FALSE
      )
  }
  
  # ── Step 6: Biplot (loadings from full single-cell PCA) ──────────────────────
  # Scores shown are centroids; arrows are from the single-cell rotation matrix
  scores <- centroids
  
  loadings <- as.data.frame(pca_result$rotation[, c(pc_x, pc_y)])
  colnames(loadings) <- c(pc_x_name, pc_y_name)
  
  # Scale loadings to be visible alongside centroid spread
  loading_scale     <- max(abs(c(centroids[[pc_x_name]], centroids[[pc_y_name]]))) * 0.8
  loadings$xend     <- loadings[[pc_x_name]] * loading_scale
  loadings$yend     <- loadings[[pc_y_name]] * loading_scale
  
  var_lookup <- data.frame(
    var_name = rownames(loadings),
    var_num  = 1:nrow(loadings)
  )
  
  # Optional: colour arrows by feature category (first word before underscore)
  if (color_arrows_by_category) {
    var_categories <- str_extract(rownames(loadings), "^[^_]+")
    var_categories[is.na(var_categories)] <- rownames(loadings)[is.na(var_categories)]
    
    if (length(unique(var_categories)) > 6) {
      top_categories <- names(sort(table(var_categories), decreasing = TRUE)[1:5])
      var_categories[!var_categories %in% top_categories] <- "Other"
    }
    loadings$category  <- var_categories
    var_lookup$category <- var_categories
  }
  
  # ── Biplot: arrows only, coloured by feature name ────────────────────────────
  # Add feature name to loadings for colour mapping
  loadings$feature <- rownames(loadings)
  
  # If colour_arrows_by_category is TRUE, use category as the colour grouping,
  # otherwise colour each arrow by its full feature name.
  if (color_arrows_by_category) {
    arrow_colour_var <- "category"
    colour_label     <- "Feature category"
  } else {
    loadings$feature_label <- rownames(loadings)
    arrow_colour_var       <- "feature_label"
    colour_label           <- "Feature"
  }
  
  p_biplot <- ggplot() +
    geom_vline(xintercept = 0, linetype = "dashed", colour = "grey70", linewidth = 0.4) +
    geom_hline(yintercept = 0, linetype = "dashed", colour = "grey70", linewidth = 0.4) +
    geom_segment(
      data = loadings,
      aes(x = 0, y = 0, xend = xend, yend = yend,
          colour = .data[[arrow_colour_var]]),
      arrow     = arrow(length = unit(0.25, "cm"), type = "closed"),
      linewidth = 0.6,
      alpha     = 0.8
    ) +
    labs(
      x      = paste0("PC", pc_x, " (", round(var_exp_x, 1), "%)"),
      y      = paste0("PC", pc_y, " (", round(var_exp_y, 1), "%)"),
      title  = paste0("PCA Biplot - loadings (PC", pc_x, " vs PC", pc_y, ")"),
      colour = colour_label
    ) +
    coord_fixed() +
    theme_minimal() +
    theme(legend.position = "right",
          legend.text     = element_text(size = 7))
  
  # If using numbered biplot, also produce the variable lookup table
  if (use_numbered_biplot) {
    lookup_df    <- var_lookup %>%
      mutate(var_name = stringr::str_trunc(var_name, 40))
    chunk_size   <- 15
    num_chunks   <- ceiling(nrow(lookup_df) / chunk_size)
    lookup_plots <- list()
    
    for (i in 1:num_chunks) {
      start_idx <- (i - 1) * chunk_size + 1
      end_idx   <- min(i * chunk_size, nrow(lookup_df))
      chunk_df  <- lookup_df[start_idx:end_idx, ]
      
      if (color_arrows_by_category) {
        p <- ggplot(chunk_df, aes(x = 1, y = reorder(var_num, -var_num))) +
          geom_text(aes(label = paste0(var_num, ": ", var_name), color = category),
                    hjust = 0, size = 3) +
          scale_color_brewer(palette = "Set1") +
          labs(title = paste0("Variable Lookup Table (Part ", i, " of ", num_chunks, ")"),
               x = "", y = "", color = "Category") +
          theme_void() +
          theme(plot.title      = element_text(hjust = 0.5),
                plot.margin     = margin(10, 10, 10, 10),
                legend.position = "bottom") +
          xlim(1, 10)
      } else {
        p <- ggplot(chunk_df, aes(x = 1, y = reorder(var_num, -var_num))) +
          geom_text(aes(label = paste0(var_num, ": ", var_name)),
                    hjust = 0, size = 3) +
          labs(title = paste0("Variable Lookup Table (Part ", i, " of ", num_chunks, ")"),
               x = "", y = "") +
          theme_void() +
          theme(plot.title  = element_text(hjust = 0.5),
                plot.margin = margin(10, 10, 10, 10)) +
          xlim(1, 10)
      }
      lookup_plots[[i]] <- p
    }
  } else {
    lookup_plots <- NULL
  }
  
  # ── Step 7: Cluster summary table ────────────────────────────────────────────
  cluster_table <- table(Condition = centroids[[condition_col]],
                         Cluster   = centroids$cluster)
  
  # ── Step 7b: Condition mean heatmap annotated by cluster ─────────────────────
  require(pheatmap)
  
  # Compute per-condition mean for each selected feature (original feature space)
  condition_means <- data %>%
    group_by(!!sym(condition_col)) %>%
    summarise(across(all_of(selected_features), mean, na.rm = TRUE),
              .groups = "drop") %>%
    as.data.frame()
  rownames(condition_means) <- condition_means[[condition_col]]
  feat_means_mat <- as.matrix(condition_means[, selected_features])
  
  # Scale features to z-scores across conditions so all features are comparable
  feat_means_scaled <- scale(feat_means_mat)
  
  # Annotation: cluster membership per condition, ordered to match heatmap rows
  cluster_annotation <- data.frame(
    Cluster = as.factor(centroids$cluster),
    row.names = centroids[[condition_col]]
  )
  
  # Annotation colours: match Dark2 palette used in PCA cluster plot
  n_clusters     <- nlevels(centroids$cluster)
  dark2_colours  <- RColorBrewer::brewer.pal(max(3, n_clusters), "Dark2")[1:n_clusters]
  annot_colours  <- list(
    Cluster = setNames(dark2_colours, levels(centroids$cluster))
  )
  
  # Use the same hierarchical clustering as the PCA (hclust object on centroids)
  # so the row order in the heatmap is consistent with the dendrogram
  p_heatmap <- pheatmap(
    feat_means_scaled,
    cluster_rows      = hc,
    cluster_cols      = TRUE,
    annotation_row    = cluster_annotation,
    annotation_colors = annot_colours,
    color             = colorRampPalette(c("#2166ac", "white", "#b2182b"))(100),
    breaks            = seq(-3, 3, length.out = 101),
    border_color      = NA,
    fontsize_row      = 8,
    fontsize_col      = 7,
    angle_col         = 45,
    main              = "Condition mean features (z-scored), annotated by cluster",
    legend            = TRUE,
    annotation_legend = FALSE,
    legend_breaks     = c(-3, -2, -1, 0, 1, 2, 3),
    silent            = TRUE
  )
  
  # ── Step 7c: Filtered heatmap — reference constructs only ────────────────────
  # Z-scores are computed on the full dataset (all conditions) so the scale is
  # comparable to the full heatmap. Only the display is restricted to the four
  # reference constructs that bracket the expected behavioural range.
  # Keep only reference conditions that are actually present in the data
  reference_conditions <- reference_conditions[
    reference_conditions %in% rownames(feat_means_scaled)
  ]
  
  feat_means_scaled_ref <- feat_means_scaled[reference_conditions, , drop = FALSE]
  
  # Retain the column order from the full heatmap so features align between plots
  full_col_order        <- colnames(feat_means_scaled)[p_heatmap$tree_col$order]
  feat_means_scaled_ref <- feat_means_scaled_ref[, full_col_order, drop = FALSE]
  
  cluster_annotation_ref <- cluster_annotation[
    rownames(cluster_annotation) %in% reference_conditions, , drop = FALSE
  ]
  
  p_heatmap_ref <- pheatmap(
    feat_means_scaled_ref,
    cluster_rows      = FALSE,   # preserve biological order supplied
    cluster_cols      = FALSE,   # use full heatmap column order instead
    treeheight_col    = 0,       # no column dendrogram
    annotation_row    = cluster_annotation_ref,
    annotation_colors = annot_colours,
    color             = colorRampPalette(c("#2166ac", "white", "#b2182b"))(100),
    breaks            = seq(-3, 3, length.out = 101),
    border_color      = NA,
    fontsize_row      = 10,
    fontsize_col      = 7,
    angle_col         = 45,
    main              = "Reference constructs - z-scores relative to all conditions",
    annotation_legend = FALSE,
    silent            = TRUE
  )
  
  # ── Step 7c-ii: Delta heatmap — |mean(-EX) - mean(+EX)| per feature ──────────
  # Group reference conditions by the first word (space-separated) of their name.
  # Compute mean z-score per group per feature, then take the absolute difference.
  # Group reference conditions by the first word (space-separated) of their name.
  # Compute mean z-score per group per feature, then take the absolute difference.
  ref_groups <- data.frame(
    condition = rownames(feat_means_scaled_ref),
    group     = sub(" .*", "", rownames(feat_means_scaled_ref))  # first word
  )
  
  # Mean z-score per group per feature using colMeans
  group_labels   <- unique(ref_groups$group)   # e.g. "-EX" and "+EX"
  group_mat_list <- lapply(group_labels, function(g) {
    rows <- ref_groups$condition[ref_groups$group == g]
    colMeans(feat_means_scaled_ref[rows, , drop = FALSE], na.rm = TRUE)
  })
  names(group_mat_list) <- group_labels
  
  # Absolute difference: always |-EX mean - +EX mean|
  # Order: first group minus second group (alphabetical), then abs
  delta_vec <- abs(group_mat_list[[group_labels[1]]] - group_mat_list[[group_labels[2]]])
  
  # Reshape to a single-row matrix with a descriptive row name
  delta_label <- paste0("|\u0394| ", group_labels[1], " vs ", group_labels[2])
  delta_mat   <- matrix(delta_vec, nrow = 1,
                        dimnames = list(delta_label, names(delta_vec)))
  
  # Sequential colour scale: white (0) to dark orange (max difference)
  delta_max   <- ceiling(max(delta_mat) * 10) / 10   # round up to 1 d.p.
  
  p_heatmap_delta <- pheatmap(
    delta_mat,
    cluster_rows      = FALSE,
    cluster_cols      = FALSE,
    treeheight_col    = 0,
    treeheight_row    = 0,
    color             = colorRampPalette(c("white", "#E07B00"))(100),
    breaks            = seq(0, max(delta_max, 0.01), length.out = 101),
    border_color      = "grey80",
    fontsize_row      = 10,
    fontsize_col      = 7,
    fontsize_number   = 6,
    angle_col         = 45,
    display_numbers   = TRUE,               # show values in each cell
    number_format     = "%.2f",             # 2 decimal places
    main              = paste0("Absolute difference in mean z-score: ",
                               group_labels[1], " vs ", group_labels[2]),
    annotation_legend = FALSE,
    legend            = TRUE,
    silent            = TRUE
  )
  
  # ── Step 7d: Subset heatmap — user-specified features (columns) ──────────────
  # Z-scores are from the full dataset. Rows (conditions) are all preserved.
  # Columns are restricted to heatmap_subset_features if provided.
  if (!is.null(heatmap_subset_features)) {
    subset_features <- heatmap_subset_features[
      heatmap_subset_features %in% colnames(feat_means_scaled)
    ]
    missing_features <- setdiff(heatmap_subset_features, colnames(feat_means_scaled))
    if (length(missing_features) > 0) {
      warning(paste("heatmap_subset_features: the following features were not found and are excluded:",
                    paste(missing_features, collapse = ", ")))
    }
  } else {
    subset_features <- full_col_order
  }
  
  # Retain the full heatmap column order within the subset
  subset_col_order     <- full_col_order[full_col_order %in% subset_features]
  feat_means_scaled_sub <- feat_means_scaled[, subset_col_order, drop = FALSE]
  
  p_heatmap_sub <- pheatmap(
    feat_means_scaled_sub,
    cluster_rows      = hc,      # same row clustering as full heatmap
    cluster_cols      = FALSE,   # retain full heatmap column order within subset
    treeheight_col    = 0,
    annotation_row    = cluster_annotation,
    annotation_colors = annot_colours,
    color             = colorRampPalette(c("#2166ac", "white", "#b2182b"))(100),
    breaks            = seq(-3, 3, length.out = 101),
    border_color      = NA,
    fontsize_row      = 8,
    fontsize_col      = 7,
    angle_col         = 45,
    main              = "Subset heatmap - z-scores relative to all conditions",
    legend            = TRUE,
    legend_breaks     = c(-3, -2, -1, 0, 1, 2, 3),
    annotation_legend = FALSE,
    silent            = TRUE
  )
  result_list <- list(
    # Raw results
    pca_result  = pca_result,           # prcomp object fitted on all cells
    centroids   = centroids,            # per-condition mean PC scores + cluster
    clustering  = list(hclust = hc, clusters = clusters),
    variance    = list(individual  = var_explained_pct,
                       cumulative  = cum_var_explained),
    cluster_table = cluster_table,
    var_lookup  = var_lookup,
    
    # Plots
    plots = list(
      variance_individual = p_var_ind,
      variance_cumulative = p_var_cum,
      scree               = p_scree,
      dendrogram          = p_dend,
      pca_by_condition    = p_cond,
      pca_by_cluster      = p_clust,
      biplot              = p_biplot,
      condition_heatmap     = p_heatmap,
      condition_heatmap_ref = p_heatmap_ref,
      condition_heatmap_delta = p_heatmap_delta,
      condition_heatmap_sub = p_heatmap_sub
    )
  )
  
  if (use_numbered_biplot) {
    result_list$plots$lookup_tables <- lookup_plots
  }
  
  return(result_list)
}

```

## Loose intensity filtering

### Features from correlation clustering, 2 clusters in PCA
```{r PCA analysis after feature reduction based on pearson correlation loose intensity, echo = FALSE}
SNX2_muts_PCAresults_pc1_2_new <- run_pca_analysis(
    data = Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
      dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')) %>% 
      dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)), # Your data frame
    condition_col = "Construct", # Column name for condition IDs
    selected_features = features_to_keep_sc_new_loose,          # Vector of feature column names to use for PCA
    do_center = TRUE,           # Whether to center the data
    do_scale = TRUE,            # Whether to scale the data
    num_clusters = 2,           # Number of clusters to create
    pc_x = 1,                   # PC for x-axis in plots
    pc_y = 2,                   # PC for y-axis in plots
    add_ellipses = FALSE,        # Whether to add confidence ellipses
    add_labels = FALSE,           # Whether to add labels to points
    point_size = 5,             # Size of points in plots
    use_numbered_biplot = TRUE,  # Whether to use numbers instead of text in biplot
    biplot_color_by = "none",    # Color biplot points: "none", "cluster", or "condition"
    color_arrows_by_category = FALSE, # Color arrows by first word in variable name
    show_point_numbers = TRUE,  # Show or hide the numbers on points in the biplot
    num_pcs_for_clustering = 5 ,  # Number of PCs to use for hierarchical clustering
    reference_conditions = c("-EX (rep1)", "-EX (rep2)", "-EX (rep3)", "+EX"), # Conditions to show in the reference heatmap
    colour_col = "4_residue_insert",  # Column to colour points by (binary TRUE/FALSE)
    colour_values = c("TRUE" = "#00BFC4", "FALSE" = "#F8766D"), # Colours for the two values
    point_stroke = 1.5,           # Stroke thickness for condition/cluster plot points
    heatmap_subset_features = c('Granularity_2_MCHERRY_BACKCORR',
                                'Intensity_Std_mean_norm',
                                'Texture_AngularSecondMoment_MCHERRY_BACKCORR_2_01_256',
                                'Texture_Correlation_MCHERRY_BACKCORR_2_01_256')) # Character vector of conditions to include in subset heatmap (NULL = all)
    
SNX2_muts_PCAresults_pc1_2_new$plots$scree
SNX2_muts_PCAresults_pc1_2_new$plots$pca_by_condition
SNX2_muts_PCAresults_pc1_2_new$plots$pca_by_cluster
SNX2_muts_PCAresults_pc1_2_new$plots$biplot

```

```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap endogenous isoforms, echo = FALSE, fig.width=20}
SNX2_muts_PCAresults_pc1_2_new$plots$condition_heatmap_ref

```


```{r CA analysis after feature reduction based on pearson correlation loose intensity condition heatmap endogenous isoforms delta, echo = FALSE}
SNX2_muts_PCAresults_pc1_2_new$plots$condition_heatmap_delta
```


```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap, echo = FALSE, fig.height=10}
SNX2_muts_PCAresults_pc1_2_new$plots$condition_heatmap

```


```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap feature subset, echo = FALSE, fig.height=10}
SNX2_muts_PCAresults_pc1_2_new$plots$condition_heatmap_sub
```


### Features from correlation clustering, 2 clusters in PCA nontransfected
```{r PCA analysis after feature reduction based on pearson correlation nontransfected, echo = FALSE}
SNX2_muts_PCAresults_pc1_2_new_neg <- run_pca_analysis(
    data = NegTransfected_only_without_outliers_SNX2muts %>% 
      dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')) %>% 
      dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)), # Your data frame
    condition_col = "Construct", # Column name for condition IDs
    selected_features = features_to_keep_sc_new_loose,          # Vector of feature column names to use for PCA
    do_center = TRUE,           # Whether to center the data
    do_scale = TRUE,            # Whether to scale the data
    num_clusters = 2,           # Number of clusters to create
    pc_x = 1,                   # PC for x-axis in plots
    pc_y = 2,                   # PC for y-axis in plots
    add_ellipses = FALSE,        # Whether to add confidence ellipses
    add_labels = FALSE,           # Whether to add labels to points
    point_size = 5,             # Size of points in plots
    use_numbered_biplot = TRUE,  # Whether to use numbers instead of text in biplot
    biplot_color_by = "none",    # Color biplot points: "none", "cluster", or "condition"
    color_arrows_by_category = FALSE, # Color arrows by first word in variable name
    show_point_numbers = TRUE,  # Show or hide the numbers on points in the biplot
    num_pcs_for_clustering = 5 ,  # Number of PCs to use for hierarchical clustering
    reference_conditions = c("-EX (rep1)", "-EX (rep2)", "-EX (rep3)", "+EX"), # Conditions to show in the reference heatmap
    colour_col = "4_residue_insert",  # Column to colour points by (binary TRUE/FALSE)
    colour_values = c("TRUE" = "#00BFC4", "FALSE" = "#F8766D"), # Colours for the two values
    point_stroke = 1.5,           # Stroke thickness for condition/cluster plot points
    heatmap_subset_features = c('Granularity_2_MCHERRY_BACKCORR',
                                'Intensity_Std_mean_norm',
                                'Texture_AngularSecondMoment_MCHERRY_BACKCORR_2_01_256',
                                'Texture_Correlation_MCHERRY_BACKCORR_2_01_256')) # Character vector of conditions to include in subset heatmap (NULL = all)

SNX2_muts_PCAresults_pc1_2_new_neg$plots$scree
SNX2_muts_PCAresults_pc1_2_new_neg$plots$pca_by_condition
SNX2_muts_PCAresults_pc1_2_new_neg$plots$pca_by_cluster
SNX2_muts_PCAresults_pc1_2_new_neg$plots$biplot

```


```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap endogenous isoforms nontransfected, echo = FALSE, fig.width=20}
SNX2_muts_PCAresults_pc1_2_new_neg$plots$condition_heatmap_ref

```

```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap nontransfected, echo = FALSE, fig.height=10}
SNX2_muts_PCAresults_pc1_2_new_neg$plots$condition_heatmap

```

```{r PCA analysis after feature reduction based on pearson correlation loose intensity condition heatmap feature subset nontransfected, echo = FALSE, fig.height=10}
SNX2_muts_PCAresults_pc1_2_new_neg$plots$condition_heatmap_sub
```


# Line plots
## Dataframe 
```{r}
#
df_for_lineplots_main_figure <- Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')) %>% 
  dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)) %>% 
  dplyr::filter(!Construct %in% c('-EX (rep1)','-EX (rep3)')) %>% 
  dplyr::mutate(main_cluster_identity = case_when(
    `4_residue_insert` == TRUE | Construct == '-EX: EIeE|----|W' ~ 'SNX2+EX cluster',
    `4_residue_insert` == FALSE & Construct != '-EX: EIeE|----|W' ~ 'SNX2-EX cluster')) %>%  
    dplyr::mutate(sub_cluster_identity = case_when(
      #Construct %in% c('+EX: EIRk|EIEE|W','+EX: EIRa|EIEE|W') ~ 'SNX2+EX E452',
      Construct %in% c('-EX: EIqE|----|W','-EX: EIaE|----|W') ~ 'SNX2-EX transitioning',
      Construct %in% c('-EX (rep1)','-EX (rep2)','-EX (rep3)','-EX: EIkE|----|W') ~ 'SNX2-EX cluster',
      .default = 'SNX2+EX cluster')) %>%
  dplyr::mutate(sub_cluster_identity = factor(sub_cluster_identity, levels = c('SNX2-EX cluster', 'SNX2-EX transitioning', 'SNX2+EX cluster', 'SNX2+EX E452'))) %>% 
  dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR <= 0.06)

# Create custom linetype scale
linetype_standard_subcluster <- c(1, 2, 3, 6)
names(linetype_standard_subcluster) <- levels(df_for_lineplots$sub_cluster_identity)
linetype_scale_subcluster <- scale_linetype_manual(name = 'Cluster',values = linetype_standard_subcluster)

```


```{r echo = FALSE}
#
df_for_lineplots_main_figure %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR/transfection_threshold, y = Granularity_2_MCHERRY_BACKCORR, color = `4_residue_insert`, group = Construct))+
  scale_x_log10()+
  geom_smooth(data = df_for_lineplots_main_figure %>% 
                dplyr::filter(Construct %in% c('+EX','-EX (rep2)')),
                aes(linetype = main_cluster_identity), se = FALSE, linewidth = 2, color = 'black')+
  geom_smooth(aes(linetype = main_cluster_identity), se = FALSE, linewidth = 1.5)+
  linetype_scale_subcluster+
    labs(title = 'SNX2 isoforms and mutants',
       y = 'Granularity',
       x = 'mCherry intensity (relative to threshold)',
       linetype = 'Cluster',
       color = 'Construct')+
  theme_bw(base_size = 16)
###

```
