---
title: "12_Analysis_of_transfected_cells_SNX2mutants_v1_20250319"
author: "Peter Kjer Hansen"
date: "2025-04-01"
output:
  html_document:
    fig_width: 12
    fig_height: 6
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(dev = "svg")


# Packages
library(tidyverse)
library(caret)
library(lme4)
library(lmerTest)
library(broom.mixed)
library(broom)
library(readxl)
library(lsr) #Contains cohensD() function
library(nnet) #Feedforward neural network
library(UpSetR) #Package for doing upset plots
library(ggrepel) #Package for making repel text
library(factoextra) #
library(ggdendro) # Package for dendrograms

# Working directory with transfected cell data
Directory_with_transfected_cell_measurements <- 'INSERT PATH TO FOLDER WITH .CSVS CONTAINING THE SINGLE CELL MEASUREMENTS'

#Working directory
#Exon description dataset
Path_to_exon_description_sheet <- 'INSERT PATH TO SHEET WITH EXON DESCRIPTIONS'
File_with_exon_description_sheet <- 'INSERT FILE NAME OF .XLSX WITH EXON DESCRIPTIONS'
Event_sheet <- 'INSERT SHEET NAME'
LUMIER_sheet <- 'INSERT SHEET NAME'

#Model folders
#Postrans
Postransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON TRANSFECTED CELLS'
#Negtrans 10 percentile with rep aware sampling, No Golgin
Negtransfected_model_folder <- 'INSERT PATH TO FOLDER WITH CLASSIFIERS TRAINED ON NON-TRANSFECTED CELLS'

# SNX2 isoform classifier pair
PAIRS_1A <- c('PAIR_09')

### Thresholds for important variables
# Threshold for the contribution ratio (pos_trans / neg_trans). Higher is more stringent
ratio_threshold <- 2.6
# Threshold for the contribution ratio X contribution prop (positive) variable. Higher is more stringent
ratio_times_importance_threshold <- 1.5
#
confidence_interval_threshold_for_bootstrap <- 0.99

# mCherry mean intensity value that marks the transfection threshold. Is used to list intensities relative to the transfection threshold.
transfection_threshold <- 0.00065
```

```{r well construct ids, echo = FALSE}
# Assinging well metadata to all the cells
Well_mutant_pairing <- bind_cols(Well_ID = c('A01','A02','A03','A04','A05','A06',
                                             'B01','B02','B03','B04','B05','B06',
                                             'C01','C02','C03','C04','C05','C06',
                                             'D01','D02','D03','D04','D05','D06'),
                                 Construct = c('Nontransfected', 'mCherry', '-EX: EIaE|----|W','-EX: EIqE|----|W', '-EX: EIeE|----|W', '-EX: EIkE|----|W',
                                             '+EX: EIRk|EIEE|W', '+EX: EIRa|EIEE|W', '+EX: EIRq|EIEE|W', '+EX: EIRE|aaaa|W', '+EX: EIRE|aIaa|W', '+EX: EIRE|qIqq|W',
                                             '+EX: EIRE|qIEE|W','+EX: EIRE|EIqE|W', '+EX: EIRE|EIEq|W', '+EX: EIRE|qIEq|W', '+EX: EIRE|qIqE|W', '+EX: EIRE|EIqq|W',
                                              '-EX (rep1)', '-EX (rep2)','+EX: EIRE|EIaE|W', '+EX: EIRE|EIrE|W','+EX', '-EX (rep3)'))
```


```{r Function for loading in cells, echo=FALSE}
Load_transfected_cells_and_summary_SNX2muts <- function(WORKING_DIRECTORY, SET){
  setwd(WORKING_DIRECTORY)

  Transfected_cell_files <- list.files(path = WORKING_DIRECTORY) %>% 
    str_subset(pattern = '_TRANSFECTED_CELLS')
  
  Transfection_summary_files <- list.files(path = WORKING_DIRECTORY)%>% 
    str_subset(pattern = '_TRANSFECTION_SUMMARY')
  
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP1_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_1 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP2_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_2 <- Transfected_cellbodies
  rm(Transfected_cellbodies)
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP3_TRANSFECTED_CELLS'))
  TRANSFECTED_CELLS_REP_3 <- Transfected_cellbodies
  rm(Transfected_cellbodies)

  #
  Transfected_cells <- bind_rows(TRANSFECTED_CELLS_REP_1,
                                 TRANSFECTED_CELLS_REP_2,
                                 TRANSFECTED_CELLS_REP_3)
  # SUMMARIES
  #
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP1_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_1 <- Transfection_summary
  rm(Transfection_summary)
  
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP2_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_2 <- Transfection_summary
  rm(Transfection_summary)
  
  load(file = paste0(WORKING_DIRECTORY,'/',SET,'_REP3_TRANSFECTION_SUMMARY'))
  TRANSFECTION_SUMMARY_REP_3 <- Transfection_summary
  rm(Transfection_summary)
  
  Transfection_summary <- bind_rows(TRANSFECTION_SUMMARY_REP_1,
                                    TRANSFECTION_SUMMARY_REP_2,
                                    TRANSFECTION_SUMMARY_REP_3)
  return(list(Transfected_cells, Transfection_summary))
}
```

```{r Loading in cells and summaries, echo=FALSE}
#
TRANSFECTED_SNX2muts <- Load_transfected_cells_and_summary_SNX2muts(WORKING_DIRECTORY = Directory_with_transfected_cell_measurements,
                                   SET = 'SET_SNX2mutants')[[1]]
#
SUMMARY_SNX2muts <- Load_transfected_cells_and_summary_SNX2muts(WORKING_DIRECTORY = Directory_with_transfected_cell_measurements,
                                   SET = 'SET_SNX2mutants')[[2]]
```

```{r Function to reduce features, echo=FALSE}
remove_non_mcherry_vars_SNX2muts <- function(CELL_DATA, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = FALSE){
  if(REDUCE_FEATURES == TRUE){
    Reduced_dataset <- CELL_DATA %>% 
      dplyr::select(ImageNumber, ObjectNumber, Metadata_Well, Experiment_Set, Experiment_Rep, TRANSFECTED, 
                    starts_with('Intensity_') & ends_with('_MCHERRY_BACKCORR'),
                    starts_with('Correlation_'),
                    starts_with('Granularity_'), starts_with('RadialDistribution'), starts_with('Texture_'), starts_with('AreaShape_')) %>% 
      dplyr::select(!c(starts_with('Correlation') & contains('GOLGIN97_AUTOF_CORR'))) %>% 
      na.omit()
  }
  if(REDUCE_FEATURES == FALSE){
    Reduced_dataset <- CELL_DATA %>% 
      dplyr::select(ImageNumber, ObjectNumber, Metadata_Well, Experiment_Set, Experiment_Rep, TRANSFECTED, everything()) %>% 
      dplyr::select(!c(Experiment_SetRep, ends_with('_BACKGROUND'), Number_Object_Number, Parent_Segmentation)) %>% 
      na.omit()
  }
  if(ONLY_TRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == TRUE)
  }
  if(ONLY_NEGTRANSFECTED == TRUE){
    Reduced_dataset <- Reduced_dataset %>% 
      dplyr::filter(TRANSFECTED == FALSE)
  }
  return(Reduced_dataset)
}
```

```{r Generating datasets with reduced number of features, echo=FALSE}
Reduced_transfected_SNX2muts <- remove_non_mcherry_vars_SNX2muts(CELL_DATA = TRANSFECTED_SNX2muts, ONLY_TRANSFECTED = TRUE, REDUCE_FEATURES = TRUE)

Reduced_negtrans_SNX2muts <- remove_non_mcherry_vars_SNX2muts(CELL_DATA = TRANSFECTED_SNX2muts, ONLY_TRANSFECTED = FALSE, REDUCE_FEATURES = TRUE, ONLY_NEGTRANSFECTED = TRUE)
```


```{r population mean expression plots, echo = FALSE}

plot_construct_order <- c('-EX (rep1)', '-EX (rep2)', '-EX (rep3)','-EX: EIaE|----|W','-EX: EIkE|----|W','-EX: EIeE|----|W','-EX: EIqE|----|W',
                          '+EX','+EX: EIRE|aaaa|W','+EX: EIRE|aIaa|W', '+EX: EIRE|qIEE|W','+EX: EIRE|EIqE|W', '+EX: EIRE|EIEq|W','+EX: EIRE|qIqE|W','+EX: EIRE|qIEq|W','+EX: EIRE|EIqq|W',
                          '+EX: EIRE|qIqq|W','+EX: EIRE|EIaE|W', '+EX: EIRE|EIrE|W','+EX: EIRa|EIEE|W','+EX: EIRk|EIEE|W',  '+EX: EIRq|EIEE|W','Nontransfected')
                          

# THIS PLOT MAY BE QUITE NICE (FOR SUPP) - NEED MUTANT NAMES. A MAIN TAKE AWAY IS POOR EXPRESSION OF B04 - WHICH HAPPENS TO BE SNX2 4As - although we also see poor expression of mCherry (A02)
population_intensity_df <- TRANSFECTED_SNX2muts %>% 
  dplyr::filter(TRANSFECTED == TRUE) %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::filter(!Metadata_Well %in% c('A01','A02')) %>% 
  dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)) %>% 
  dplyr::mutate(Construct = factor(Construct, levels = plot_construct_order)) #%>% 
  
population_intensity_df %>%
  ggplot(aes(y = Construct,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR))+
  geom_boxplot(outlier.shape = NA, aes(fill = `4_residue_insert`))+
  geom_text(data = population_intensity_df %>%
              ungroup() %>% 
              group_by(Construct) %>% 
              summarize(n_cell = n()),
            aes(x = 0.85, y = Construct, label = paste0('n=',n_cell)), color = 'black', size = 3)+
  coord_cartesian(xlim = c(0.0005, 0.9))+
  scale_x_log10()+
  scale_y_discrete(limits = rev)+
  labs(title = 'Expression levels of SNX2 constructs',
       subtitle = 'Cells pooled from 3 experimental repeats',
       x = 'mCherry intensity (a.u.)',
       y = 'SNX2 construct',
       fill = '4-residue\ninsertion')+
  theme_bw(base_size = 14)

# Facet according to replicates, but shows same thing
Reduced_transfected_SNX2muts %>% 
  ggplot(aes(y = Metadata_Well,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR))+
  geom_boxplot()+
  facet_wrap(~Experiment_Rep)
```


```{r Function to remove outliers bright cells, echo=FALSE}

#Outliers (DEFINED AS AS HAVING Intensity_MeanIntensity_MCHERRY_BACKCORR > 1.5 x IQR + 75% quantile Intensity_MCHERRY_BACKCORR for construct with lowest RANGE - Note, non-trans, mCherry, and B04 (4xA) not part of this 
###
#Note, function also removes NAN columns and zero colummns
Identify_and_remove_outliers_SNX2muts <- function(DATASET,
                                         USE_LOWER_MAX_UPPER_HINGE,
                                         ONLY_NEGTRANS = FALSE,
                                         REMOVE_TOP_x_PERCENTILE_NEGATIVE = FALSE,
                                         TOP_x_PERCENTILE = 0.1,
                                         REMOVE_SAME_COLS_AS_TRANSFECTED = FALSE,
                                         TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = NULL,
                                         WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04')
                                         ){
  TRANSFECTED_ONLY <- DATASET %>% 
    dplyr::filter(TRANSFECTED == TRUE)
  #In the case that only nontransfected cells are in the original dataset, we don't want to remove them by filtering (as we don't have any cells left then)
  if(ONLY_NEGTRANS == TRUE){
    TRANSFECTED_ONLY <- DATASET 
  }
  if(ONLY_NEGTRANS == TRUE & REMOVE_TOP_x_PERCENTILE_NEGATIVE == TRUE){
    #Read in dataset
    TRANSFECTED_ONLY <- DATASET %>% 
      # Group by the variables of interest
      group_by(Experiment_Rep, Metadata_Well) %>%
      # Arrange within groups by intensity (descending)
      arrange(desc(Intensity_MeanIntensity_MCHERRY_BACKCORR), .by_group = TRUE) %>%
      # Calculate the percentile within each group
      mutate(percentile = row_number()/n()) %>%
      # Keep only the bottom 80%
      filter(percentile > TOP_x_PERCENTILE) %>%
      # Remove the helper column
      select(-percentile) %>%
      # Ungroup to remove grouping structure
      ungroup()
  }
  
  SUMMARY_STATISTICS <- TRANSFECTED_ONLY %>%
    dplyr::mutate('LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    ungroup() %>% 
    group_by(Experiment_Rep, Metadata_Well) %>% 
    summarise(n_cells = n(),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              QUANTILE_75_INTENSITY = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25)))  %>% 
    ungroup() %>% 
    dplyr::mutate('REP_WELL' = paste0(Experiment_Rep,'_',Metadata_Well))
  
  #Can be used to remove the skew of very bright cells if present in one isoform but not another (simply allows using the highest UPPER hing value from one isoform as the filter for the other isoform)
  MAX_INTENSITY_CUTOFF_SET_BASED <- SUMMARY_STATISTICS %>%
    dplyr::filter(!Metadata_Well %in% WELLS_NOT_USED_FOR_DEFINING_OUTLIERS) %>% 
    group_by(Experiment_Rep) %>% 
    summarise('LOWER_MAX_UPPER_HINGE' = min(UPPER_HINGE_IQRx1.5))
  #
  

    Transfected_cells_outliers_removed <-TRANSFECTED_ONLY %>%
    dplyr::mutate('LOG_INTENSITY' = log10(Intensity_MeanIntensity_MCHERRY_BACKCORR)) %>% 
    ungroup() %>%
    dplyr::mutate('Intensity_Edge_mean_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Edge_max_norm' = Intensity_MeanIntensityEdge_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Max_mean_norm' = Intensity_MaxIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MassDisp_mean_norm' = Intensity_MassDisplacement_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_Std_mean_norm' = Intensity_StdIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR,
                  'Intensity_MAD_mean_norm' = Intensity_MADIntensity_MCHERRY_BACKCORR / Intensity_MeanIntensity_MCHERRY_BACKCORR) %>% 
    dplyr::left_join(x = ., y = SUMMARY_STATISTICS, by = join_by('Experiment_Rep' == 'Experiment_Rep', 'Metadata_Well' == 'Metadata_Well')) %>%
    dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < UPPER_HINGE_IQRx1.5) %>%
    dplyr::select(-c(MEAN_INTENSITY, MEDIAN_INTENSITY, SD_INTENSITY, LOG_MEAN_INTENSITY, LOG_SD_INTENSITY, QUANTILE_75_INTENSITY, n_cells)) %>% 
    dplyr::select(c(1:6, 'REP_WELL', 'LOG_INTENSITY','UPPER_HINGE_IQRx1.5', everything()))
  
  if(USE_LOWER_MAX_UPPER_HINGE == TRUE){
    Transfected_cells_outliers_removed <- Transfected_cells_outliers_removed %>% 
      dplyr::left_join(x = ., y = MAX_INTENSITY_CUTOFF_SET_BASED, by = join_by('Experiment_Rep' == 'Experiment_Rep')) %>% 
      dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR < LOWER_MAX_UPPER_HINGE) %>% 
      dplyr::select(c(1:9, 'LOWER_MAX_UPPER_HINGE', everything()))
  }
  
  #Seems to remove columns with NANs and no variance
  if(USE_LOWER_MAX_UPPER_HINGE == TRUE){
    FEATURE_START <- 11
  }
  if(USE_LOWER_MAX_UPPER_HINGE == FALSE){
    FEATURE_START <- 10
  }
  Wells <- Transfected_cells_outliers_removed %>% 
    dplyr::filter(!Metadata_Well %in% WELLS_NOT_USED_FOR_DEFINING_OUTLIERS) %>% 
    dplyr::pull(Metadata_Well) %>% 
    unique()
  
  CONSTANT_COLS <-c()
  NAN_COLS <- c()
  FEATURES <- colnames(Transfected_cells_outliers_removed)
  FEATURE_END <- length(colnames(Transfected_cells_outliers_removed))
  for(i in Wells){
    PAIR_x_df <- Transfected_cells_outliers_removed %>% 
      dplyr::filter(Metadata_Well == i)
    
    for(j in FEATURE_START:FEATURE_END){
      constant_value <- length(unique(PAIR_x_df[[j]]))
      NAN_value <- any(is.na(PAIR_x_df[[j]]))
      
      if(constant_value == 1){
        CONSTANT_COLS <- c(CONSTANT_COLS, j)
      }
      if(NAN_value == TRUE){
        NAN_COLS <- c(NAN_COLS, j)
      }
    }
  }
  CONSTANT_FEATURES <- FEATURES[CONSTANT_COLS]
  NAN_FEATURES <- FEATURES[NAN_COLS]
  FEATURES_TO_REMOVE <- c(unique(CONSTANT_FEATURES), unique(NAN_FEATURES)) #REMOVES 8 VARIABLES FOR SET A (MOSTLY Manders Correlation)
  TEXT_CONSTANT <- paste0('The variables with CONSTANT values for at least one PAIR are: ', unique(CONSTANT_FEATURES))
  TEXT_NULL <- paste0('The variables with MISSING values for at least one PAIR are: ', unique(NAN_FEATURES))
  print(TEXT_CONSTANT)
  print(TEXT_NULL)
  
  
  Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>% 
    dplyr::select(!c(all_of(FEATURES_TO_REMOVE))) #%>% 
  #dplyr::select(!(c(starts_with('Intensity') & ends_with('MCHERRY_BACKCORR'))))
  
  if(ONLY_NEGTRANS == TRUE & REMOVE_SAME_COLS_AS_TRANSFECTED == TRUE){
    Transfected_cells_outliers_removed_REDUCED_COLS <- Transfected_cells_outliers_removed %>%
      dplyr::select(c(colnames(TRANSFECTED_DATASET_FOR_COLS_TO_KEEP)))
  }
  
  
  SUMMARY_STATISTICS_OUTLIERS_REMOVED <- Transfected_cells_outliers_removed %>%
    ungroup() %>% 
    group_by(Experiment_Rep, Metadata_Well) %>% 
    summarise(n_cells = n(),
              MEAN_INTENSITY = mean(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              MEDIAN_INTENSITY = mean(Intensity_MedianIntensity_MCHERRY_BACKCORR),
              SD_INTENSITY = sd(Intensity_MeanIntensity_MCHERRY_BACKCORR),
              LOG_MEAN_INTENSITY = mean(LOG_INTENSITY),
              LOG_SD_INTENSITY = sd(LOG_INTENSITY),
              UPPER_HINGE_IQRx1.5 = quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) + 1.5 * (quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.75) - quantile(Intensity_MeanIntensity_MCHERRY_BACKCORR, probs = 0.25))) %>% 
    dplyr::mutate('REP_WELL' = paste0(Experiment_Rep,'_',Metadata_Well))
  
  
  return(list(Transfected_cells_outliers_removed_REDUCED_COLS, SUMMARY_STATISTICS, SUMMARY_STATISTICS_OUTLIERS_REMOVED))
}
#####
```


```{r Creating transfected datasets with outlier removal, echo=FALSE, message=FALSE}
#Transfected cells for each isoform pair and controls
Transfected_only_without_outliers_SNX2muts_strict_intensity <- Identify_and_remove_outliers_SNX2muts(Reduced_transfected_SNX2muts, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04'))[[1]] 


#
Transfected_only_without_outliers_SNX2muts_loose_intensity <- Identify_and_remove_outliers_SNX2muts(Reduced_transfected_SNX2muts, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = FALSE,
                                                                    WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04'))[[1]] 

#Set 1
NegTransfected_only_without_outliers_SNX2muts <- Identify_and_remove_outliers_SNX2muts(Reduced_negtrans_SNX2muts, 
                                                                    USE_LOWER_MAX_UPPER_HINGE = TRUE,
                                                                    ONLY_NEGTRANS = TRUE,
                                                                    REMOVE_TOP_x_PERCENTILE_NEGATIVE = TRUE,
                                                                    TOP_x_PERCENTILE = 0.1,
                                                                    REMOVE_SAME_COLS_AS_TRANSFECTED = TRUE,
                                                                    TRANSFECTED_DATASET_FOR_COLS_TO_KEEP = Transfected_only_without_outliers_SNX2muts_strict_intensity,
                                                                    WELLS_NOT_USED_FOR_DEFINING_OUTLIERS = c('A01', 'A02', 'B04'))[[1]]


### ADDDING CONSTRUCT IDS
#
Transfected_only_without_outliers_SNX2muts_strict_intensity <- Transfected_only_without_outliers_SNX2muts_strict_intensity %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::select(c(1:9, 'Construct', everything())) %>% 
  dplyr::select(-LOWER_MAX_UPPER_HINGE)
#
Transfected_only_without_outliers_SNX2muts_strict_intensity_w_max_limit <- Transfected_only_without_outliers_SNX2muts_strict_intensity %>% 
  dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR <= 0.003)
#
Transfected_only_without_outliers_SNX2muts_loose_intensity <- Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::select(c(1:9, 'Construct', everything()))
#
NegTransfected_only_without_outliers_SNX2muts <- NegTransfected_only_without_outliers_SNX2muts %>% 
  dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::select(c(1:9, 'Construct', everything()))%>% 
  dplyr::select(-LOWER_MAX_UPPER_HINGE)

```


## Population expression plots but using intensity filtered cells
### Strict intensity threshold
```{r population mean expression plots of strict threshold cells, echo=FALSE}
population_intensity_df <- Transfected_only_without_outliers_SNX2muts_strict_intensity %>% 
  #dplyr::filter(TRANSFECTED == TRUE) %>% 
  #dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::filter(!Metadata_Well %in% c('A01','A02')) %>% 
  dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)) %>% 
  dplyr::mutate(Construct = factor(Construct, levels = plot_construct_order))


population_intensity_df %>%
  ggplot(aes(y = Construct,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR))+
  geom_boxplot(outlier.shape = NA, aes(fill = `4_residue_insert`))+
  #geom_vline(xintercept = 0.003)+
  geom_text(data = population_intensity_df %>%
              ungroup() %>% 
              group_by(Construct) %>% 
              summarize(n_cell = n()),
            aes(x = 0.85, y = Construct, label = paste0('n=',n_cell)), color = 'black', size = 3)+
  coord_cartesian(xlim = c(0.0005, 0.9))+
  scale_x_log10()+
  scale_y_discrete(limits = rev)+
  labs(title = 'Expression levels of SNX2 constructs',
       subtitle = 'Cells pooled from 3 experimental repeats',
       x = 'mCherry intensity (a.u.)',
       y = 'SNX2 construct',
       fill = '4-residue\ninsertion')+
  theme_bw(base_size = 14)

population_intensity_df %>%
  ggplot(aes(y = Construct,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR/transfection_threshold))+
  geom_boxplot(outlier.shape = NA, aes(fill = `4_residue_insert`))+
  #geom_vline(xintercept = 0.003)+
  geom_text(data = population_intensity_df %>%
              ungroup() %>% 
              group_by(Construct) %>% 
              summarize(n_cell = n()),
            aes(x = 55, y = Construct, label = paste0('n=',n_cell)), color = 'black', size = 3)+
  coord_cartesian(xlim = c(1, 65))+
  scale_x_log10()+
  scale_y_discrete(limits = rev)+
  labs(title = 'Expression levels of SNX2 constructs',
       subtitle = 'Cells pooled from 3 experimental repeats',
       x = 'mCherry intensity (relative to transfection threshold)',
       y = 'SNX2 construct',
       fill = '4-residue\ninsertion')+
  theme_bw(base_size = 14)
```

### Strict intensity threshold and limited to X mean intensity
```{r population mean expression plots of cells not getting above 00030, echo=FALSE, eval=FALSE}
population_intensity_df <- Transfected_only_without_outliers_SNX2muts_strict_intensity_w_max_limit %>% 
  #dplyr::left_join(x = ., y = Well_mutant_pairing, by = join_by('Metadata_Well' == 'Well_ID')) %>% 
  dplyr::filter(!Metadata_Well %in% c('A01','A02')) %>% 
  dplyr::mutate('4_residue_insert' = case_when(substr(Construct, start = 1, stop = 3) == '+EX' ~ TRUE,
                                               substr(Construct, start = 1, stop = 3) == '-EX' ~ FALSE,
                                               .default = NA)) %>% 
  dplyr::mutate(Construct = factor(Construct, levels = plot_construct_order))


population_intensity_df %>%
  ggplot(aes(y = Construct,
             x = Intensity_MeanIntensity_MCHERRY_BACKCORR))+
  geom_boxplot(outlier.shape = NA, aes(fill = `4_residue_insert`))+
  #geom_vline(xintercept = 0.003)+
  geom_text(data = population_intensity_df %>%
              ungroup() %>% 
              group_by(Construct) %>% 
              summarize(n_cell = n()),
            aes(x = 0.85, y = Construct, label = paste0('n=',n_cell)), color = 'black', size = 3)+
  coord_cartesian(xlim = c(0.0005, 0.9))+
  scale_x_log10()+
  scale_y_discrete(limits = rev)+
  labs(title = 'Expression levels of SNX2 constructs',
       subtitle = 'Cells pooled from 3 experimental repeats',
       x = 'mCherry intensity (a.u.)',
       y = 'SNX2 construct',
       fill = '4-residue\ninsertion')+
  theme_bw(base_size = 14)
```


## Importing SNX2 isoform classifiers and extracting the isoform-distinguishing features
```{r Function to load in the classifier performance and importance, echo=FALSE}
#
Replicate_performance_and_importance <- function(MODEL_FOLDER, SET, PAIR, TRANSFECTION_STATUS, PERCENTILE_CUTOFF = 0){
  if(TRANSFECTION_STATUS == 'POSITIVE'){
    load(paste0(MODEL_FOLDER,'/',SET,'_',PAIR))
  }
  if(TRANSFECTION_STATUS == 'NEGATIVE'){
    load(paste0(MODEL_FOLDER,'/NegTransModel_',SET,'_',PAIR))
  }
  #
  modeL_fit_and_tune <- function(variable){
    a <- variable$results %>%
      dplyr::filter(!is.na(ROC)) %>% 
      dplyr::arrange(desc(ROC)) %>% 
      dplyr::slice_head(n = 1) %>% 
      dplyr::mutate(size_decay_tune = paste0('size:',size,'_decay:',decay))
    return(a)
  }
  #
  variable_importance_ranking <- function(variable){
    variable_importance <- variable$variable_importance %>% 
      arrange(desc(Overall)) %>%
      rownames_to_column(var = 'Feature') %>% 
      as_tibble()
    
    rank <- seq(1, dim(variable_importance)[1])
    
    variable_importance <- bind_cols(variable_importance, 'Rank' = rank)
    return(variable_importance)
  }
  #
  n_cells <- function(variable){
    cell_count <- variable$training_data_intensity %>% 
    count()
    return(cell_count)
  }
  #
  
  ISOFORM_MODELS <- as.list(replicate_nnet[1,]) #Converts matrix rows into lists
  NEGATIVE_MODELS <- as.list(replicate_nnet[2,])
  POSITIVE_MODELS <- as.list(replicate_nnet[3,])
  
  #
  isoform_model_fit_and_tune <- lapply(ISOFORM_MODELS, FUN = modeL_fit_and_tune)
  isoform_variable_importance <- lapply(ISOFORM_MODELS, FUN = variable_importance_ranking)
  isoform_n_cells <- lapply(ISOFORM_MODELS, FUN = n_cells)
  #
  negative_fit_and_tune <- lapply(NEGATIVE_MODELS, FUN = modeL_fit_and_tune)
  negative_variable_importance <- lapply(NEGATIVE_MODELS, FUN = variable_importance_ranking)
  negative_n_cells <- lapply(NEGATIVE_MODELS, FUN = n_cells)
  #
  positive_fit_and_tune <- lapply(POSITIVE_MODELS, FUN = modeL_fit_and_tune)
  positive_variable_importance <- lapply(POSITIVE_MODELS, FUN = variable_importance_ranking)
  positive_n_cells <- lapply(POSITIVE_MODELS, FUN = n_cells)
  
  #
  iso_performance <- bind_rows(isoform_model_fit_and_tune, .id = 'Replicate')
  neg_performance <- bind_rows(negative_fit_and_tune, .id = 'Replicate')
  pos_performance <- bind_rows(positive_fit_and_tune, .id = 'Replicate') %>% 
    rename_with(~paste0(.,"_pos"), -Replicate)
  
  #
  iso_n <- bind_rows(isoform_n_cells, .id = 'Replicate')
  neg_n <- bind_rows(negative_n_cells, .id = 'Replicate')
  pos_n <- bind_rows(positive_n_cells, .id = 'Replicate')
  n_cells_all_models <- bind_rows(iso_n, neg_n, pos_n, .id = 'Group')%>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  ###
  pair_x_performance <- bind_rows(iso_performance, neg_performance, bind_rows(positive_fit_and_tune, .id = 'Replicate'),.id = 'Group') %>% 
    dplyr::mutate('Group' = as_factor(case_when(Group == 1 ~ 'Isoform',
                                                Group == 2 ~ 'Negative',
                                                Group == 3 ~ 'Positive')),
                  'Group' = fct_relevel(Group, 'Negative','Isoform', 'Positive'))
  
  #
  
  ###
  relative_performance <- full_join(x = iso_performance, y = neg_performance, by = c('Replicate'), suffix = c('_iso', '_neg')) %>% 
    full_join(x = ., y = pos_performance, by = c('Replicate')) %>% 
    dplyr::mutate('ROC_difference_from_neg' = ROC_iso - ROC_neg,
                  'ROC_difference_from_pos' = ROC_iso - ROC_pos,
                  'ROC_difference_pos_from_neg' = ROC_pos - ROC_neg)
  
  #
  
  ###
  number_of_classifier_iterations <- length(isoform_variable_importance)
  number_of_features <- length(unique(isoform_variable_importance[[1]]$Feature))
  #
  iso_importance <- bind_rows(isoform_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance <- bind_rows(negative_variable_importance, .id = 'Replicate') %>% 
    ungroup() %>% 
    group_by(Feature) %>% 
    summarize('Rank_sum' = sum(Rank),
              'Rank_median' = median(Rank),
              'Rank_05percent' = quantile(Rank, probs = c(0.05)),
              'Rank_10percent' = quantile(Rank, probs = c(0.1)),
              'Rank_25percent' = quantile(Rank, probs = c(0.25)),
              'Rank_75percent' = quantile(Rank, probs = c(0.75)),
              'Rank_90percent' = quantile(Rank, probs = c(0.9)),
              'Rank_95percent' = quantile(Rank, probs = c(0.95)),
              'Overall_sum' = sum(Overall),
              'Overall_sd' = sd(Overall)) %>% 
    dplyr::mutate('No_iterations' = number_of_classifier_iterations,
                  'Highest_potential_overall' = 100 * number_of_classifier_iterations,
                  'Highest_potential_rank' = number_of_classifier_iterations,
                  'Lowest_potential_rank' = number_of_classifier_iterations * number_of_features,
                  'Rank_75_25' = Rank_75percent - Rank_25percent,
                  'Rank_90_10' = Rank_90percent - Rank_10percent,
                  'Rank_95_05' = Rank_95percent - Rank_05percent) %>%
    dplyr::mutate('Rank_avg' = Rank_sum/No_iterations,
                  'Overall_avg' = Overall_sum/No_iterations) %>% 
    dplyr::arrange(Rank_sum)
  #
  neg_importance_reduced <- neg_importance %>% 
    dplyr::select(Feature, Rank_sum, Rank_avg, Rank_median, Rank_90_10, Rank_95_05, Overall_sum, Overall_avg, Overall_sd)
  
    #
  iso_neg_comb_importance <- dplyr::full_join(x = iso_importance, y = neg_importance_reduced, by = c('Feature'), suffix = c('','_neg')) %>% 
    dplyr::mutate('Rank_median_difference' = Rank_median_neg - Rank_median,
                  'Rank_sum_difference' = Rank_sum_neg - Rank_sum,
                  'Rank_90_10_difference' = Rank_90_10_neg - Rank_90_10,
                  'Rank_95_05_difference' = Rank_95_05_neg - Rank_95_05)
  
  
  #
  
  results_list <- list('performance' = pair_x_performance, 'SET' = SET, 'PAIR' = PAIR, 'relative_performance' = relative_performance, 'TRANSFECTION_STATUS' = TRANSFECTION_STATUS, 'PERCENTILE_CUTOFF' = PERCENTILE_CUTOFF,
                       'var_importance_iso' = iso_importance, 'var_importance_neg' = negative_variable_importance, 'var_importance_pos' = positive_variable_importance,
                       'var_importance_iso_w_contrast' = iso_neg_comb_importance, 'n_cells' = n_cells_all_models)
  return(results_list)
}
```

```{r Loading Positive transfectant models, echo = FALSE}
#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Postransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'POSITIVE')
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('postrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('postrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('postrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
```

```{r Loading negative transfectant models 10 percentile, echo = FALSE}
#Set 1A
for(i in PAIRS_1A){
  test <- Replicate_performance_and_importance(MODEL_FOLDER = Negtransfected_model_folder,
                                               SET = 'SET_1A',
                                               PAIR = i,
                                               TRANSFECTION_STATUS = 'NEGATIVE',
                                               PERCENTILE_CUTOFF = 10)
  #
  
  #Creates absolute performance metrics (single metrics)
  assign(paste0('negtrans_model_performance_',test$SET,'_',test$PAIR),test$performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF) %>% 
           left_join(., y = test$n_cells, by = c('Replicate','Group')))
  #Creates relative performance object
  assign(paste0('negtrans_relative_performance_',test$SET,'_',test$PAIR), test$relative_performance %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
  #Creates variable importance object
  assign(paste0('negtrans_iso_variable_contrast_importance_',test$SET,'_',test$PAIR), test$var_importance_iso_w_contrast %>% 
           dplyr::mutate('SET' = test$SET,
                         'ISOFORM_PAIR' = test$PAIR,
                         'TRANSFECTION_STATUS' = test$TRANSFECTION_STATUS,
                         'PERCENTILE_CUTOFF' = test$PERCENTILE_CUTOFF))
}
```

```{r Loading exon descriptions, echo = FALSE}
#Exon description
Exon_descriptions <- readxl::read_xlsx(path = paste0(Path_to_exon_description_sheet, File_with_exon_description_sheet),
                                       sheet = Event_sheet) %>% 
  dplyr::mutate('microexon' = Exon_length_NT <= 30) %>% 
  dplyr::mutate(Gene_name_Rclassifier = case_when( #Note, currently because names in SET D are marked w. asteriks, they have to be so in this exon description file. But excel didn't like starting the name w. an asteriks.
    Gene_name_Rclassifier == 'ATXN2' ~ '*ATXN2', #Only done for the isoform pairs that are not recurring
    Gene_name_Rclassifier == 'EVI5' ~ '*EVI5',
    Gene_name_Rclassifier == 'PPFIA1' ~ '*PPFIA1',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExA' ~ 'CLASP1_ExA_vs_ExB',
    Gene_name_Rclassifier == 'CLASP1' & Exon_name_Rclassifier == 'ExB' ~ 'CLASP1_noEx_vs_ExB',
    .default = Gene_name_Rclassifier))

Exon_descriptions_reduced <- Exon_descriptions %>% 
  dplyr::select(microexon, Splice_event_enriched_in_neural_tissue, Splice_event_enriched_in_pancreatic_islet_cells, Enrichment_comment, Exon_length_NT, Gene_name_Rclassifier, Exon_name_Rclassifier, EVENT_ID_vastDB, Location_in_protein) %>% 
  dplyr::filter(!c(Gene_name_Rclassifier == 'VAV2')) #Current_naming_doesn't_work_well_with_genes_with_multiple_exons

### ISOFORM_PAIRS_EXCLUDE
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_DOUBLES <- c('VAV2','*SH3KBP1_D/E','*OCRL_D/E','*SH3GLB1_D/E')
ISOFORM_PAIRS_TO_EXCLUDE_DUE_TO_INTENSITY <- c('VAV2','PACSIN2') ##THIS DEFINES WHICH ISOFORM PAIRS ARE EXCLUDED.

```


```{r combining absolute classifier outputs into proper datasets, echo = FALSE}
#Combining individual isoforms into proper dataset
## Absolute performance
#Set 1A
combined_model_performance_SET_1A <- bind_rows(mget(ls(pattern = 'model_performance_SET_1A_PAIR'))) #Will contain both SET_1A normal comps and alternative CLASP1 comparisons
rm(list = ls(pattern = 'model_performance_SET_1A_PAIR'))

#All
combined_model_performance_all <- bind_rows(mget(ls(pattern = 'combined_model_performance_SET_'))) %>%  #WRITE CASE_WHEN TO GIVE ALL SET + PAIR COMBINATIONS THEIR GENE NAME (COULD POTENTIALLY BE GENE + EXON ID -> ALTHOUGH COMBINATIONS GET TRICKY STILL)
  dplyr::mutate('Gene_name' = case_when(
    SET == 'SET_1A' & ISOFORM_PAIR == 'PAIR_09' ~ 'SNX2'
   )) %>% 
  #left_join(., y = SUMMARY_of_all_sample_ratios, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) %>% 
  left_join(., y = Exon_descriptions_reduced, by = join_by('Gene_name' == 'Gene_name_Rclassifier')) %>% 
  #The fusion doesn't work perfectly for genes with multiple events - the line below removes an unwanted duplication of the VAV2 data (NOTE, THIS IS WHAT GIVES RISE TO THE MANY-TO-MANY RELATIONSHIP)
  dplyr::filter(!c(SET == 'SET_1A' & Gene_name == 'VAV2' & Exon_name_Rclassifier == 'ExB')) %>% 
  #
  dplyr::mutate(microexon = case_when( #Hacky way of making all events have microexon, yes/no label
    word(Gene_name, 1, 1, sep = fixed('_')) == '*APP' ~ FALSE,
    word(Gene_name, 1, 1, sep = fixed('_')) == '*VAV2' ~ TRUE,
    word(Gene_name, 1, 1, sep = fixed('_')) == 'CLASP1' ~ TRUE,
    .default = microexon))
#

#Dataframe w. the gene name SET + PAIR combination
gene_ids_match <- combined_model_performance_all %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB) %>%
  unique()

#Dataframe w. n used for classifier and the gene names
n_used_for_classifier <- combined_model_performance_all %>% 
  dplyr::select(n, Gene_name) %>% 
  unique() %>% 
  dplyr::group_by(Gene_name) %>% 
  summarize(n = mean(n))

```


```{r creating relative ROC that compares negative transfectant and positive transfectant ROCs, echo = FALSE}
#Splitting the combined ROC dataset according to transfection status
#Positive transfectants
combined_model_performance_all_postrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE')
#Negative transfectants
combined_model_performance_all_negtrans <- combined_model_performance_all %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE')

#Joining positive and negative transfectants in a wide-format
combined_model_performance_all_posneg_relative <- full_join(x = combined_model_performance_all_postrans, y = combined_model_performance_all_negtrans,
                                                            by = join_by(SET, ISOFORM_PAIR, Group, Replicate),
                                                            suffix = c('_postrans', '_negtrans')) %>%
  # Creating ROC relative column (pos - neg). Can be negative.
  dplyr::mutate(ROC_posneg_relative = ROC_postrans - ROC_negtrans,
                tmp_norm_ROC = (ROC_postrans - ROC_negtrans)/(1 - ROC_negtrans),
                Ceiling_normalised_ROC = if_else(tmp_norm_ROC >= 0, tmp_norm_ROC, (ROC_postrans - ROC_negtrans)/(1 - ROC_postrans)))
```


```{r Function to perform bootstrap confidence interval caluclations, echo = FALSE}
#' Bootstrap Test for Pre-Normalized ROC Scores with Group Support
#'
#' This function calculates bootstrap confidence intervals for normalized ROC scores
#' that have already been calculated. It supports grouping by a variable (e.g., gene name).
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param group_value Value to filter by in the group column (e.g., specific gene name)
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#'
#' @return A list containing bootstrap statistics and test results
#'
#' @examples
#' # Example with pre-calculated normalized values
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2))
#' )
#' result <- bootstrap_norm_roc_grouped(data, "norm_roc", "Gene_name", "Gene1")
#' print(result)
#'
bootstrap_norm_roc_grouped <- function(data, 
                                       norm_col = "norm_roc", 
                                       group_col = NULL,
                                       group_value = NULL,
                                       conf_level = 0.95,
                                       n_bootstrap = 2000,
                                       one_sided = TRUE) {
  
  # Require boot package
  if (!requireNamespace("boot", quietly = TRUE)) {
    stop("Please install the 'boot' package: install.packages('boot')")
  }
  
  # Filter data by group if specified
  if (!is.null(group_col) && !is.null(group_value)) {
    if (!(group_col %in% colnames(data))) {
      stop(paste("Group column", group_col, "not found in data"))
    }
    data <- data[data[[group_col]] == group_value, ]
    if (nrow(data) == 0) {
      stop(paste("No data found for", group_col, "=", group_value))
    }
  }
  
  # Check if norm_col exists
  if (!(norm_col %in% colnames(data))) {
    stop(paste("Normalized score column", norm_col, "not found in data"))
  }
  
  # Extract normalized scores
  norm_scores <- data[[norm_col]]
  
  # Function for bootstrapping
  boot_func <- function(data, indices) {
    return(mean(data[indices]))
  }
  
  # Perform bootstrap
  boot_result <- boot::boot(norm_scores, boot_func, R = n_bootstrap)
  
  # Calculate confidence interval
  if (one_sided) {
    # One-sided interval (lower bound only)
    alpha <- 1 - conf_level
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound of percentile interval
    upper_bound <- Inf
  } else {
    # Two-sided interval
    ci <- boot::boot.ci(boot_result, type = "perc", conf = conf_level)
    lower_bound <- ci$percent[4]  # Lower bound
    upper_bound <- ci$percent[5]  # Upper bound
  }
  
  # Determine if zero is in the confidence interval
  zero_in_ci <- (lower_bound <= 0 && upper_bound >= 0)
  
  # Create summary results
  result <- list(
    mean = mean(norm_scores),
    median = median(norm_scores),
    sd = sd(norm_scores),
    ci_lower = lower_bound,
    ci_upper = ifelse(one_sided, Inf, upper_bound),
    one_sided = one_sided,
    conf_level = conf_level,
    zero_in_ci = zero_in_ci,
    significant = !zero_in_ci,
    n_iterations = length(norm_scores),
    n_bootstrap = n_bootstrap,
    group_col = group_col,
    group_value = group_value,
    raw_scores = norm_scores,
    boot_result = boot_result
  )
  
  return(result)
}

#' Run Bootstrap Tests for Multiple Groups
#'
#' This function runs bootstrap tests for multiple groups and returns results in a data frame
#'
#' @param data A data frame containing the normalized scores
#' @param norm_col Name of the column containing normalized ROC values
#' @param group_col Name of the column for grouping (e.g., "Gene_name")
#' @param conf_level Confidence level (default 0.95)
#' @param n_bootstrap Number of bootstrap iterations (default 2000)
#' @param one_sided Logical; if TRUE, returns one-sided interval (default TRUE)
#' @param adjust_method Method for multiple testing correction (default "BH"). Options include 
#'                     "holm", "hochberg", "hommel", "bonferroni", "BH", "BY", "fdr", "none"
#'
#' @return A data frame with bootstrap test results for each group, including adjusted p-values
#'
#' @examples
#' # Example with pre-calculated normalized values for multiple genes
#' data <- data.frame(
#'   Gene_name = rep(c("Gene1", "Gene2", "Gene3"), each = 50),
#'   norm_roc = c(rnorm(50, 0.3, 0.1), rnorm(50, -0.1, 0.2), rnorm(50, 0.15, 0.15))
#' )
#' results <- bootstrap_multiple_groups(data, "norm_roc", "Gene_name")
#' print(results)
#'
bootstrap_multiple_groups <- function(data, 
                                      norm_col = "norm_roc", 
                                      group_col,
                                      conf_level = 0.95,
                                      n_bootstrap = 2000,
                                      one_sided = TRUE,
                                      adjust_method = "BH") {
  
  # Get unique groups
  groups <- unique(data[[group_col]])
  
  # Create empty results data frame
  results <- data.frame(
    group = character(),
    mean = numeric(),
    median = numeric(),
    sd = numeric(),
    ci_lower = numeric(),
    ci_upper = numeric(),
    p_value = numeric(),
    significant = logical(),
    adj_p_value = numeric(),
    adj_significant = logical(),
    n_iterations = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Loop through groups
  group_results <- list()
  p_values <- numeric(length(groups))
  
  for (i in seq_along(groups)) {
    group <- groups[i]
    # Run bootstrap test
    boot_result <- bootstrap_norm_roc_grouped(
      data = data,
      norm_col = norm_col,
      group_col = group_col,
      group_value = group,
      conf_level = conf_level,
      n_bootstrap = n_bootstrap,
      one_sided = one_sided
    )
    
    # Calculate p-value from bootstrap distribution
    if (one_sided) {
      # For one-sided test, calculate p-value as proportion of bootstrap values <= 0
      p_value <- mean(boot_result$boot_result$t <= 0)
    } else {
      # For two-sided test, calculate p-value based on whether 0 is in the CI
      # This is approximate but aligns with the confidence interval approach
      z_stat <- boot_result$mean / (boot_result$sd / sqrt(boot_result$n_iterations))
      p_value <- if (boot_result$mean >= 0) 2 * pnorm(-abs(z_stat)) else 2 * pnorm(-abs(z_stat))
    }
    
    p_values[i] <- p_value
    
    # Store result
    group_results[[i]] <- data.frame(
      group = group,
      mean = boot_result$mean,
      median = boot_result$median,
      sd = boot_result$sd,
      ci_lower = boot_result$ci_lower,
      ci_upper = ifelse(one_sided, Inf, boot_result$ci_upper),
      p_value = p_value,
      significant = boot_result$significant,
      n_iterations = boot_result$n_iterations
    )
  }
  
  # Adjust p-values for multiple testing
  adj_p_values <- p.adjust(p_values, method = adjust_method)
  
  # Combine results
  results <- do.call(rbind, group_results)
  results$adj_p_value <- adj_p_values
  results$adj_significant <- results$adj_p_value < (1 - conf_level)
  
  # Return results
  return(results)
}

#' Visualize Bootstrap Distribution
#'
#' Creates a histogram of bootstrap means with confidence interval
#'
#' @param boot_result Result from bootstrap_norm_roc_grouped function
#' @param bins Number of histogram bins (default 30)
#'
#' @return A ggplot2 object
#'
plot_bootstrap_dist <- function(boot_result, bins = 30) {
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Extract bootstrap samples
  t_values <- boot_result$boot_result$t
  
  # Create dataframe for plotting
  df <- data.frame(value = t_values)
  
  # Determine title suffix based on grouping
  group_suffix <- ""
  if (!is.null(boot_result$group_col) && !is.null(boot_result$group_value)) {
    group_suffix <- paste(" for", boot_result$group_col, "=", boot_result$group_value)
  }
  
  # Create plot
  p <- ggplot2::ggplot(df, ggplot2::aes(x = value)) +
    ggplot2::geom_histogram(bins = bins, fill = "steelblue", color = "white", alpha = 0.7) +
    ggplot2::geom_vline(xintercept = boot_result$ci_lower, color = "red", linetype = "dashed") +
    ggplot2::geom_vline(xintercept = 0, color = "black", linetype = "solid") +
    ggplot2::labs(
      title = paste0("Bootstrap Distribution of Normalized ROC Score", group_suffix),
      subtitle = paste0(
        ifelse(boot_result$one_sided, "One-sided ", "Two-sided "), 
        boot_result$conf_level * 100, "% CI: [", 
        round(boot_result$ci_lower, 4), ", ", 
        ifelse(boot_result$one_sided, "∞", round(boot_result$ci_upper, 4)), "]"
      ),
      x = "Normalized ROC Score",
      y = "Frequency",
      caption = paste("Mean:", round(boot_result$mean, 4), 
                      "| Significant:", boot_result$significant)
    ) +
    ggplot2::theme_minimal()
  
  return(p)
}

#' Create Forest Plot of Bootstrap Results
#'
#' Creates a forest plot of bootstrap results for multiple groups
#'
#' @param results Data frame from bootstrap_multiple_groups function
#' @param sort_by Column to sort by (default "mean")
#' @param decreasing Logical; if TRUE, sorts in decreasing order (default TRUE)
#' @param color_by_significance Logical; if TRUE, colors points by significance (default TRUE)
#'
#' @return A ggplot2 object
#'
plot_forest <- function(results, 
                        sort_by = "mean", 
                        decreasing = TRUE,
                        color_by_significance = TRUE,
                        use_adjusted_significance = TRUE) {
  
  # Require ggplot2
  if (!requireNamespace("ggplot2", quietly = TRUE)) {
    stop("Please install the 'ggplot2' package: install.packages('ggplot2')")
  }
  
  # Sort results
  results <- results[order(results[[sort_by]], decreasing = decreasing), ]
  
  # Make sure group is a factor in the right order for plotting
  results$group <- factor(results$group, levels = results$group)
  
  # Determine which significance column to use
  sig_col <- if(use_adjusted_significance && "adj_significant" %in% colnames(results)) {
    "adj_significant"
  } else {
    "significant"
  }
  
  # Create plot
  p <- ggplot2::ggplot(results, ggplot2::aes(x = mean, y = group)) +
    ggplot2::geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    ggplot2::geom_errorbarh(ggplot2::aes(xmin = ci_lower, xmax = ci_upper), height = 0.2) +
    ggplot2::geom_point(ggplot2::aes(color = if(color_by_significance) .data[[sig_col]] else NULL), 
                        size = 3) +
    scale_y_discrete(limits = rev(levels(results$group)))+
    ggplot2::labs(
      title = paste0("Normalized ROC Scores with Bootstrap Confidence Intervals",
                     ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                            "\n(adjusted for multiple testing)", "")),
      x = "Normalized ROC Score",
      y = NULL,
      subtitle = ifelse("adj_p_value" %in% colnames(results), 
                        paste0("Multiple testing correction: ", 
                               ifelse(any(results$adj_p_value != results$p_value), "Applied", "None")),
                        "")
    ) +
    ggplot2::theme_minimal() +
    ggplot2::theme(
      axis.text.y = ggplot2::element_text(size = 10),
      legend.position = "bottom"
    )
  
  # Add color scale if coloring by significance
  if (color_by_significance) {
    p <- p + ggplot2::scale_color_manual(
      values = c("FALSE" = "gray50", "TRUE" = "steelblue"),
      name = ifelse(use_adjusted_significance && "adj_significant" %in% colnames(results),
                    "Significant (Adjusted)", "Significant"),
      labels = c("FALSE" = "No", "TRUE" = "Yes")
    )
  }
  
  return(p)
}

# Example usage:
# # Create sample data with pre-calculated normalized ROC values
# set.seed(123)
# data <- data.frame(
#   Gene_name = rep(c("Gene1", "Gene2", "Gene3", "Gene4"), each = 50),
#   norm_roc = c(rnorm(50, 0.3, 0.1), 
#               rnorm(50, -0.1, 0.2), 
#               rnorm(50, 0.15, 0.15),
#               rnorm(50, 0.05, 0.1))
# )
# 
# # Test a single gene
# result_gene1 <- bootstrap_norm_roc_grouped(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name",
#   group_value = "Gene1"
# )
# print(result_gene1)
# plot1 <- plot_bootstrap_dist(result_gene1)
# print(plot1)
# 
# # Test all genes
# results_all <- bootstrap_multiple_groups(
#   data = data,
#   norm_col = "norm_roc",
#   group_col = "Gene_name"
# )
# print(results_all)
# 
# # Create forest plot
# plot2 <- plot_forest(results_all)
# print(plot2)

# Remove a specific item from legend
# If you need to remove an item from a ggplot2 legend (such as color), 
# you can use the following approach after creating your plot:

# Example:
# p <- plot_forest(results_all, use_adjusted_significance = TRUE)
# 
# # To remove the color legend completely:
# p <- p + ggplot2::theme(legend.position = "none")
# 
# # To keep the legend but remove specific guides:
# p <- p + ggplot2::guides(color = "none")
# 
# # To create a table of results
# library(knitr)
# results_table <- results_all[, c("group", "mean", "ci_lower", "ci_upper", 
#                                 "p_value", "adj_p_value", "adj_significant")]
# results_table <- results_table[order(results_table$adj_p_value), ]
# kable(results_table, digits = 4)
# 
# print(p)
```

This code runs the bootstrap confidence interval testing so we can select statisticallyt signfiicant isos
```{r Calculating bootstrap confidence intervals and creates confidence interval plot, echo=FALSE}
bootstrap_scores <- bootstrap_multiple_groups(data = combined_model_performance_all_posneg_relative %>% 
                                    dplyr::filter(Group == 'Isoform'), 
                          norm_col = "Ceiling_normalised_ROC", 
                          group_col = 'Gene_name_postrans',
                          conf_level = confidence_interval_threshold_for_bootstrap,
                          n_bootstrap = 2000,
                          one_sided = TRUE,
                          adjust_method = "BH") 

#Note, p-values are zero or 1 in most cases - anyhow, we can just indicate significance, I guess.

#Could include this plot as supplementary (?)
```


```{r Loading variable importance classifier data, echo = FALSE}
#Variable importance
combined_variable_importance_set_1A <- bind_rows(mget(ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR')))
rm(list = ls(pattern = 'iso_variable_contrast_importance_SET_1A_PAIR'))
#
combined_variable_importance_all <- bind_rows(mget(ls(pattern = 'combined_variable_importance_set_'))) %>%
  left_join(x = ., y = gene_ids_match, by = join_by('SET' == 'SET', 'ISOFORM_PAIR' == 'ISOFORM_PAIR')) 

#
combined_overall <- combined_variable_importance_all %>% 
  ungroup() %>% 
  group_by(Gene_name, TRANSFECTION_STATUS) %>% 
  summarize('Combined_overall' = sum(Overall_avg),
            'Combined_overall_neg' = sum(Overall_avg_neg))%>% 
  dplyr::arrange(Combined_overall)


combined_variable_importance_all_w_overall <- combined_variable_importance_all %>% 
  left_join(., x = combined_overall, by = join_by('Gene_name' == 'Gene_name', 'TRANSFECTION_STATUS' == 'TRANSFECTION_STATUS')) %>%
  dplyr::mutate('contribution_prop' = (Overall_avg/Combined_overall)*100,
                'contribution_prop_sd' = (Overall_sd/Combined_overall)*100,
                'contribution_prop_neg' = (Overall_avg_neg/Combined_overall_neg)*100,
                'contribution_prop_neg_sd' = (Overall_sd_neg/Combined_overall_neg)*100)

# Combining the variable importance data for negtrans and postrans in a wider format
# Positive transfectants
combined_variable_importance_all_w_overall_postrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'POSITIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)
# Negative transfectants
combined_variable_importance_all_w_overall_negtrans <- combined_variable_importance_all_w_overall %>% 
  dplyr::filter(TRANSFECTION_STATUS == 'NEGATIVE') %>% 
  dplyr::select(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, TRANSFECTION_STATUS, Feature,  Rank_median, contribution_prop, contribution_prop_sd,
                'Rank_median_negcontrol' = Rank_median_neg, 'contribution_prop_negcontrol' = contribution_prop_neg,
                'contribution_prop_negcontrol_sd' = contribution_prop_neg_sd)

# Combined positive and negative transfectants
combined_variable_importance_all_w_overall_posneg <- combined_variable_importance_all_w_overall_postrans %>% 
  # Joining variable importance for postrans and negtrans
  dplyr::left_join(x = ., y = combined_variable_importance_all_w_overall_negtrans, by = join_by(SET, ISOFORM_PAIR, Gene_name, microexon, Exon_length_NT, EVENT_ID_vastDB, Feature), suffix = c('_pos', '_neg')) %>% 
  # Introducing the contribution proportion ratio (postrans/negtrans)
  dplyr::mutate(contribution_prop_ratio = contribution_prop_pos/contribution_prop_neg,
                contribution_prop_ratio_negcontrol = contribution_prop_negcontrol_pos/contribution_prop_negcontrol_neg,
                ratio_times_importance = contribution_prop_ratio * contribution_prop_pos,
                noteworthy_feature = if_else(ratio_times_importance >= ratio_times_importance_threshold & contribution_prop_ratio > ratio_threshold, TRUE, FALSE)) %>% 
  # Add p-values from the bootstrapping confidence intervals
    left_join(x = .,
            y = bootstrap_scores %>% dplyr::select(group, adj_p_value, adj_significant),
            by = join_by('Gene_name' == 'group'))
```


```{r Selecting noteworthy SNX2 isoform features to use for PCA, echo = FALSE}
SNX2_noteworthy_features <- combined_variable_importance_all_w_overall_posneg %>% 
  dplyr::filter(Gene_name == 'SNX2') %>% 
  dplyr::filter(noteworthy_feature == TRUE) %>% 
  dplyr::arrange(desc(ratio_times_importance)) %>% 
  dplyr::pull(Feature)
```

## Reducing the noteworthy features by removing highly correlated features based on measurements of SNX2 mutants

```{r Function for reducing number of noteworthy features by removing highly correlated features, echo=FALSE}
# Function for removing highly correlated features
Identify_and_remove_highly_correlated_features <- function(DATASET, CUTOFF_THRESHOLD, SEED){ #variables_to_keep = c('')
  set.seed(SEED)
  correlationMatrix <- cor(DATASET[,], use = 'pairwise.complete.obs')
  highlyCorrelated <- findCorrelation(correlationMatrix, cutoff=CUTOFF_THRESHOLD, names = TRUE, exact = TRUE)
  HIGHLY_CORRELATED_FEATURES_TO_REMOVE <- as_tibble(bind_cols('HIGHLY_CORRELATED_FEATURES' = highlyCorrelated)) %>%
    #dplyr::filter(!c(HIGHLY_CORRELATED_FEATURES %in% variables_to_keep)) %>% 
    dplyr::pull(HIGHLY_CORRELATED_FEATURES)
  #print(HIGHLY_CORRELATED_FEATURES_TO_REMOVE)
  DATASET_VARIABLES_REDUCED <- DATASET %>% 
    dplyr::select(!(all_of(HIGHLY_CORRELATED_FEATURES_TO_REMOVE)))
  # Retained variables
  Retained_variables <- colnames(DATASET_VARIABLES_REDUCED)
  
  return(list(Reduced_dataset = DATASET_VARIABLES_REDUCED,
              Retained_variables = Retained_variables,
              Removed_variables = HIGHLY_CORRELATED_FEATURES_TO_REMOVE))
}
```


```{r Reducing number of noteworthy features by removing highly correlated features, echo=FALSE}
### Strict intensity thresholding ###
# Using well means as input
SNX2_noteworthy_features_without_highly_corr_strict_intensity_wells <- Identify_and_remove_highly_correlated_features(
  Transfected_only_without_outliers_SNX2muts_strict_intensity  %>% 
    dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')) %>% 
    group_by(Metadata_Well, Construct) %>%
    summarize(across(all_of(SNX2_noteworthy_features), mean, na.rm = TRUE)) %>% 
    ungroup() %>% 
    dplyr::select(!all_of(c('Metadata_Well','Construct'))),
  CUTOFF_THRESHOLD = 0.80,
  SEED = 123)$Retained_variables




# Output of selected features
SNX2_noteworthy_features_without_highly_corr_strict_intensity_wells
```


# PCA
## PCA with reduced noteworthy feature list

```{r Full PCA postrans after removing highly correlated features, echo = FALSE}
SNX2_muts_PCAresults_pc1_2 <- run_pca_analysis(
    data = Transfected_only_without_outliers_SNX2muts_strict_intensity %>% 
      dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')),                     # Your data frame
    condition_col = "Construct", # Column name for condition IDs
    selected_features = SNX2_noteworthy_features_without_highly_corr_strict_intensity_wells,          # Vector of feature column names to use for PCA
    do_center = TRUE,           # Whether to center the data
    do_scale = TRUE,            # Whether to scale the data
    num_clusters = 6,           # Number of clusters to create
    pc_x = 1,                   # PC for x-axis in plots
    pc_y = 2,                   # PC for y-axis in plots
    add_ellipses = FALSE,        # Whether to add confidence ellipses
    add_labels = FALSE,           # Whether to add labels to points
    point_size = 3,             # Size of points in plots
    use_numbered_biplot = TRUE,  # Whether to use numbers instead of text in biplot
    biplot_color_by = "none",    # Color biplot points: "none", "cluster", or "condition"
    color_arrows_by_category = TRUE, # Color arrows by first word in variable name
    show_point_numbers = FALSE  # Show or hide the numbers on points in the biplot
)
SNX2_muts_PCAresults_pc1_2$plots$scree
SNX2_muts_PCAresults_pc1_2$plots$pca_by_condition
SNX2_muts_PCAresults_pc1_2$plots$pca_by_cluster
SNX2_muts_PCAresults_pc1_2$plots$biplot
SNX2_muts_PCAresults_pc1_2$plots$lookup_tables
```

```{r Full PCA for negtrans after removing highly correlated features, echo=FALSE}
SNX2_muts_PCAresults_pc1_2_negtrans <- run_pca_analysis(
    data = NegTransfected_only_without_outliers_SNX2muts %>% 
      dplyr::filter(!Metadata_Well %in% c('A01','A02','B04')),                     # Your data frame
    condition_col = "Construct", # Column name for condition IDs
    selected_features = SNX2_noteworthy_features_without_highly_corr_strict_intensity_wells,          # Vector of feature column names to use for PCA
    do_center = TRUE,           # Whether to center the data
    do_scale = TRUE,            # Whether to scale the data
    num_clusters = 6,           # Number of clusters to create
    pc_x = 1,                   # PC for x-axis in plots
    pc_y = 2,                   # PC for y-axis in plots
    add_ellipses = FALSE,        # Whether to add confidence ellipses
    add_labels = FALSE,           # Whether to add labels to points
    point_size = 3,             # Size of points in plots
    use_numbered_biplot = TRUE,  # Whether to use numbers instead of text in biplot
    biplot_color_by = "none",    # Color biplot points: "none", "cluster", or "condition"
    color_arrows_by_category = TRUE, # Color arrows by first word in variable name
    show_point_numbers = FALSE   # Show or hide the numbers on points in the biplot
)
SNX2_muts_PCAresults_pc1_2_negtrans$plots$scree
SNX2_muts_PCAresults_pc1_2_negtrans$plots$pca_by_condition
SNX2_muts_PCAresults_pc1_2_negtrans$plots$pca_by_cluster
SNX2_muts_PCAresults_pc1_2_negtrans$plots$biplot
SNX2_muts_PCAresults_pc1_2_negtrans$plots$lookup_tables
```

##

```{r lineplots of intensity versus granularity, echo = FALSE}
Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  dplyr::filter(Construct %in% c('+EX','-EX (rep2)','+EX: EIRE|qIqq|W', '+EX: EIRk|EIEE|W','-EX: EIaE|----|W','-EX: EIkE|----|W','-EX: EIeE|----|W','-EX: EIqE|----|W')) %>% 
  dplyr::mutate(cluster_identity = case_when(Construct %in% c('+EX','-EX: EIeE|----|W','+EX: EIRE|qIqq|W', '+EX: EIRk|EIEE|W') ~ 'SNX2+EX cluster',
                                             Construct == "-EX: EIqE|----|W" ~ 'In-between cluster',
                                             Construct %in% c('-EX (rep2)','-EX: EIaE|----|W','-EX: EIkE|----|W') ~ 'SNX2 -EX cluster',
                                             .default = 'None')) %>% 
  #dplyr::filter(Construct %in% c('-EX: EIkE|----|W')) %>% 
  dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR <= 0.06) %>% 
  #dplyr::filter(Construct %in% c('+EX','-EX (rep2)', '-EX: EIaE|----|W', '-EX: EIkE|----|W','-EX: EIqE|----|W','-EX: EIeE|----|W')) %>% 
  #ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Granularity_1_MCHERRY_BACKCORR, color = Construct))+
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Granularity_2_MCHERRY_BACKCORR, color = Construct))+
  #geom_vline(xintercept = 0.00075)+
  scale_x_log10()+
  #geom_point()+
  geom_smooth(aes(linetype = cluster_identity), se = FALSE)+
    labs(title = 'SNX2 isoforms and mutants',
       y = 'Granularity 2',
       x = 'mCherry intensity (a.u.)',
       linetype = 'Cluster',
       color = 'Construct')+
  theme_bw(base_size = 16)

###
Transfected_only_without_outliers_SNX2muts_loose_intensity %>% 
  dplyr::filter(Construct %in% c('+EX','-EX (rep2)','+EX: EIRE|qIqq|W', '+EX: EIRk|EIEE|W','-EX: EIaE|----|W','-EX: EIkE|----|W','-EX: EIeE|----|W','-EX: EIqE|----|W')) %>% 
  dplyr::mutate(cluster_identity = case_when(Construct %in% c('+EX','-EX: EIeE|----|W','+EX: EIRE|qIqq|W', '+EX: EIRk|EIEE|W') ~ 'SNX2+EX cluster',
                                             Construct == "-EX: EIqE|----|W" ~ 'In-between cluster',
                                             Construct %in% c('-EX (rep2)','-EX: EIaE|----|W','-EX: EIkE|----|W') ~ 'SNX2 -EX cluster',
                                             .default = 'None')) %>% 
  #dplyr::filter(Construct %in% c('-EX: EIkE|----|W')) %>% 
  dplyr::filter(Intensity_MeanIntensity_MCHERRY_BACKCORR <= 0.06) %>% 
  #dplyr::filter(Construct %in% c('+EX','-EX (rep2)', '-EX: EIaE|----|W', '-EX: EIkE|----|W','-EX: EIqE|----|W','-EX: EIeE|----|W')) %>% 
  #ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Granularity_1_MCHERRY_BACKCORR, color = Construct))+
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR/transfection_threshold, y = Granularity_2_MCHERRY_BACKCORR, color = Construct))+
  #geom_vline(xintercept = 0.00075)+
  scale_x_log10()+
  #geom_point()+
  geom_smooth(aes(linetype = cluster_identity), se = FALSE)+
    labs(title = 'SNX2 isoforms and mutants',
       y = 'Granularity 2',
       x = 'mCherry intensity (relative to transfection threshold)',
       linetype = 'Cluster',
       color = 'Construct')+
  theme_bw(base_size = 16)

```


