---
title: "09_Cell_filtering_and_transfection_calling"
author: "Peter Kjer Hansen"
date: "2025-03-18"
output:
  html_document:
    fig_width: 12
---
This .rmd is used to import the cell measurements obtained from cell profiler and filter the cells and images to remove cells that are mis-segmented or dividing. It then enables exploration of the mCherry levels in the non-transfected cell populations which can be used to determine a transfection threshold (using mCherry mean intensity and upper quartile) that defines the mCherry-positive cells. Using the transfection threshold, we can then define whether cells are transfected or not, which is used for subsequent analysis.
The filter cell dataset with assigned transfection status can be saved as a new .csv file that is then used for down-stream classifier-based analysis OR other types of analysis such as principal compoonent analysis used for the SNX2 mutant constructs.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Required packages
library(tidyverse)
library(readxl)
```

```{r Defining working directories and file names, echo = FALSE}
### Working directories for different reps
# Rep1
working_directory_rep1 <- 'INSERT DIRECTORY'
# Rep 2
working_directory_rep2 <- 'INSERT DIRECTORY'
# Rep 3
working_directory_rep3 <- 'INSERT DIRECTORY'

### File names
# Cellbody
cellbody_file <- 'INSERT file name of .csv containing cellprofiler measurements from cellbody segmentations'
# Cellbody not on border
cellbody_not_on_border_file <- 'INSERT file name of .csv containing cellprofiler measurements from cellbody not on border'
# Nuclues
nuclei_file <- 'INSERT file name of .csv containing cellprofiler measurements from nucleus segmentation'
# Cytoplasm
cytoplasm_file <- 'INSERT file name of .csv containing cellprofiler measurements from cytoplasm segmentation'
# Metadata file  
metadata_file <- 'INSERT file name of .csv containing image-level information'

### Excel sheet describing images to manually remove
# Path
fovs_to_remove_file <- 'INSERT PATH TO .xlsx that describes what images to remove based on artifacts (fibres, out-of-focus, etc.)'
# Sheet
sheet_name <- 'INSERT SHEET NAME'
```


```{r Filter function ONE For filtering cells based on classification and touching border, echo = FALSE}
cell_classification <- function(DATASET){
  cell_classification <- DATASET %>% 
    dplyr::select(ImageNumber, ObjectNumber, Children_Cellbodies_NOT_ON_BORDER_Count, Classify_DYING_DIVIDING_CELL, Classify_PROPER_CELL) %>% 
    dplyr::mutate('Cell_classification' = case_when(
      Classify_DYING_DIVIDING_CELL == 1 ~ 'DYING_DIVIDING',
      Classify_PROPER_CELL == 1 ~ 'PROPER'),
      Touching_border = if_else(Children_Cellbodies_NOT_ON_BORDER_Count == 1, FALSE, TRUE)) %>% 
    dplyr::select(ImageNumber, ObjectNumber, Cell_classification, Touching_border) 
  NEW_DATASET <- dplyr::left_join(x = DATASET, y = cell_classification, by = c("ImageNumber","ObjectNumber")) %>%
    dplyr::filter(Touching_border == FALSE) %>% 
    dplyr::filter(Cell_classification == 'PROPER') %>%
    dplyr::select(!c(Classify_DYING_DIVIDING_CELL, Classify_PROPER_CELL)) %>% 
    dplyr::select(!ends_with('_Object_prediction')) #NOTE, THIS LINE OF CODE CAN BE USED UPON IMPORT AND THAT IS LIKELY PREFERABLE
  return(NEW_DATASET)
}
```

```{r Filter function TWO For removing cells based on degree of touching, echo = FALSE}
#Remove cells with PercentTouching of other cellbodies above a certain limit, e.g. 80%. Takes dataset and cutoff as inputs
remove_high_touchpercent_cells <- function(DATASET,TOUCH_CUTOFF){
  NEW_DATASET <- DATASET %>% 
    dplyr::filter(Neighbors_PercentTouching_Adjacent < TOUCH_CUTOFF)
  return(NEW_DATASET)
}
```

```{r Filter function THREE For removing cells based on nuclei count and touching nuclei, echo=FALSE}
#Filters cellbodies based on containing multiple nuclei
#AND based on whether nuclei from separate cells are within 10 pixels from one another (which may also indicate multiple nuclei + mis-segment)
#It is basically are an expansion of the single nucleus per cellbody filter. Use either one or the other. (can be used sequentially but 'keep one nuclei' is done by this function as well)
remove_cells_with_touching_nuclei <- function(PARENT_DATASET,
                                              CHILD_DATASET,
                                              CELLBODY_NOT_ON_BORDER_DATASET){
  Nucleus_information <- CELLBODY_NOT_ON_BORDER_DATASET %>% 
    dplyr::filter(Children_Nucleus_segmentation_Count == 1) %>% 
    dplyr::mutate(CELLBODY_NOT_ON_BORDER_ID = paste0(ImageNumber,'_',ObjectNumber),
                  Parent_Segmentation_ID = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)) %>% 
    #
    dplyr::left_join(x = ., y = CHILD_DATASET %>%
        dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbodies_NOT_ON_BORDER),
                      'NUCLEUS_ID' = paste0(ImageNumber,'_',ObjectNumber)) %>%
        dplyr::filter(!Parent_Cellbodies_NOT_ON_BORDER == 0) %>% 
        dplyr::select(NUCLEUS_ID, PARENT_ID,
                      'NumberOfNeighbors_nucleus' = contains('Neighbors_NumberOfNeighbors'),
                      'PercentTouching_nucleus' = contains('Neighbors_PercentTouching')),
        by = join_by(CELLBODY_NOT_ON_BORDER_ID == PARENT_ID)) %>% 
    dplyr::select(CELLBODY_NOT_ON_BORDER_ID,
                  Parent_Segmentation_ID,
                  NUCLEUS_ID,
                  NumberOfNeighbors_nucleus,
                  PercentTouching_nucleus)
    
  #
  single_nuclei_cellbody <- PARENT_DATASET %>% 
    dplyr::mutate('OBJECT_ID' = paste0(ImageNumber,'_',ObjectNumber)) %>% 
    dplyr::inner_join(x = ., y = Nucleus_information, by = join_by(OBJECT_ID == Parent_Segmentation_ID))%>%
    dplyr::filter(NumberOfNeighbors_nucleus == 0 & PercentTouching_nucleus == 0)
  
  return(single_nuclei_cellbody)
}
```

```{r Filter function FOUR For removing images with weird cell morphologies determined manually, echo=FALSE}

# Reading in FOVs to remove
FOVS_to_remove_df <- read_xlsx(path = fovs_to_remove_file,
          sheet = sheet_name)


# Function to remove the FOVs listed in the dataframe
Remove_FOVs_manually <- function(CELL_DATA,
                                 FOV_DATA,
                                 EXP_REP){ # Numeric
  # Selects only FOVS from specific REP
  FOV_DATA_REP_SPECIFIC <- FOV_DATA %>%
    dplyr::filter(Rep == EXP_REP)
  
  # Filters the cell data according to the FOVs to remove
  CELL_DATA_FILTERED <- CELL_DATA %>% 
    dplyr::mutate(FOV_ID = paste0('r',Metadata_Row,'c',Metadata_Column,'f',Metadata_FOV)) %>% 
    dplyr::filter(!FOV_ID %in% FOV_DATA_REP_SPECIFIC$FOV_ID) %>% 
    dplyr::select(-FOV_ID) # Removes the column used for pairing
  #
  return(CELL_DATA_FILTERED)
}
```


```{r Function for cleaning up duplicated columns, echo=FALSE}
# Function to remove duplicate columns and clean column names
clean_duplicated_columns <- function(df) {
  # Get column names
  col_names <- names(df)
  
  # Extract base names (removing the "...x" suffix)
  base_names <- gsub("\\.\\.\\.[0-9]+$", "", col_names)
  
  # Create a dataframe to track unique columns
  col_df <- data.frame(
    original_name = col_names,
    base_name = base_names,
    index = 1:length(col_names),
    stringsAsFactors = FALSE
  )
  
  # Keep first occurrence of each base name
  keep_cols <- tapply(col_df$index, col_df$base_name, min)
  
  # Select only the columns to keep
  clean_df <- df[, keep_cols]
  
  # Clean the column names by removing the "...x" suffix
  names(clean_df) <- gsub("\\.\\.\\.[0-9]+$", "", names(clean_df))
  
  return(clean_df)
}

# Example usage
# my_clean_df <- clean_duplicated_columns(my_df)
```


```{r Function to define transfected cells, echo = FALSE}
#Intensity threshold to define transfected population and summary of transfection rates
#####
#Thresholds:
Define_transfected <- function(DATASET, MEAN_INTENSITY_THRESHOLD, UPPER_QUARTILE_INTENSITY_THRESHOLD, EXP_SET, EXP_REP){
  #
  TRANSFECTION_DATASET <- DATASET  %>%
    dplyr::mutate('TRANSFECTED' = Intensity_MeanIntensity_MCHERRY_BACKCORR > MEAN_INTENSITY_THRESHOLD & 
                    Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR > UPPER_QUARTILE_INTENSITY_THRESHOLD)
  
  #
  TRANSFECTION_SUMMARY <- TRANSFECTION_DATASET %>% 
      ungroup() %>%
      group_by(Metadata_Well, TRANSFECTED) %>% 
      summarise(n = n()) %>%
      ungroup() %>% 
      pivot_wider(id_cols = c('Metadata_Well'), names_from = TRANSFECTED, names_prefix = 'Transfected_', values_from = c('n')) %>% 
      dplyr::mutate('n_cells' = if_else(is.na(Transfected_TRUE) == TRUE, Transfected_FALSE, Transfected_TRUE + Transfected_FALSE),
                'Trans_rate' = if_else(is.na(Transfected_TRUE) == TRUE, 0,Transfected_TRUE/n_cells * 100,0),
                'MeanIntensity_Threshold' = MEAN_INTENSITY_THRESHOLD,
                'UpperQuartileIntensity_Threshold' = UPPER_QUARTILE_INTENSITY_THRESHOLD) %>%
      dplyr::mutate('Experiment_Set' =  EXP_SET,
                'Experiment_Rep' = EXP_REP)
      
  TRANSFECTION_SUMMARY[is.na(TRANSFECTION_SUMMARY)] = 0
  
  #
  TRANSFECTION_LIST <- list(TRANSFECTION_DATASET = TRANSFECTION_DATASET,
                            TRANSFECTION_SUMMARY = TRANSFECTION_SUMMARY)
  return(TRANSFECTION_LIST)
}
```


## Replicate 1
```{r Loading datasets from rep1, echo = FALSE, message = FALSE, warning=FALSE}
# Read in PARENT_DATASET (CELLBODY)
working_directory <- working_directory_rep1
cellbody <- read_csv(paste0(working_directory,'/',cellbody_file))

# Read in CHILD_DATASET (NUCLEI, CYTOPLASM)
cellbody_not_on_border <- read_csv(paste0(working_directory,'/',cellbody_not_on_border_file))
nuclei <- read_csv(paste0(working_directory,'/',nuclei_file))
cytoplasm <- read_csv(paste0(working_directory,'/',cytoplasm_file))

# Read in metadata  
metadata <- read_csv(paste0(working_directory,'/',metadata_file)) %>%
  dplyr::select(ImageNumber,Metadata_Row, Metadata_Column, Metadata_Well ,Group_Number, Group_Index,
                c(starts_with('Classify'), starts_with('Count_Cellbodies'),starts_with('Count_Nucleus'), starts_with('Count_Segmentation')),
                starts_with('PathName_')) %>% 
    dplyr::mutate('Experiment_Set' = paste('SET_SNX2mutants'),
                'Experiment_Rep' = paste0('REP_',substr(word(PathName_MCHERRY, start = 7, end = 7, sep = fixed("/")),4,4)), #(Whereas SetRep isn't required for the PC12s, I have included it as it may make the subsequent pipeline run more easily)
                'Experiment_SetRep' = paste0(Experiment_Set,'_',Experiment_Rep))
```


```{r Applying all filter functions REP 1, echo = FALSE}
#TEST OF ALL FILTERS
ONE <- cell_classification(cellbody)
TWO <- remove_high_touchpercent_cells(ONE, 90)
THREE <- remove_cells_with_touching_nuclei(PARENT_DATASET = TWO,
                                          CHILD_DATASET = nuclei,
                                          CELLBODY_NOT_ON_BORDER_DATASET = cellbody_not_on_border)
FOUR <- Remove_FOVs_manually(CELL_DATA = THREE,
                             FOV_DATA = FOVS_to_remove_df,
                             EXP_REP = 1)

# Filtering the cellbodies not on border dataset according to cells retained in cell bodies (we do this as CELLBODIES Not on border had additional measurements made)
FIVE <- FOUR %>%
  #
  dplyr::mutate('OBJECT_ID' = paste0(ImageNumber,'_',ObjectNumber)) %>% 
  dplyr::select(OBJECT_ID) %>% 
  dplyr::left_join(x = .,
                   y = cellbody_not_on_border %>%  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)),
                   by = join_by('OBJECT_ID' == 'PARENT_ID'),
                   keep = TRUE) %>% 
  dplyr::select(-OBJECT_ID)

```


```{r Removing additional columns and cleaning up df rep 1, echo =FALSE}
# Generating a nuclei dataset for fusion that only contains minimal variables
filtered_reduced_nuclei <- nuclei %>% 
  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)) %>% 
  dplyr::select(PARENT_ID, 'AreaShape_Area_NUCLEUS' = AreaShape_Area...12, 'AreaShape_Eccentricity_NUCLEUS' = AreaShape_Eccentricity...56)

#
cols_to_discard <- c('AreaShape_Center_X','AreaShape_Center_Y','AreaShape_Compactness','AreaShape_EquivalentDiameter','AreaShape_EulerNumber',
                     'AreaShape_Solidity', 'AreaShape_Extent','AreaShape_BoundingBoxArea',
                     'AreaShape_BoundingBoxMinimum_X','AreaShape_BoundingBoxMinimum_Y','AreaShape_BoundingBoxMaximum_X','AreaShape_BoundingBoxMaximum_Y',
                     'AreaShape_ConvexArea','AreaShape_MajorAxisLength','AreaShape_MinorAxisLength',
                     'AreaShape_Orientation','AreaShape_MaximumRadius','AreaShape_MedianRadius',
                     'AreaShape_MeanRadius','AreaShape_MinFeretDiameter','AreaShape_MaxFeretDiameter',
                     'Metadata_Row','Metadata_Column',
                     'Metadata_Channel','Metadata_FOV','Metadata_FileLocation','Metadata_Frame','Metadata_Series','Metadata_Slice',
                     'Children_Nucleus_segmentation_Count','Children_Cytoplasm_Count',
                     'Parent_Cellbody_segmentation',
                     'Classify_DYING_DIVIDING_CELL','Classify_PROPER_CELL')



# Fusing the nuclei with the cellbodies and adding metadata from metadata file
Filtered_cellbodies <- FIVE %>% 
  dplyr::left_join(x = .,
                   y = filtered_reduced_nuclei,
                   by = join_by('PARENT_ID' == 'PARENT_ID')) %>% 
  # Removes rows with no nucleus area.
  dplyr::filter(!is.na(AreaShape_Area_NUCLEUS) == TRUE) %>% 
  # Fusing with meta data
  dplyr::left_join(x = ., y = metadata %>% dplyr::select(ImageNumber, Experiment_Set, Experiment_Rep, Experiment_SetRep), by = join_by('ImageNumber' == 'ImageNumber')) %>% 
  #
  clean_duplicated_columns() %>% 
  #
  dplyr::select(!all_of(cols_to_discard)) %>% 
  dplyr::select(!(c(#starts_with('AreaShape_SpatialMoment_'), starts_with('AreaShape_CentralMoment'), starts_with('AreaShape_NormalizedMoment'),
                    'AreaShape_NormalizedMoment_0_0','AreaShape_NormalizedMoment_0_1','AreaShape_NormalizedMoment_1_0',
                    ends_with('_Object_prediction'),
                    starts_with('Location_CenterMassIntensity_'),starts_with('Location_MaxIntensity_'), starts_with('Location_Center_')))) #%>%

```

```{r Plot used to define transfection cutoffs rep 1, echo = FALSE}
#
Mean_threshold_rep1 <- 0.0008
Upperquantile_threshold_rep1 <- 0.00110


Filtered_cellbodies %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep1, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep1, color = 'red')+
  coord_cartesian(xlim = c(0, 0.005), ylim = c(0, 0.005))+
  theme_bw()


Filtered_cellbodies %>% 
  dplyr::filter(Metadata_Well == 'A01') %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  #facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep1, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep1, color = 'red')+
  coord_cartesian(xlim = c(0, 0.0015), ylim = c(0, 0.005))+
  theme_bw()
```

```{r Assigning transfection status rep1, echo = FALSE, message = FALSE}
Transfected_cells_and_summary <- Define_transfected(DATASET = Filtered_cellbodies,
                                       MEAN_INTENSITY_THRESHOLD = Mean_threshold_rep1,
                                       UPPER_QUARTILE_INTENSITY_THRESHOLD = Upperquantile_threshold_rep1,
                                       EXP_SET = 'SET_SNX2mutants',
                                       EXP_REP = 'REP_1')
#
Transfected_cellbodies <- Transfected_cells_and_summary$TRANSFECTION_DATASET
Transfection_summary <- Transfected_cells_and_summary$TRANSFECTION_SUMMARY
```


```{r Save transfected data from rep 1, echo=FALSE}
save(Transfected_cellbodies, file = paste0(working_directory,'/SET_SNX2mutants_REP1_TRANSFECTED_CELLS'))
save(Transfection_summary, file = paste0(working_directory,'/SET_SNX2mutants_REP1_TRANSFECTION_SUMMARY'))
```


## Replicate 2
```{r Loading datasets from rep2, echo = FALSE, message = FALSE, warning=FALSE}
# Read in PARENT_DATASET (CELLBODY)
working_directory <- working_directory_rep2
cellbody <- read_csv(paste0(working_directory,'/',cellbody_file))

# Read in CHILD_DATASET (NUCLEI, CYTOPLASM)
cellbody_not_on_border <- read_csv(paste0(working_directory,'/',cellbody_not_on_border_file))
nuclei <- read_csv(paste0(working_directory,'/',nuclei_file))
cytoplasm <- read_csv(paste0(working_directory,'/',cytoplasm_file))

# Read in metadata  
metadata <- read_csv(paste0(working_directory,'/',metadata_file)) %>%
  dplyr::select(ImageNumber,Metadata_Row, Metadata_Column, Metadata_Well ,Group_Number, Group_Index,
                c(starts_with('Classify'), starts_with('Count_Cellbodies'),starts_with('Count_Nucleus'), starts_with('Count_Segmentation')),
                starts_with('PathName_')) %>% 
    dplyr::mutate('Experiment_Set' = paste('SET_SNX2mutants'),
                'Experiment_Rep' = paste0('REP_',substr(word(PathName_MCHERRY, start = 7, end = 7, sep = fixed("/")),4,4)), #(Whereas SetRep isn't required for the PC12s, I have included it as it may make the subsequent pipeline run more easily)
                'Experiment_SetRep' = paste0(Experiment_Set,'_',Experiment_Rep))
```


```{r Applying all filter functions REP 2, echo = FALSE}
#TEST OF ALL FILTERS
ONE <- cell_classification(cellbody)
TWO <- remove_high_touchpercent_cells(ONE, 90)
THREE <- remove_cells_with_touching_nuclei(PARENT_DATASET = TWO,
                                          CHILD_DATASET = nuclei,
                                          CELLBODY_NOT_ON_BORDER_DATASET = cellbody_not_on_border)
FOUR <- Remove_FOVs_manually(CELL_DATA = THREE,
                             FOV_DATA = FOVS_to_remove_df,
                             EXP_REP = 2)

# Filtering the cellbodies not on border dataset according to cells retained in cell bodies (we do this as CELLBODIES Not on border had additional measurements made)
FIVE <- FOUR %>%
  #
  dplyr::mutate('OBJECT_ID' = paste0(ImageNumber,'_',ObjectNumber)) %>% 
  dplyr::select(OBJECT_ID) %>% 
  dplyr::left_join(x = .,
                   y = cellbody_not_on_border %>%  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)),
                   by = join_by('OBJECT_ID' == 'PARENT_ID'),
                   keep = TRUE) %>% 
  dplyr::select(-OBJECT_ID)

```


```{r Removing additional columns and cleaning up df rep 2, echo =FALSE}
# Generating a nuclei dataset for fusion that only contains minimal variables
filtered_reduced_nuclei <- nuclei %>% 
  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)) %>% 
  dplyr::select(PARENT_ID, 'AreaShape_Area_NUCLEUS' = AreaShape_Area...12, 'AreaShape_Eccentricity_NUCLEUS' = AreaShape_Eccentricity...56)

#
cols_to_discard <- c('AreaShape_Center_X','AreaShape_Center_Y','AreaShape_Compactness','AreaShape_EquivalentDiameter','AreaShape_EulerNumber',
                     'AreaShape_Solidity', 'AreaShape_Extent','AreaShape_BoundingBoxArea',
                     'AreaShape_BoundingBoxMinimum_X','AreaShape_BoundingBoxMinimum_Y','AreaShape_BoundingBoxMaximum_X','AreaShape_BoundingBoxMaximum_Y',
                     'AreaShape_ConvexArea','AreaShape_MajorAxisLength','AreaShape_MinorAxisLength',
                     'AreaShape_Orientation','AreaShape_MaximumRadius','AreaShape_MedianRadius',
                     'AreaShape_MeanRadius','AreaShape_MinFeretDiameter','AreaShape_MaxFeretDiameter',
                     'Metadata_Row','Metadata_Column',
                     'Metadata_Channel','Metadata_FOV','Metadata_FileLocation','Metadata_Frame','Metadata_Series','Metadata_Slice',
                     'Children_Nucleus_segmentation_Count','Children_Cytoplasm_Count',
                     'Parent_Cellbody_segmentation',
                     'Classify_DYING_DIVIDING_CELL','Classify_PROPER_CELL')



# Fusing the nuclei with the cellbodies and adding metadata from metadata file
Filtered_cellbodies <- FIVE %>% 
  dplyr::left_join(x = .,
                   y = filtered_reduced_nuclei,
                   by = join_by('PARENT_ID' == 'PARENT_ID')) %>% 
  # Removes rows with no nucleus area.
  dplyr::filter(!is.na(AreaShape_Area_NUCLEUS) == TRUE) %>% 
  # Fusing with meta data
  dplyr::left_join(x = ., y = metadata %>% dplyr::select(ImageNumber, Experiment_Set, Experiment_Rep, Experiment_SetRep), by = join_by('ImageNumber' == 'ImageNumber')) %>% 
  #
  clean_duplicated_columns() %>% 
  #
  dplyr::select(!all_of(cols_to_discard)) %>% 
  dplyr::select(!(c(#starts_with('AreaShape_SpatialMoment_'), starts_with('AreaShape_CentralMoment'), starts_with('AreaShape_NormalizedMoment'),
                    'AreaShape_NormalizedMoment_0_0','AreaShape_NormalizedMoment_0_1','AreaShape_NormalizedMoment_1_0',
                    ends_with('_Object_prediction'),
                    starts_with('Location_CenterMassIntensity_'),starts_with('Location_MaxIntensity_'), starts_with('Location_Center_')))) #%>%

```

```{r Plot used to define transfection cutoffs rep 2, echo = FALSE}
#
Mean_threshold_rep2 <- 0.00070
Upperquantile_threshold_rep2 <- 0.00100


Filtered_cellbodies %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep2, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep2, color = 'red')+
  coord_cartesian(xlim = c(0, 0.005), ylim = c(0, 0.005))+
  theme_bw()


Filtered_cellbodies %>% 
  dplyr::filter(Metadata_Well == 'A01') %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  #facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep2, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep2, color = 'red')+
  coord_cartesian(xlim = c(0, 0.0015), ylim = c(0, 0.005))+
  theme_bw()
```

```{r Assigning transfection status rep2, echo = FALSE, message = FALSE}
Transfected_cells_and_summary <- Define_transfected(DATASET = Filtered_cellbodies,
                                       MEAN_INTENSITY_THRESHOLD = Mean_threshold_rep2,
                                       UPPER_QUARTILE_INTENSITY_THRESHOLD = Upperquantile_threshold_rep2,
                                       EXP_SET = 'SET_SNX2mutants',
                                       EXP_REP = 'REP_2')
#
Transfected_cellbodies <- Transfected_cells_and_summary$TRANSFECTION_DATASET
Transfection_summary <- Transfected_cells_and_summary$TRANSFECTION_SUMMARY
#View(Transfection_summary)
```


```{r Save transfected data from rep 2, echo=FALSE}
save(Transfected_cellbodies, file = paste0(working_directory,'/SET_SNX2mutants_REP2_TRANSFECTED_CELLS'))
save(Transfection_summary, file = paste0(working_directory,'/SET_SNX2mutants_REP2_TRANSFECTION_SUMMARY'))
```


## Replicate 3
```{r Loading datasets from rep3, echo = FALSE, message = FALSE, warning=FALSE}
# Read in PARENT_DATASET (CELLBODY)
working_directory <- working_directory_rep3
cellbody <- read_csv(paste0(working_directory,'/',cellbody_file))

# Read in CHILD_DATASET (NUCLEI, CYTOPLASM)
cellbody_not_on_border <- read_csv(paste0(working_directory,'/',cellbody_not_on_border_file))
nuclei <- read_csv(paste0(working_directory,'/',nuclei_file))
cytoplasm <- read_csv(paste0(working_directory,'/',cytoplasm_file))

# Read in metadata  
metadata <- read_csv(paste0(working_directory,'/',metadata_file)) %>%
  dplyr::select(ImageNumber,Metadata_Row, Metadata_Column, Metadata_Well ,Group_Number, Group_Index,
                c(starts_with('Classify'), starts_with('Count_Cellbodies'),starts_with('Count_Nucleus'), starts_with('Count_Segmentation')),
                starts_with('PathName_')) %>% 
    dplyr::mutate('Experiment_Set' = paste('SET_SNX2mutants'),
                'Experiment_Rep' = paste0('REP_',substr(word(PathName_MCHERRY, start = 7, end = 7, sep = fixed("/")),4,4)), #(Whereas SetRep isn't required for the PC12s, I have included it as it may make the subsequent pipeline run more easily)
                'Experiment_SetRep' = paste0(Experiment_Set,'_',Experiment_Rep))
```


```{r Applying all filter functions REP 3, echo = FALSE}
#TEST OF ALL FILTERS
ONE <- cell_classification(cellbody)
TWO <- remove_high_touchpercent_cells(ONE, 90)
THREE <- remove_cells_with_touching_nuclei(PARENT_DATASET = TWO,
                                          CHILD_DATASET = nuclei,
                                          CELLBODY_NOT_ON_BORDER_DATASET = cellbody_not_on_border)
FOUR <- Remove_FOVs_manually(CELL_DATA = THREE,
                             FOV_DATA = FOVS_to_remove_df,
                             EXP_REP = 3)

# Filtering the cellbodies not on border dataset according to cells retained in cell bodies (we do this as CELLBODIES Not on border had additional measurements made)
FIVE <- FOUR %>%
  #
  dplyr::mutate('OBJECT_ID' = paste0(ImageNumber,'_',ObjectNumber)) %>% 
  dplyr::select(OBJECT_ID) %>% 
  dplyr::left_join(x = .,
                   y = cellbody_not_on_border %>%  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)),
                   by = join_by('OBJECT_ID' == 'PARENT_ID'),
                   keep = TRUE) %>% 
  dplyr::select(-OBJECT_ID)

```


```{r Removing additional columns and cleaning up df rep 3, echo =FALSE}
# Generating a nuclei dataset for fusion that only contains minimal variables
filtered_reduced_nuclei <- nuclei %>% 
  dplyr::mutate('PARENT_ID' = paste0(ImageNumber,'_',Parent_Cellbody_segmentation)) %>% 
  dplyr::select(PARENT_ID, 'AreaShape_Area_NUCLEUS' = AreaShape_Area...12, 'AreaShape_Eccentricity_NUCLEUS' = AreaShape_Eccentricity...56)

#
cols_to_discard <- c('AreaShape_Center_X','AreaShape_Center_Y','AreaShape_Compactness','AreaShape_EquivalentDiameter','AreaShape_EulerNumber',
                     'AreaShape_Solidity', 'AreaShape_Extent','AreaShape_BoundingBoxArea',
                     'AreaShape_BoundingBoxMinimum_X','AreaShape_BoundingBoxMinimum_Y','AreaShape_BoundingBoxMaximum_X','AreaShape_BoundingBoxMaximum_Y',
                     'AreaShape_ConvexArea','AreaShape_MajorAxisLength','AreaShape_MinorAxisLength',
                     'AreaShape_Orientation','AreaShape_MaximumRadius','AreaShape_MedianRadius',
                     'AreaShape_MeanRadius','AreaShape_MinFeretDiameter','AreaShape_MaxFeretDiameter',
                     'Metadata_Row','Metadata_Column',
                     'Metadata_Channel','Metadata_FOV','Metadata_FileLocation','Metadata_Frame','Metadata_Series','Metadata_Slice',
                     'Children_Nucleus_segmentation_Count','Children_Cytoplasm_Count',
                     'Parent_Cellbody_segmentation',
                     'Classify_DYING_DIVIDING_CELL','Classify_PROPER_CELL')



# Fusing the nuclei with the cellbodies and adding metadata from metadata file
Filtered_cellbodies <- FIVE %>% 
  dplyr::left_join(x = .,
                   y = filtered_reduced_nuclei,
                   by = join_by('PARENT_ID' == 'PARENT_ID')) %>% 
  # Removes rows with no nucleus area.
  dplyr::filter(!is.na(AreaShape_Area_NUCLEUS) == TRUE) %>% 
  # Fusing with meta data
  dplyr::left_join(x = ., y = metadata %>% dplyr::select(ImageNumber, Experiment_Set, Experiment_Rep, Experiment_SetRep), by = join_by('ImageNumber' == 'ImageNumber')) %>% 
  #
  clean_duplicated_columns() %>% 
  #
  dplyr::select(!all_of(cols_to_discard)) %>% 
  dplyr::select(!(c(#starts_with('AreaShape_SpatialMoment_'), starts_with('AreaShape_CentralMoment'), starts_with('AreaShape_NormalizedMoment'),
                    'AreaShape_NormalizedMoment_0_0','AreaShape_NormalizedMoment_0_1','AreaShape_NormalizedMoment_1_0',
                    ends_with('_Object_prediction'),
                    starts_with('Location_CenterMassIntensity_'),starts_with('Location_MaxIntensity_'), starts_with('Location_Center_')))) #%>%

```

```{r Plot used to define transfection cutoffs rep 3, echo = FALSE}
#
Mean_threshold_rep3 <- 0.00065
Upperquantile_threshold_rep3 <- 0.00098


Filtered_cellbodies %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep3, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep3, color = 'red')+
  coord_cartesian(xlim = c(0, 0.005), ylim = c(0, 0.005))+
  theme_bw()


Filtered_cellbodies %>% 
  dplyr::filter(Metadata_Well == 'A01') %>% 
  ggplot(aes(x = Intensity_MeanIntensity_MCHERRY_BACKCORR, y = Intensity_UpperQuartileIntensity_MCHERRY_BACKCORR))+
  geom_point(alpha = 0.2)+
  #facet_wrap(~Metadata_Well, nrow = 4)+
  geom_vline(xintercept = Mean_threshold_rep3, color = 'red')+
  geom_hline(yintercept = Upperquantile_threshold_rep3, color = 'red')+
  coord_cartesian(xlim = c(0, 0.0015), ylim = c(0, 0.005))+
  theme_bw()
```

```{r Assigning transfection status rep3, echo = FALSE, message = FALSE}
Transfected_cells_and_summary <- Define_transfected(DATASET = Filtered_cellbodies,
                                       MEAN_INTENSITY_THRESHOLD = Mean_threshold_rep3,
                                       UPPER_QUARTILE_INTENSITY_THRESHOLD = Upperquantile_threshold_rep3,
                                       EXP_SET = 'SET_SNX2mutants',
                                       EXP_REP = 'REP_3')
#
Transfected_cellbodies <- Transfected_cells_and_summary$TRANSFECTION_DATASET
Transfection_summary <- Transfected_cells_and_summary$TRANSFECTION_SUMMARY
#View(Transfection_summary)
```


```{r Save transfected data from rep 3, echo=FALSE}
save(Transfected_cellbodies, file = paste0(working_directory,'/SET_SNX2mutants_REP3_TRANSFECTED_CELLS'))
save(Transfection_summary, file = paste0(working_directory,'/SET_SNX2mutants_REP3_TRANSFECTION_SUMMARY'))
```
